% !TEX encoding = UTF-8 Unicode
% !TEX TS-program = XeLaTeX

\documentclass[11pt]{article}
\usepackage{geometry}
\geometry{letterpaper,margin=1in}

% Typography
\usepackage{fontspec,realscripts}
\defaultfontfeatures{Ligatures=TeX}
\setromanfont[Numbers=OldStyle]{Arno Pro}
\setsansfont[Numbers=OldStyle]{Scala Sans Pro}
\setmonofont[Scale=MatchLowercase]{Menlo}
\usepackage{sectsty}
\allsectionsfont{\sffamily}
\frenchspacing

\title{Guidelines for Papers and Other Written Assignments}
\author{Daniel R. Driver, PhD}
\date{}

\begin{document}
\maketitle


\section{Make an Argument}

Academic writing aims to persuade. In this course, therefore, you are
asked to craft thoughtful, defensible arguments. Whether you are
summarizing an article, conducting a book review, interpreting an
ancient text, outlining a theological position, organizing historical
evidence, or advancing a thesis in a major paper, you should be certain
that you have a point to make, and that your writing serves that point
effectively. Different assignments call for arguments to be mounted in
different ways, but in virtually every case your submission should have
a clear thesis statement that is well supported by the rest of the
piece. Your readers should be able to identify it easily, not least
because it takes the form of a single, grammatical sentence. In the best
cases it will even be elegant. As Nicholas Lash writes, “God’s beauty is
not well served by ugly prose.”\footnote{Nicholas Lash, \emph{The
Beginning and the End of “Religion”} (Cambridge: Cambridge University
Press, 1996), 122.}

What makes a thesis strong? Arguments can take many forms, but a good
thesis has three main characteristics: it must be \textbf{restricted},
\textbf{unified}, and \textbf{precise}.\footnote{Margot Northey,
Bradford A. Anderson, and Joel N. Lohr, \emph{Making Sense in Religious
Studies: A Student's Guide to Research and Writing}, 3rd ed. (Don Mills,
ON: Oxford University Press, 2019), 64–66.}

To be \textbf{restricted}, a thesis must limit the scope of an essay to
what can be discussed in detail within the bounds of the paper's
expected length. Whole monographs have been written on single psalms. It
is simply not realistic to think that you can prove something about the
entire Book of Psalms in twenty pages. A good thesis is narrow in focus.
For example: “The divine warrior motif in Psalm 24:7–10 finds natural
resonance in later Christian liturgies of Christ's Harrowing of Hell, as
seen in the libretto of Handel's \emph{Messiah}.”

Second, a thesis must be \textbf{unified}; in other words, it must
express only one idea. Consider the following sentence: “Sabbath keeping
has different rationales in the Old Testament, is radically transformed
by Jesus in the New Testament, and yet interest in the topic seems to be
growing as Christians struggle to find rest and renewal in their busy
lives.” The problem with this thesis is that it commits the writer to
several different topics: (1) rationales for sabbath observance in
ancient Israel, (2) the transformation of sabbath practices in the early
Church, and (3) contemporary accounts of spirituality that may have as
much in common with therapeutic self-help literature as with traditional
religious devotion. When a thesis uses a coordinating sentence,
containing two or more parts, it is important that all of the parts are
closely related so that the focus of the paper is not diffused.
[\emph{For homework: rewrite this thesis.}]

Third, a good thesis is \textbf{precise}, meaning that when it is read,
it can only have one interpretation. Vague words should be avoided. And
abstract words may be problematic, unless the paper is dealing with an
abstract issue. For example, a theology paper dealing with Thomist
metaphysics may require more abstract language than an exegetical paper
dealing with manuscript evidence from the Dead Sea Scrolls. Generally,
try to make the thesis as clear and specific as possible, fleeing from
words that express nondescript meaning, such as \emph{unusual},
\emph{interesting}, \emph{inspiring}, or \emph{important}, to name a
few.

Finally, a thesis sentence is most often expressed in a single sentence,
and is generally found at the end of a well developed introductory
paragraph. This rule is not set in stone but usually works well because
it helps the reader to make an easy transition into the body of the
paper. Remember, while you do have some flexibility in the way you craft
your thesis sentence, without a thesis that is restricted, unified, and
precise, it is nearly impossible to have a good paper.

\section{Consider the Specific Assignment}

Always refer to the syllabus for the exact parameters of your
assignments in a given course. For general help with some common writing
assignments in Dr. Driver's courses, see below.

\subsection{The Forum Post}

Does a 250-word forum post need to have a thesis? Not necessarily. A
class forum is a fine place to experiment with creative approaches to
big questions, so please feel free to try something unusual. Responses
could take the form of a letter (to the editor, say), a dialogue (after
Plato), an imitation of a literary genre (including those in scripture),
a children's sermon, or anything else that occurs to you as a productive
way to engage the question. Then again, the venue also gives you an
audience of peers with which to hone your persuasive writing skills.
Even if you are brimming with creative ideas for prompt responses, take
at least four opportunities over the semester to apply that energy to
the humble paragraph. Paragraphs are the building blocks of essays, and
it takes experience to know how to identify a paragraph-sized idea and
then nurture it into a form that can help support a larger argument. Use
the forum to practice. Learn to develop a robust, 250-word unit governed
by a clear topic sentence, which is a thesis in miniature: compose a
single, well-ordered paragraph in answer to four or more discussion
prompts this term.

\subsection{The Review (Book or Article)}

A book review can facilitate critical reflection on a significant work
of biblical interpretation or theology, but note well: a book review is
not the same thing as a book report. A report simply summarizes the
contents of a book, as if the only goal were to prove that you read it,
whereas a review is a focused exercise in critical analysis and
evaluation. In very limited space, this kind of paper should first
explain the message of a book or article, and then present an assessment
of its significance. It should have the following elements:

\begin{enumerate}

\item full bibliographic details about the work under review.

\item an introductory hook (a phatic or attention-getting device).

\item a summary of the work and its arguments. You should describe the
main argument in your own words and through the judicious
use of quotes. Your aim should be to be objective (would the author
recognize your summary of their work? is it fair?) and insightful (do
you capture the work's central points?). Please avoid critical
comment at this stage.

\item an analysis and evaluation of the work, possibly through
discussion of a representative example. If the scholar's focus is
exegetical, examine a characteristic instance of biblical
interpretation. Read the biblical passage being interpreted, and ask
yourself the following sorts of questions: Is the interpretation
insightful? Does it help you understand the biblical text? Does it
include everything in the biblical text? What does it omit? Why? Are
there any problems with the interpretation? Does the biblical text aid
the scholar’s wider argument? Alternately, if the work is not especially
exegetical, consider the list of questions suggested by Northey et
al.\footnote{Northey, Anderson, and Lohr, \emph{Making Sense}, 85–86.}
Critical comments should be thoughtful and measured.

\item optionally, a brief statement of your personal response to the
work.

\item an apt conclusion. The final paragraph is often a good place to
put a thesis statement, since the reviewed work must be understood
before you can make an argument about it.

\end{enumerate}

Unless the professor or syllabus states otherwise, at least half of the
paper (50\%) should be evaluative. Mere plot summary is not required. In
the case of an assigned text, unlike a review that might appear in
print, you can assume that your audience is already somewhat familiar
with the work.

\subsection{The Exegetical Essay}

The basic task of an exegetical essay is to identify a suitable passage
from the Bible (perhaps between four and eight verses long, and not more
than ten), and to offer a reading of that text that supports an
appropriate thesis.

The biblical exegete needs a plan of attack. Unfortunately, I know of no
method that applies universally. I took a few courses on the Bible when
I was an undergraduate. In one I remember being presented with an
authoritative list of steps for exegesis – I believe there were twelve
steps in all. At the time, as a student of English Literature, the
hermeneutical program struck me as artless. It felt far too formulaic.
Now that I have looked into the matter more thoroughly, I have become
convinced that all such schemes are artificial. They might serve a
purpose for a time and a place, but they cannot guarantee excellent
results, even in the limited contexts in which they arise. This problem
becomes more obvious when one studies the history of the Bible's
interpretation. Some methods that worked for Origen or Jerome in one
situation could not be followed by Diodore or Theodore in another. And
Augustine's famous treatise on the interpretation of scripture, called
\emph{On Christian Doctrine}, is still worth studying, but it does not
resolve all the interpretive conundrums that readers of the Bible have
faced ever since. What is one to do? If you find yourself glowing with
confidence about your favourite approach to the Bible, the first step
might be to take a dose of humility. Walk through a world class
theological research library, if you get the chance, and marvel at just
how much has been written about the Bible over the centuries. If, on the
other had, you find yourself duly intimidated by the task, I commend the
steps outlined in \emph{Making Sense in Religious Studies} as a
reasonable and practical place to start.\footnote{For details on these
eight steps see Northey, Anderson, and Lohr, \emph{Making Sense},
105–112.}

\begin{enumerate}

\item Find a text of suitable length.

\item Translate the passage or read it through in multiple translations.

\item Determine the genre.

\item Conduct literary analysis.

\item Examine the historical context.

\item Examine the compositional history (when possible).

\item Consult secondary literature.

\item Iterate. Revisit the above steps.

\end{enumerate}

Note, too, that the thesis of an exegetical essay should have an organic
relationship to the text it seeks to describe. If you only find in a
passage something you already thought was there, the exercise has
failed. Practically speaking, this means that the final version of your
thesis statement may be the last thing you are able to write. However, a
lucid statement of it still belongs in the paper's introduction. Lead
off by presenting the results of your study of a biblical text, and then
take the reader through the exegetical spade work that got you there. It
can even be a virtue if, in the interest of honesty, you point out some
limits in your reading. The goal is not to override but to clarify the
text.

\subsection{The Thesis Proper}

A thesis proper, by which I mean not just a sentence but a total
argument, is often a culminating work in a degree program. I regularly
set a question that calls for a final thesis as the culminating
assignment of a course as well. It requires all the things that have
been described above: a sound thesis statement, mature and topical
supporting paragraphs, an exegetical foundation, and a competent
awareness of secondary literature. My main advice is to write and
rewrite. Leaving most of the work to the night before a deadline is no
recipe for success. Give yourself as much time as you can to revise your
work, knowing that our understanding of text, church, and world is
always a work in progress.

\section{Try the Paramedic Method}


Handout copied from - https://owl.english.purdue.edu/owl/resource/635/01/

Use the Paramedic Method (originally developed by Richard Lanham in
\emph{Revising Prose}) to edit any kind of professional writing. Editing
your professional writing using the Paramedic Method will make your
prose easier to read. Sentences that are easy to read are more
persuasive and more user-centered.

Professional writers understand the need for clear, concise prose. An
industry standard for helping workplace writers achieve user-centered,
persuasive, and clear prose is the Paramedic Method. When you use the
Paramedic Method, you will reduce your word count by eliminating
unnecessary words. The Paramedic Method also helps you activate your
sentences by eliminating passive voice and redundancies. The Paramedic
Method is an easy to learn, systematic way to make your sentences more
persuasive and more user-centered.

Follow the seven steps below to improve the readability of your sentences.

\subsection{The Paramedic Method}

\begin{enumerate}
\item Circle the prepositions (of, in, about, for, onto, into)
\item Draw a box around the “is” verb forms
\item Ask, “Where's the action?”
\item Change the “action” into a simple verb
\item Move the doer into the subject (Who's kicking whom)
\item Eliminate any unnecessary slow wind-ups
\item Eliminate any redundancies
\end{enumerate}

\subsection{Now You Try}

Use the Paramedic Method in the sentences below to practice making your
sentences more concise. After you use the Paramedic Method on these
sentences, check your results against the sentences at the bottom of
this handout.
%[Removed. See the suggested answers online.]

\begin{enumerate}
\item The point I wish to make is that the employees working at this company are in need of a much better manager of their money.
\item It is widely known that the engineers at Sandia Labs have become active participants in the Search and Rescue operations in most years.
\item After reviewing the results of your previous research, and in light of the relevant information found within the context of the study, there is ample evidence for making important, significant changes to our operating procedures.
\end{enumerate}

Example Concise Solutions:

\begin{enumerate}
\item Employees at this company need a better money manager. (Original word count: 26. New word count: 10).
\item In recent years, engineers at Sandia Labs have participated in the Search and Rescue operations. (Original word count: 24. New word count: 16).
\item After reviewing the results of your research, and within the context of the study, we find evidence supporting significant changes in our operating procedures. (Original word count: 36. New word count: 25).
\end{enumerate}


\end{document}
