% -*- program: xelatex -*-

\documentclass[11pt]{article}

% Typography
\usepackage{fontspec}
\setmainfont[Ligatures=TeX]{Arno Pro}
\setsansfont[Ligatures=TeX]{Myriad Pro}
\setmonofont[Scale=MatchLowercase]{Menlo}
\usepackage{booktabs}
\frenchspacing

\title{Winter 2015 Textbook Requisitions}
\author{Daniel R. Driver (616-226-6620 x2201 or ddriver@tyndale.ca)}
\date{Submitted to the Tyndale Bookstore on 14 October 2014}

\begin{document}

\maketitle

Please order the following textbooks for my \textbf{three} classes next semester. All
textbooks are \textbf{required} unless otherwise stated.

\section{BSTH 1013: Old Testament Scripture (66/75 students enrolled)}

\begin{description}

	\item[978-0801048852] R.\,W.\,L. Moberly.
    \emph{Old Testament Theology: Reading the Hebrew Bible as Christian Scripture}.
    Grand Rapids: Baker Academic, 2013.

	\item[978-0374529758] Abraham Joshua Heschel.
    \emph{The Sabbath: Its Meaning for Modern Man}.
    New York: Farrar, Straus and Giroux, 1951 (repr. 2005).

	\item[978-0195289602] \emph{The New Oxford Annotated Bible with Apocrypha}.
    Oxford: Oxford University Press, 2010 (4\textsuperscript{th} edition).
    If students do not already have a copy of the NRSV then they should purchase this one for this class.

\end{description}

\section{BSTH 4403: TOBITH -- Forgiveness (12/12 students enrolled)}

\begin{description}

	\item[978-0142437261]  Nathaniel Hawthorne, ed. by Thomas E. Connolly.
	\emph{The Scarlet Letter} (paperback).
	Penguin Classics, 2002.

	\item[978-0393348880] Dara Horn.
    \emph{A Guide for the Perplexed: A Novel} (paperback).
    W. W. Norton \& Company, 2014.

	\item[978-1107680203] David Konstan.
	\emph{Before Forgiveness: The Origins of a Moral Idea} (paperback).
	Cambridge University Press, 2012.

    \item[978-0385496902] Desmond Tutu.
    \emph{No Future Without Forgiveness} (paperback).
    New York: Image / Doubleday, 2000.

    \item[978-0802808615, optional] L. Gregory Jones.
    \emph{Embodying Forgiveness: A Theological Analysis}.
    Grand Rapids: Eerdmans, 1995.

\end{description}

\section{HEBR 3023: Readings in Biblical Hebrew II (5 students enrolled)}

\begin{description}

	\item[978-1932792911] Robert D. Holmstedt.
	\emph{Ruth: A Handbook on the Hebrew Text}.
	Baylor University Press, 2010.

	\item[978-0802094292] John C. Beckman.
	\emph{Williams' Hebrew Syntax, Third Edition}.
	University of Toronto Press, 2007.

\end{description}

\end{document}