\ProvidesFile{exams.tex}[2013/08/19 v1.0 -- Course policy]

\subsection{Examinations}
\label{exams}

My examination policy follows that outlined in \SecAC, part of which is
summarized below for emphasis.

\begin{enumerate}
  \item
    Midterm exams will be held as scheduled by the instructor. If you miss
    the exam for a legitimate reason, you must write the exam within the same
    number of days that you were absent from school (possibly the next day).
  \item
    Final examinations will take place during the exam period as scheduled
    by the Registrar. Students are responsible for noting the date, time and
    location of their final exam in this class. Students are also responsible
    for familiarizing themselves with the Registrar's examination policies.
  \item
    Special rules apply when midterms and finals are held, including one that
    prohibits students from leaving their seats during the final fifteen minutes
    of the exam period. See the \AC\ for full details.
%    The following rules apply to every final examination:
%    \begin{enumerate}
%      \item
%        No student is permitted to take into the examination room any materials
%        relating to the examination subject, including Bibles.
%      \item
%        No student may leave the room without permission from the proctor.
%      \item
%        No student may leave his or her seat during the final fifteen minutes.
%      \item
%        Students must not linger in the halls outside the examination rooms
%        while examinations are being written.
%      \item
%        No student will be permitted to write beyond the allotted time without
%        special permission of the Registrar (see Section~\ref{accessibility}).
%    \end{enumerate}
  \item
    Provisions exist for students who are justifiably unable to write the final
    exam at the scheduled time. See the \AC\ for details, and make arrangements
    through the Office of the Registrar.
  \item
    Normally, a final exam can only be reschedule in two circumstances:
    (a) a documented illness, or (b) a conflict with another
    exam (two at the same time, or three within 24 hours).
    \href{http://www.tyndale.ca/registrar/final-exam-schedule-and-policies}
    {Apply to the Registrar} in either case.
\end{enumerate}
