\ProvidesFile{grades.tex}[2022/01/11 v1.0 -- Course policy]

% Tutorial-style assessment, adapted from Evangeline Kozitza Dean's
% policy at Oxford, which she said was adapted from others in turn

Given the small class size this term, I have adopted a tutorial format
for \ccode.

\begin{enumerate}

	\item Each week you will write a 1000–1200 word essay responding to
	a prompt.

	\item Essays should interact thoughtfully with both primary and
	secondary sources, and should be \textbf{thesis-driven}. Your essay
	must argue a thesis, and not simply describe what you have learned
	or what others have argued. At the tutorial, you should know what
	you think about the question, and should be able to summarize the
	argument of your essay in one sentence.

	\item Reading preparation should always give priority of attention
	to the assigned primary texts. Secondary literature will be
	important in lending guidance to the essay, but scholarly opinions
	should always be assessed on the basis of how helpful they are in
	explaining the primary text.

	\item By email or Teams, please send me your essay as a Microsoft
	Word document by 4pm the day before class. Essays received on time
	will receive written feedback. Late essays are not guaranteed
	written feedback. If you do not provide an essay at all, class may
	be cancelled. Essays will not be accepted after class (with rare
	exceptions).

	\item Written feedback will be returned by email or on Teams
	following discussion in the tutorial. Marks will not be assigned to
	the essays submitted on a weekly basis. Instead, affirmation and
	redirection will be provided as needed.

	\item Select two of your best essays to revise and resubmit for a
	formal mark. Both essays must be submitted before the last day of
	class. You can opt to submit them early.

\end{enumerate}

The breakdown for the semester's total work is shown in
\autoref{grade-dist}.

\begin{table}[htbp]
  \centering
  {\lining
  \begin{tabular}{lr}
    \toprule
    Completion of All Essays      & 70\% \\
    Assessment of Selected Essays & 30\% \\
    \bottomrule
  \end{tabular}}
  \caption{Distribution of Grades}
  \label{grade-dist}
\end{table}
