% -*- program: xelatex -*-
% -*- pdf: BSTH_1013_Driver_F14 -*-

\documentclass[titlepage]{article}
% clone the necessary input files: git@github.com:danieldriver/syllabus.git
\newcommand\policy{../policy}
\newcommand\incl{../includes}
\input{\incl/variables}

\coursecode[7.0]{BSTH 1013}
\coursetitle{Old Testament Scripture}

% Previously taught as RLGS 1013 in:
%   * Fall 2008
%   * Winter 2009
%   * Fall 2009
%   * Winter 2010
%   * Fall 2010
%   * Winter 2011
% Previously taught as BSTH 1013 in:
%   * tk

\professor{Daniel R. Driver}
\phone{416-226-6620 ext. 2201}
\email{ddriver@tyndale.ca}
\officehours{Mon. \& Thur., 1:30--3:30 \PM}

\semester{Fall 2014}
\meets{Tuesdays \& Thursdays} % \meets{on}{at}{in}
      {3:45--5:05 \PM}
      {Ballyconnor 2087}
\website{classes.tyndale.ca}
\cdescription{% copy from tyndale.ca/registrar/calendar
  Survey of the redemptive story in the three major divisions of the Old
  Testament (the Law/Torah, the Prophets, and the Writings), including
  an orientation to the historical backgrounds, religious context,
  literary forms, apocryphal dimensions, prophetic elements, matters of
  canon, text, interpretation, and critical issues.

  {\itshape Note that this class is both a general studies requirement
  and a prerequisite for advanced courses in Biblical Studies \&
  Theology.}
}

\input{\incl/preamble}

\begin{document}
\input{\incl/title}

\section{Learning Outcomes}
\label{outcomes}

The learning outcomes in this course will be determined by each
student's ability to meet specific goals (learning objectives). By the
end of the course students should be able to:
  name major Old Testament people and events;
  identify representative biblical quotes by book and chapter;
  give key dates for Israel's history and summarize the succession of superpowers in the Ancient Near Eastern political theatre from the time of Egypt to Greece;
  locate a few important biblical sites on a map;
  understand the general shape of the Masoretic Text tradition and differentiate it from other canonical orders and traditions;
  recognize genres of biblical literature and cite examples from the reading;
  list the Ten Commandments in order;
  articulate multiple rationales for sabbath observance;
  defend a decision to pronounce or circumlocute the divine name;
  classify prophetic literature relative to the exile;
  report on apparent parallels, synchronisms, tensions, and contradictions in and across the Law and the Prophets;
  memorize and recite Psalm 8.

Students should also be able to identify settings in which the
scriptures of Israel are read (notably the synagogue, church, and
academy), employ terminology appropriate to these reading communities,
recognize where their own biographies and commitments place them in
relation to the Hebrew Bible/Old Testament and its uses, and monitor and
test their individual attitudes and assumptions. They should be able
to extend their awareness of the Bible's reading communities to the
Bible's long history of reception. Finally, students should be able to
infer what Jesus might have meant in speaking of ``the law of Moses, the
prophets, and the psalms'' (Luke 24:44), and begin to hear claims about
New Testament fulfilment of scripture in light of the unique voice that
the Old Testament retains along side of the New in Christian scripture.

\section{Required Texts \& Materials}
\label{texts}

All required textbooks are available in the Tyndale Bookstore. The
coursepack is available in class, directly from Dr. Driver.

\begingroup
\renewcommand{\section}[2]{}% temporarily remove the section heading
\begin{thebibliography}{Heschel}% use the longest item in the bibliography
  \bibitem[NRSV]{nrsv} \emph{The New Oxford Annotated Bible with Apocrypha}.
    Oxford: Oxford University Press, 2010 (4\textsuperscript{th}
    edition). Many serviceable translations of the Bible exist, but I
    assign the NRSV because it is a standard among biblical scholars. If
    you do not already have a copy then you must purchase one for this
    class.
  \bibitem[Heschel]{heschel} Abraham Joshua Heschel.
    \emph{The Sabbath: Its Meaning for Modern Man}. New York: Farrar,
    Straus and Giroux, 1951 (repr. 2005). Read this classic example of
    20\textsuperscript{th} century Jewish spirituality on your own, no
    later than the fourth week of class. Review it in preparation for the
    class on which it is assigned.
  \bibitem[Moberly]{moberly} R.\,W.\,L. Moberly.
    \emph{Old Testament Theology: Reading the Hebrew Bible as Christian
    Scripture}. Grand Rapids: Baker Academic, 2013. Read these eight
    essays by a leading Old Testament scholar and biblical theologian in
    parallel with (but after completing) the assigned Bible readings.
  \bibitem[OTSIC]{otsic} Daniel R. Driver.
    \emph{\ctitle\ Introductory Coursepack}. Toronto, \csemester.
    In response to the requests of many students I have compiled a pack
    of notes for my lectures. I will circulate the relevant pages before
    each class. It behooves you to gather, annotate, and study this
    material carefully.
\end{thebibliography}
\endgroup

\section{Supplementary Texts}
\label{supplementary}

Supplementary readings are listed in the bibliographies that follow each
page of notes in the coursepack. Excerpts from this literature,
ordinarily an article or a book chapter per week, will be available for
download through the course website (alternately, some may be kept on
reserve in the library). Students are not strictly required to read this
supplementary material; then again, students who choose not to read it
should not expect to get an A for the course.

Note that the required readings for this survey emphasize a selection of
primary texts from the Old Testament. Reading in the vast body of
secondary literature on the Bible is largely left for upper-division
courses. Diligent students, however, and all prospective majors, will
make a special point of reviewing the supplementary articles.

\section{Evaluation}
\label{evaluation}

\subsection{Grade Structure for \ccode}
\label{structure}

\begin{enumerate}
 \item At various points throughout the semester I will announce
   \textbf{reading quizzes}. They are designed to ensure that you have
   read the assigned material carefully, and may be administered online
   (outside of class) or on paper (in class). Online quizzes are open
   book, but they are timed and limited to a single attempt. Quizzes
   given in class are closed book, and they may not be made up in the
   case of absence.
 \item Students are to \textbf{memorize Psalm 8} in the King James
   Version (KJV) and recite it to me privately, in my office, in the
   fourth or fifth week of class. An online sign-up sheet will be posted
   to the class website in week three.
 \item A \textbf{midterm exam} will be given in class as scheduled in
   the course outline (Section~\ref{outline}). At the instructor's
   option, it may include a take-home writing component.
 \item A comprehensive \textbf{final exam} will be held during the exam
   period as schedule by the Registrar (see Section~\ref{exams}). It is
   designed to assess learning outcomes, i.e., your attainment of the
   objectives in Section~\ref{outcomes}. Test your readiness for the
   final by asking yourself how well you can perform the tasks outlined
   in those paragraphs.
\end{enumerate}

The breakdown for the semester's total work is as follows:

\begin{table}[htbp]
  \centering
  {\lining
  \begin{tabular}{lr}
    \toprule
    Reading Quizzes & 25\% \\
    Memorization    & 15\% \\
    Midterm Exam    & 30\% \\
    Final Exam      & 30\% \\
    \bottomrule
  \end{tabular}}
  \caption{Distribution of Grades}
  \label{distribution}
\end{table}

\input{\policy/grades}

\section{Policy on Assignments \& Exams}
\label{policy}

\input{\policy/academic_calendar}
\input{\policy/assignments}
\input{\policy/exams}

\section{Student Expectations \& Guidelines}
\label{expectations}

\input{\policy/academic_integrity}
\input{\policy/attendance}
\input{\policy/technology}

\input{\policy/support}

\section{Course Outline}
\label{outline}

Readings should be completed before the start of the class for which they are
assigned. Primary readings (from scripture) and required secondary texts
(Heschel and Moberly) are compulsory. Any supplementary readings that I
circulate (per Section~\ref{supplementary}) will be keyed to the session
number (listed under \textbf{\S} in Table~\ref{schedule}), and should ideally
be read before class as well. We will adhere to the schedule as closely as
possible, though I reserve the right to adjust it to suit the needs of the
class.

\setcolumncount{4} % set up \sessioncount, \unit{} and \noclass{} macros
\begin{table}[htb]
  \centering
  \begin{tabular}{>{\sessioncount.}r@{ }llr}
    \toprule
    \sessionskip{\textbf{\S}.}&\textbf{Primary Reading or Event}&\textbf{Secondary Reading}&\textbf{Date}\\
    \midrule

    \unit{Beginnings} \\

          & Psalms 8, 74, 104               & Syllabus         &  4 Sep.     \\
          
          & Genesis 1--11                   & Heschel (begin)  &  9 Sep.     \\
          & Genesis 12--36                  &                  & 11 Sep.     \\
          
          & Genesis 37--50                  &                  & 16 Sep.     \\
          & Exodus 1--6, 32--34             &                  & 18 Sep.     \\ [1ex]

    \unit{Out of Egypt} \\
          
          & Exodus 7--24                    & Moberly 3        & 23 Sep.     \\
          & Exodus 20, Deuteronomy 5        & Heschel (finish) & 25 Sep.     \\
    \reminder{\textbf{Recitation of Psalm 8} (during Dr. Driver's office hours)}{\emph{from} 25 Sep.} \\ 
          
          & Deuteronomy 1--11               & Moberly 1        & 30 Sep.     \\
          & Deuteronomy 12--26              &                  &  2 Oct.     \\
          
          & Deuteronomy 27--34              & Moberly 2        &  7 Oct.     \\ [1ex]

    \unit{In the Land} \\

          & Joshua 1--13:7, 22--24          &                  &  9 Oct.     \\
          
          & Judges 1--16, 19--21            & Moberly 4        & 14 Oct.     \\
          & 1 Samuel 1--15                  &                  & 16 Oct.     \\
          
          & \textbf{Midterm Exam} (given in class) &           & 21 Oct.     \\
    \noclass{Reading Days}                                     & 23--24 Oct. \\
    \reminder{\textbf{Take-home Essay Due} (submit PDF online)}{24 Oct.} \\

    
          & 1 Samuel 16--31, 2 Samuel 1--12 &                  & 28 Oct.     \\
          & 1 Kings 1--14                   &                  & 30 Oct.     \\
          
          & 2 Kings 17--25                  &                  &  4 Nov.     \\ [1ex]
    \unit{Latter Prophets} \\
          & Isaiah 1--12, 36--39            & Moberly 5        &  6 Nov.     \\

          & Hosea 1--14, Joel 1--3          &                  & 11 Nov.     \\
          & Amos 1--9, Obadiah, Jonah 1--4  & Moberly 6        & 13 Nov.     \\ [1ex]
          
    \unit{Wisdom \& Praise} \\

          & Job 1--11                       &                  & 18 Nov.     \\
          & Job 27--31, 38--42              & Moberly 8        & 20 Nov.     \\ 
          
          & Ecclesiastes 1--12              &                  & 25 Nov.     \\
          & Psalms 1--2, 44, 72--73, 89--90, 105--106, 150 & Moberly 7 & 27 Nov. \\ [1ex]
          
    \noclass{Reading Days}                                     & 2--3 Dec.   \\
    \reminder{\textbf{Final Exam} (as schedule by the Registrar)}{4--11 Dec.} \\
    \bottomrule
  \end{tabular}
  \caption{Schedule of Readings}
  \label{schedule}
\end{table}

See the \href{http://www.tyndale.ca/registrar/important-dates}{Registrar's
website} for a list of other important dates. The last day to add a class, or
to drop one without penalty, is ordinarily the end of the term's second week.

\section{Course Bibliography}
\label{bibliography}

An introductory bibliography is provided at the end of each page of
notes in the coursepack. Pursue this material as your interest
dictates, or if you wish to check my handling of any of the material I
present. Pay special attention to items flagged as supplementary reading
(Section~\ref{supplementary}).

\end{document}
