% Copyright (c) 2015 by Daniel R. Driver.
% !TEX encoding = UTF-8 Unicode
% !TEX TS-program = XeLaTeX

\documentclass[titlepage]{article}

% This document presumes a file structure and set of inputs that are
% available at: git@github.com:danieldriver/syllabi.git

\newcommand\policy{../policy}
\newcommand\incl{../includes}
\input{\incl/variables}

\coursecode[8.5]{BSTH 1013}
\coursetitle{Old Testament Scripture}

% Previously taught as RLGS 1013 in:
%   - Fall 2008
%   - Winter 2009
%   - Fall 2009
%   - Winter 2010
%   - Fall 2010
%   - Winter 2011 (Fall 2011 was covered by Joel Lohr in a course release)
%   - Winter 2012
%   - Fall 2012
%   - Winter 2013
% Previously taught as BSTH 1013 in:
%   - Fall 2013
%   - Winter 2014
%   - Fall 2014
%   - Winter 2015
%   - Fall 2015

\professor{Daniel R. Driver}
\phone{416-226-6620 ext. 2201}
\email{ddriver@tyndale.ca}
\officehours{Mon. \& Thur., 2:30--3:30 \PM}

\semester{Winter 2016}
\meets{Tue. \& Thur.}% \meets{on}{at}{in}
      {5:15--6:35 \PM}
      {Bayview E320}
\website{classes.tyndale.ca}
\cdescription{% copy from tyndale.ca/registrar/calendar
	Survey of the redemptive story in the three major divisions of the
	Old Testament (the Law/Torah, the Prophets, and the Writings),
	including an orientation to the historical backgrounds, religious
	context, literary forms, apocryphal dimensions, prophetic elements,
	matters of canon, text, interpretation, and critical issues.

	{\itshape Note that this class is both a general studies requirement
	and a prerequisite for advanced courses in Biblical Studies \&
	Theology.}
}% end of course description
\objectives{% recall Bloom's taxonomy: http://www.celt.iastate.edu/teaching/RevisedBlooms1.html

	The learning outcomes for this course are in part a function of each
	student's ability to meet specific objectives. By the end of the
	course students should be able to:
		name major Old Testament people and events;
		identify representative biblical quotes by book and chapter;
		give key dates for Israel's history and summarize the succession of superpowers in the Ancient Near Eastern political theatre from the time of Egypt to Greece;
		locate a few important biblical sites on a map;
		classify prophetic literature relative to the exile;
		recognize genres of biblical literature and cite examples from the reading;
		understand the general shape of the Masoretic Text tradition and differentiate it from other canonical orders;
%		list the Ten Commandments in order;
%		defend a decision to pronounce or circumlocute the divine name;
		report on parallel and divergent material across the Law and the Prophets;
		articulate multiple rationales for sabbath observance;
		memorize and recite Psalm 8.

	Students should also be able to identify settings in which the
	scriptures of Israel are read (notably the synagogue, church, and
	academy), employ terminology appropriate to these reading
	communities, recognize where their own biographies and commitments
	place them in relation to the Hebrew Bible/Old Testament and its
	uses, and monitor and test their individual attitudes and
	assumptions. They should be able to extend their awareness of the
	Bible's reading communities to the Bible's long history of
	reception. Finally, students should be able to infer what Jesus
	might have meant in speaking of ``the law of Moses, the prophets,
	and the psalms'' (Luke 24:44), and begin to hear claims about New
	Testament fulfilment of scripture in light of the unique voice that
	the Old Testament retains along side of the New in Christian
	scripture.

}% end of learning objectives

\input{\incl/preamble}

\begin{document}
\input{\incl/title}

\section{Required Texts \& Materials}
\label{texts}

All required textbooks are available in the Tyndale Bookstore. The
coursepack is available in class, directly from Dr. Driver.

\begingroup
\renewcommand{\section}[2]{}% temporarily remove the section heading
\begin{thebibliography}{Heschel}% use the longest item in the bibliography

	\bibitem[NJPS]{njps}
	Adele Berlin and Marc Zvi Brettler, eds.
    \emph{The Jewish Study Bible: Second Edition}.
    Oxford / New York: Oxford University Press, 2014.
    ISBN 978-0199978465.
%	Many serviceable translations of the Bible exist, including the NRSV
%	and ESV. The NJPS allows students in this course to better
%	appreciate the relationship of the first part of Christian Scripture
%	to the Scriptures of Israel (also called the Hebrew Bible), which is
%	one of the course's fundamental objectives. In addition, this
%	revised study Bible contains an outstanding set of introductory
%	notes and essays in a highly readable, single-column format. It is
%	required.

%	\bibitem[Heschel]{heschel} Abraham Joshua Heschel. \emph{The
%	Sabbath: Its Meaning for Modern Man}. New York: Farrar, Straus and
%	Giroux, 1951 (repr. 2005). Read this classic example of
%	20\textsuperscript{th} century Jewish spirituality on your own, no
%	later than the fourth week of class. Review it in preparation for
%	the class on which it is assigned.

	\bibitem[OTSIC]{otsic} Daniel R. Driver. \emph{\ctitle\ Introductory
	Coursepack}. Toronto, \csemester. In response to the requests of
	many students I have compiled a pack of notes for my lectures. I
	will circulate the relevant pages before each class. It behooves you
	to gather, annotate, and study this material carefully.

\end{thebibliography}
\endgroup

\section{Supplementary Texts}
\label{supplementary}

Supplementary readings are listed in the bibliographies that follow each
page of notes in the coursepack. Excerpts from this literature,
ordinarily an article or a book chapter per week, will either be made
available for download through the course website, or else be designated
from the introductory essays included in the NJPS Study Bible.

Students are not strictly required to read this material; then again,
students who choose not to read it should not expect to get an A for the
course.
%Note that the required readings for this survey emphasize a selection of
%primary texts from the Old Testament. Reading in the vast body of
%secondary literature on the Bible is largely left for upper-division
%courses.
Diligent students, and all prospective majors, should make a special
point of reviewing the designated supplementary texts.

\section{Course Outline}
\label{outline}

Readings should be completed before the start of the class for which
they are assigned. We will adhere to the schedule in
Table~\ref{schedule} (below) as closely as possible, though I reserve
the right to adjust it to suit the needs of the class.

%Readings should be completed before the start of the class for which
%they are assigned. Primary readings (from scripture) and required
%secondary texts (Heschel and Moberly) are compulsory. Any supplementary
%readings that I circulate (per Section~\ref{supplementary}) will be
%keyed to the session number (listed under \textbf{\S} in
%Table~\ref{schedule}), and should ideally be read before class as well.
%We will adhere to the schedule as closely as possible, though I reserve
%the right to adjust it to suit the needs of the class.

\setcolumncount{4}% set up \sessioncount, \unit{}, \noclass{}, and \reminder{memo}{date} macros
\begin{table}[p]% add p to put the schedule on its own page
  \centering
  \begin{tabular}{>{\sessioncount.}r@{ }llr}% make sure the column config agrees with \setcolumncount
	\toprule
	\sessionskip{\textbf{\S}.}&\textbf{Primary Reading}&\textbf{Secondary Reading}&\textbf{Date}\\
	\midrule

	\unit{Beginnings} \\

		& Psalms 8, 74, 104               & Syllabus         &  5 Jan.        \\
		& Genesis 1--3                    & P. Enns          &  7 Jan.        \\ [1ex]

		& Genesis 4--25                   &                  & 12 Jan.        \\
		& Genesis 26--50                  & J. Levenson      & 14 Jan.        \\ [1ex]

		& Exodus 1--6, 32--34             &                  & 19 Jan.        \\
		& Exodus 7--18                    & C. Mathews McGinnis  & 21 Jan.    \\ [1ex]

	\unit{Legal Traditions} \\

	\reminder{\textbf{Recitation of Psalm 8} (during Dr. Driver's office hours)}{\emph{from} 26 Jan.} \\
		& Exodus 19--24                   & D. Patrick       & 26 Jan.        \\
		& Exodus 20, Deuteronomy 5        &                  & 28 Jan.        \\ [1ex]

    	& Deuteronomy 1--11               &                  &  2 Feb.        \\
		& Deuteronomy 12--26              & B. Levinson      &  4 Feb.        \\ [1ex]

		& Deuteronomy 27--34              &                  &  9 Feb.        \\
		& \textbf{Midterm Exam} (given in class) &           & 11 Feb.        \\ [1ex]

	\noclass{Reading Week}                                   & 15--19 Feb.    \\ [1ex]

	\unit{Former Prophets} \\

		& Joshua 1--13:7, 22--24          & D. Earl          & 23 Feb.        \\
		& Judges 1--16, 19--21            &                  & 25 Feb.        \\ [1ex]

		& 1 Samuel 1--15                  &                  &  1 Mar.        \\
		& 1 Samuel 16--31, 2 Samuel 1--12 & M. Sweeney       &  3 Mar.        \\ [1ex]

		& 1 Kings 1--14                   &                  &  8 Mar.        \\
		& 2 Kings 17--25                  & O. Lipschits     & 10 Mar.        \\ [1ex]

	\unit{Latter Prophets} \\

		& Isaiah 1--12, 36--39            &                  & 15 Mar.        \\
		& Isaiah 40-54                    & B. Sommer        & 17 Mar.        \\ [1ex]

        & Hosea, Joel, Amos               &                  & 22 Mar.        \\
		& Jonah, Micah, Nahum             & E. Ben Zvi       & 24 Mar.        \\ [1ex]

	\unit{Wisdom \& Praise} \\

		& Ecclesiastes 1--12              &                  & 29 Mar.        \\
		& Psalms 1--2, 72--73, 89--90, 104--106 & M. Cameron & 31 Mar.        \\ [1ex]

	\noclass{Reading Day}                                    &  5 Apr.        \\ [1ex]
	\reminder{\textbf{Final Exam} (as schedule by the Registrar)}{6--13 Apr.} \\
	\bottomrule
  \end{tabular}
  \caption{Schedule of Readings}
  \label{schedule}
\end{table}

See the Registrar's website for a list of other
\href{http://www.tyndale.ca/registrar/important-dates}{important dates}.
The last day to add a class, or to drop one without penalty, is
ordinarily the end of the term's second week.

\section{Evaluation}
\label{evaluation}

\subsection{Grade Structure for \ccode}
\label{structure}

\begin{enumerate}

	\item At various points throughout the semester I will announce
	\textbf{reading quizzes}. They are designed to ensure that you have
	read the assigned material carefully, and may be administered online
	(outside of class) or on paper (in class). Online quizzes are open
	book, but they are timed and limited to a single attempt. Quizzes
	given in class are closed book, and they may not be made up in the
	case of absence.

	\item Students are to \textbf{memorize Psalm 8} in the King James
	Version (KJV) and recite it to me privately, in my office, in the
	fourth or fifth week of class. An online sign-up sheet will be
	posted to the class website in week three.

	\item A \textbf{midterm exam} will be given in class as scheduled in
	the course outline (Section~\ref{outline}). At the instructor's
	option, it may include a take-home writing component.

	\item A comprehensive \textbf{final exam} will be held during the
	exam period as schedule by the Registrar (see Section~\ref{exams}).
	It is designed to assess your attainment of the objectives in
	Section~\ref{objectives}. Test your readiness for the final by
	asking yourself how well you can perform the tasks outlined in those
	paragraphs.

\end{enumerate}

The breakdown for the semester's total work is shown in Table~\ref{distribution} (below).

\begin{table}[htbp]
  \centering
  {\lining
  \begin{tabular}{lr}
    \toprule
    Reading Quizzes & 30\% \\
    Memorization    & 10\% \\
    Midterm Exam    & 30\% \\
    Final Exam      & 30\% \\
    \bottomrule
  \end{tabular}}
  \caption{Distribution of Grades}
  \label{distribution}
\end{table}

\input{\policy/grades}

\section{Policy on Assignments \& Exams}
\label{policy}

\input{\policy/academic_calendar}
\input{\policy/assignments}
\input{\policy/exams}

\section{Student Expectations \& Guidelines}
\label{expectations}

\input{\policy/academic_integrity}
\input{\policy/attendance}
\input{\policy/technology}

\input{\policy/support}

\section{Course Bibliography}
\label{bibliography}

An introductory bibliography is provided at the end of each page of
notes in the coursepack. Pursue this material as your interest dictates,
or if you wish to check my handling of any of the material I present.
Pay special attention to items flagged as supplementary reading
(Section~\ref{supplementary}).

\end{document}
