% !TEX TS-program = XeLaTeX
% !TEX encoding = UTF-8 Unicode
% Copyright (c) 2014 by Daniel R. Driver. All rights reserved.

\documentclass[titlepage]{article}

\newcommand\policy{../policy}
\newcommand\incl{../includes}
\input{\incl/variables}

\coursecode[3.0-WIP]{BSTH 3143}
\coursetitle{Psalms in Interpretation}

% Previously taught in: Fall 2008, Winter 2011 as RLGS 3263 (Text &
% Interpretation): The Psalms in the Christian Tradition

\professor{Daniel R. Driver}
\phone{416.226.6620 x2201}
\email{ddriver@tyndale.ca}
\officehours{Mon. \& Thur., 1:30--3:30 \PM}

\semester{Fall 2014}
\meets{Mondays \& Thursdays}
      {11:15 \AM--12:35 \PM}
      {Ballyconnor 2083}
\website{classes.tyndale.ca}
\cdescription{% copy from tyndale.ca/registrar/calendar
  Examines the hymns of the people of Israel with regard to their
  theology and literary types of the Psalms. The arrangement of the
  Psalms and the history of reception of specific Psalms will form a
  significant portion of the course. Prerequisites: \textsc{bsth} 101,
  102, 201.
}

\input{\incl/preamble}

\begin{document}
\input{\incl/title}

\section{Learning Outcomes}
\label{outcomes}

% A Model of Learning Objectives
% Adapted from http://www.celt.iastate.edu/teaching/RevisedBlooms1.html
%
% A learning objective should contain a *subject* (a verb related to
% cognitive process) and an *object* (a noun identifying the knowledge
% or skill sought). Statements should be precise and measurable, e.g.,
% "By the end of this course, students will be able to <verb> <noun>."
%
% Anderson and Krathwohl name four *classes of knowledge* that students
% can be expected to acquire. Terms move from the concrete to the
% abstract:
%
%   1. factual           (basic elements, details, terminology)
%   2. conceptual        (interrelationship of basic elements)
%   3. procedural        (skills, methods, techniques, criteria)
%   4. metacognitive     (strategy, context and conditions, self-knowledge)
%
% Metacognitive knowledge is a special case. It concerns one's own
% "cognition and about oneself in relation to various subject matters"
% (Anderson and Krathwohl, 2001, p.44).
%
% A&K also identify 19 *cognitive processes*, arranged in six categories
% (a 2001 revision of Bloom's 1957 taxonomy) that progress from lower
% order to higher order thinking skills (from LOTS to HOTS):
%
%   1. remember
%      * recognizing     (identifying)
%      * recalling       (retrieving)
%   2. understand
%      * interpreting    (clarifying, paraphrasing, representing, translating)
%      * exemplifying    (illustrating, instantiating)
%      * classifying     (categorizing, subsuming)
%      * summarizing     (abstracting, generalizing)
%      * inferring       (concluding, extrapolating, interpolating, predicting)
%      * comparing       (contrasting, mapping, matching)
%      * explaining      (constructing models)
%   3. apply
%      * executing       (carrying out)
%      * implementing    (using)
%   4. analyze
%      * differentiating (discriminating, distinguishing, focusing, selecting)
%      * organizing      (finding coherence, integrating, outlining, parsing, structuring)
%      * attributing     (deconstructing)
%   5. evaluate
%      * checking        (coordinating, detecting, monitoring, testing)
%      * critiquing      (judging)
%   6. create
%      * generating      (hypothesizing)
%      * planning        (designing)
%      * producing       (constructing)
%
% If you reference a List of Measurable Verbs Used to Assess Learning
% Outcomes, remember that A&K reverse Bloom's 6th and 5th categories.

The Psalms of the Hebrew Bible/Old Testament have always played an
important part in the life of the church and synagogue. A major goal of
this course is therefore to gain some historical perspective on how the
Psalter has fed and informed Jewish and Christian faith in various
periods: in biblical times, Rabbinic and Patristic periods, the Middle
Ages, the Reformation, the Enlightenment, and finally the early and late
modern periods. Informed by recent research into the shape and shaping
of the Psalter we will also consider the arrangement of this great
anthology.

The course meets twice a week, which facilitates two main foci. Mondays
are dedicated to hermeneutical and historical factors involved in
reading the Psalter in light of long reception. Thursdays allow us to
put theory into practice by reading particular psalms in the context of
their reception. By the end of the course students should be able to:
interpret at least four distinct periods in the reception of the
Psalter; analyze key differences between ancient and modern
interpreters, and a variety of Jewish and Christian interpreters;
produce a sustained discussion of a psalm that interacts with its text
and interpretation; recite at least ten verses of a psalm; respond
creatively to a psalm in a way that demonstrates awareness of its impact.

\section{Required Texts \& Materials}
\label{texts}

All required texts are available for purchase in the Tyndale Bookstore.

\begingroup
\renewcommand{\section}[2]{}% temporarily remove the section heading
\begin{thebibliography}{Gillingham}% use the longest item in the bibliography
  \bibitem[Gillingham]{gillingham}
    Susan Gillingham. \emph{Psalms Through the Centuries: Volume One}.
    \href{http://bbibcomm.net/}{Blackwell Bible Commentaries}. Oxford:
    Blackwell, 2008. Repr., Chichester: Wiley-Blackwell, 2012.
  \bibitem[Wenham]{wenham}
    Gordon J. Wenham. \emph{Psalms as Torah: Reading Biblical Song
    Ethically}. Studies in Theological Interpretation. Grand Rapids:
    Baker Academic, 2012.
\end{thebibliography}
\endgroup

\section{Supplementary Texts}
\label{supplementary}

The following articles or book chapters represent a range of scholarly
and theological interest in the Psalms. They will either be available
for download through the course website, or kept on reserve in the
library. Students are not strictly required to read the supplementary
material; then again, students who choose not to read it should not
expect to get an A for the course.

\begin{enumerate}
 \item Katharine Dell, “\href{http://ezproxy.mytyndale.ca:2048/login?url=http://www.oxfordhandbooks.com/view/10.1093/oxfordhb/9780199204540.001.0001/oxfordhb-9780199204540-e-4}{Psalms},” pages 37--51 in M. Lieb et al., eds., \emph{The Oxford Handbook of the Reception History of the Bible} (Oxford: Oxford University Press, 2011).
 \item James Kugel, “The Psalms of David,” pages 458–473 in \emph{How to Read the Bible: A Guide to Scripture, Then and Now} (New York/Toronto: Free Press, 2007).
 \item Rolf Rendtorff, “The Psalms of David: David in the Psalms,” pages 53–64 in P. Flint and P.~Miller, eds., \emph{The Book of Psalms} (Leiden: Brill, 2005).
 \item Hermann Gunkel, “The Religion of the Psalms,” pages 134–167 in \emph{Water for a Thirsty Land} (Minneapolis: Fortress, 2001). German original published in 1922.
 \item Hans-Joachim Kraus, “The Psalms in the New Testament,” pages 177–203 in \emph{Theology of the Psalms} (Minneapolis: Augsburg, 1986). German original published in 1979.
 \item Brevard Childs, “Psalm 8 in the Context of the Christian Canon,” pages 151–163 in \emph{Biblical Theology in Crisis} (Philadelphia: Westminster, 1970).
 \item John O’Keefe, “‘A Letter that Killeth’: Toward a Reassessment of Antiochene Exegesis, or Diodore, Theodore and Theodoret on the Psalms,” \emph{Journal of Early Christian Studies} 8/1 (2000): 83–104.
 \item Jonathan Magonet, “Through Rabbinic Eyes: Psalm 23,” pages 47–61 in \emph{A Rabbi Reads the Psalms} (2nd ed.; London: SCM, 2004).
 \item Gerald Wilson, “Shaping the Psalter: A Consideration of Editorial Linkage in the Book of Psalms,” pages 72–82 in J.\,C. McCann, ed., \emph{The Shape and Shaping of the Psalter} (JSOTSup 159; Sheffield: Sheffield Academic Press, 1993).
 \item J. Clinton McCann, “Books I–III and the Editorial Purpose of the Hebrew Psalter,” pages 93–107 in J.\,C. McCann, ed., \emph{The Shape and Shaping of the Psalter} (JSOTSup 159; Sheffield: Sheffield Academic Press, 1993).
 \item Gerald Sheppard, “Theology and the Book of Psalms,” \emph{Interpretation} 46 (1992): 143–155.
 \item Erhard Gerstenberger, “Theologies in the Book of Psalms,” pages 603–625 in P. Flint and P. Miller, eds., \emph{The Book of Psalms} (Leiden: Brill, 2005).
\end{enumerate}

\section{Evaluation}
\label{evaluation}

\subsection{Grade Structure for \ccode}
\label{structure}

% Please consider the following structure in your course. Evaluation
% should be clearly linked to Learning Outcomes.
%   - Some form of meaningful evaluation should occur during the first 4
%     weeks of the course; **all students should (and first-year
%     students must) receive an indication of their performance in the
%     first half of the course.**
%   - **Plan your assignments so that each can be returned to students
%     before the next is due.**
%   - Most courses should have a rigorous final exam of 2--3 hours
%     duration. Some upper-year courses may not require a final,
%     depending on pedagogical design and assessment strategy. **Final
%     exams should be appropriately demanding in both breadth and depth
%     to assess accurately the achievement of learning outcomes.**
%   - **No assignments should be due in the last week of classes; final
%     examinations will be scheduled only by the Registrar’s Office.**

\begin{enumerate}
 \item Each week of class will typically begin with a \textbf{reading
   quiz}. These are designed to ensure that you have read the assigned
   material carefully. Quizzes given in class may not be made up in the
   case of absence, though in special cases they may be taken in advance.
 \item Students are to \textbf{memorize 10 verses of a psalm} and recite
   it to me privately, in my office, before the end of tenth week of
   class. Any psalm is allowed unless you have memorized it before
   (Psalm 8 is therefore excluded for many).
 \item Students must \textbf{creatively represent one psalm} in the class
   immediately following that psalm’s workshop (e.g., Psalm 1 at the
   start of Week 3). You can and should use visuals, audio---or whatever
   you can find or create yourself. Be inventive! The only conditions
   are (a) that you explain / demonstrate a connection with the text
   studied and (b) that your presentation last between 5 and 10 minutes.
 \item The last day of each week (Thursdays unless the only class is on
   Monday) will be devoted to a \textbf{seminar-style discussion} of
   individual psalms. Each student will be assigned a commentator for a
   period of 3 weeks, and they are responsible to report on that
   commentator and bring their insight to bear on the discussion. How
   should you prepare?
	\begin{enumerate}
	 \item Read the seminar text closely and carefully. Read it several
       times. Look for distinctive language, themes and images, and stay
       alert to intertextual connections between the main passage and
       other biblical literature. Jot down your observations.
	 \item Consult your designated commentary. It should be read
       carefully, but after you have got a sense for the psalm on its
       own. One good approach might be to read the psalm twice, make
       some preliminary notes, and then to read your commentator before
       filling out the notes.
	 \item Notes will not necessarily be collected, although I may ask to
       see them if there is any doubt about the adequacy of your
       preparation. Remember that you will be called upon to represent
       your unique commentator’s views to the class.
	\end{enumerate}
 \item In lieu of a final exam students are to \textbf{compose an essay}
   on one of the psalms we workshop. Consult all the perspectives
   brought to bear in the seminar on the psalm of your choice, and
   incorporate as many as are expedient for your discussion. The aim is
   to dig deeper into one psalm. This will be facilitated in part by the
   preliminary researches of your classmates. You will need to read more
   widely on your own, however; the seminar is only a starting point.
   You are also expected to develop a strong thesis, and to interact
   significantly with the secondary reading. The final paper will be due
   at the start of the exam period (TBA).

\end{enumerate}

The breakdown for the semester's total work is as follows:

\begin{table}[htbp]
  \centering
  \begin{tabular}{lr}
    \toprule
    Reading Quizzes         & 30\% \\
    Psalm Memorization      & 10\% \\
    Creative Representation & 10\% \\
    Seminar Contributions   & 20\% \\
    Final Paper             & 30\% \\
    \bottomrule
  \end{tabular}
  \caption{Distribution of Grades}
  \label{distribution}
\end{table}

\input{\policy/grades}

\section{Policy on Assignments \& Exams}
\label{policy}

\input{\policy/academic_calendar}
\input{\policy/assignments}
%\input{\policy/exams}

\section{Student Expectations \& Guidelines}
\label{expectations}

\input{\policy/academic_integrity}
\input{\policy/attendance}
\input{\policy/technology}

\input{\policy/support}

\section{Course Outline}
\label{outline}

Readings should be completed before the first class of the week in which
they are assigned. Research into seminar texts and any supplementary
readings that I circulate (see Section~\ref{supplementary}) should be
completed before the last class of their week. We will adhere to the
schedule as closely as possible, though I reserve the right to adjust it
to suit the needs of the class.

\newcommand\Yhwh{\textsc{Yhwh}}
\newcommand\rarr{\char"2192\hspace*{0.5pt}}

\setcolumncount{5} % set up \sessioncount, \unit{} and \noclass{} macros
\begin{table}[htb]% add p to put the schedule on its own page
  \centering
  \begin{tabular}{>{\sessioncount.}r@{ }lllr}
    \toprule
    \sessionskip{\textbf{Wk}.}
          &\textbf{Seminar Text}
                         &\textbf{Gillingham}
                                        &\textbf{Wenham} &\textbf{Date}\\
    \midrule
          & Psalm 150    & Introduction & Introduction   & 4 Sep.      \\
          & Psalm 1      & pp. 5--27    & Ch. 1          & 8, 11 Sep.  \\
          & Psalm 2      & pp. 28--55   & Ch. 2          & 15, 18 Sep. \\
          & Psalm 19     & pp. 55--76   & Ch. 3          & 22, 25 Sep. \\
          & Psalm 23     & pp. 77--104  & Ch. 4          & 29 Sep., 2 Oct. \\
          & Psalm 24     & pp. 104--130 & Ch. 5          & 6, 9 Oct.   \\
    \noclass{Thanksgiving}                               & 13 Oct.     \\
          & Psalm 51     & pp. 131--162 &                & 16 Oct.     \\
          & Psalm 73     & pp. 163--191 &                & 20 Oct.     \\
    \noclass{Reading Days}                               & 23--24 Oct. \\
          & Psalm 88     & pp. 192--215 & Ch. 6          & 27, 30 Oct. \\
          & Psalm 90     & pp. 215--241 & Ch. 7          & 3, 6 Nov.   \\
          & Psalm 110    & pp. 242--266 & Ch. 8          & 10, 13 Nov. \\
          & Psalm 116    & pp. 266--290 & Ch. 9          & 17, 20 Nov. \\
          & Psalm 137    & pp. 290--312 & Ch. 10         & 24, 27 Nov. \\
          & Psalm 145    &              &                & 1 Dec.      \\
    \noclass{Reading Days}                               & 2--3 Dec.   \\
    \bottomrule
  \end{tabular}
  \caption{Schedule of Readings}
  \label{schedule}
\end{table}

See the \href{http://www.tyndale.ca/registrar/important-dates}{%
Registrar's website} for a list of other important dates. Generally, the
last day to add or drop a class without penalty is the end of the second
week of class.

\section{Course Bibliography}
\label{bibliography}

For the weekly Psalms seminar, students should focus on a commentator
from the list below and give a short (5 minute) overview of the
interpretation of the Psalm in question. Be sure to work with four
different commentators over the semester, from at least two different
major periods. (For those with the language skills, registering notes on
one of the Hebrew or Greek can be one of the four options.) The aim is
to gain as much insight into the message of the Psalm by close attention
to text, translation and commentary.

\begin{enumerate}

 \item Ancient Versions
  \begin{enumerate}

	\item John R. Kohlenberger, III, ed., \emph{The Comparative Psalter: Hebrew-Greek-English} (Oxford: Oxford University Press, 2007) [Ref BS 1419.K645]. Very useful for our purposes, but not to be mistaken as a critical edition or a full account of ancient versions.

	\item The Septuagint/Old Greek (LXX/OG) is available in \href{http://ccat.sas.upenn.edu/ioscs/editions.html}{two main editions}, each with major and minor editions. A. Rahlfs produced the Göttingen Septuagint's \emph{editio maior} of \emph{Psalmi cum Odis} in 1931 (3rd ed., 1979). The Rahlfs-Hanhart \emph{editio minor} of the entire OG Bible is available in our library's reference section [Ref BS741.R3 2006].

	\item Vulgate/Jerome: Biblia Sacra Latina [Ref BS 75 1800 and \href{https://www.biblegateway.com/versions/?action=getVersionInfo&vid=4}{online}].

	\item Targum: \emph{The Aramaic Bible, Vol. 16: The Targum of the Psalms} (trans. David M. Stec; Collegeville, Minn: Liturgical Press, 2004) [Ref BS 709 .2 .A72 v.16 2004]. Also, \href{http://targum.info/targumic-texts/targum-psalms/}{Edward Cook's translation is available online}.

  \end{enumerate}
 \item Early Church / Synagogue
  \begin{enumerate}

	\item John Chrysostom, \emph{Commentary on the Psalms} (trans. R.\,C. Hill; 2 vols.; Brookline, Mass.: Holy Cross Orthodox Press, 1998) [BS 1430.3.J63 1998].

	\item Augustine, \emph{Expositions of the Psalms} (trans. M. Boulding; 6 vols.; Hyde Park, N.Y.: New City Press, 2000--2004) [BR 65.A5 E53 1990 pt.III/15--20]. Older English translations of \emph{Enarrationes in Psalmos} appear in the Ancient Christian Writers series (trans. S. Hebgin, F. Corrigan; Westminster, Md., Newman Press, 1960--) and in \href{http://www.ccel.org/ccel/schaff/npnf108.toc.html}{P. Schaff's NPNF translation, first printed 1847--57 and now online}. For the Latin original see Corpus Scriptorum Ecclesiasticorum Latinorum (CSEL), vols. 93--95.

	\item Diodore of Tarsus, \emph{Commentary on Psalms 1--51} (trans. R.\,C. Hill; Atlanta: SBL, 2005) [\href{http://tyndale.worldcat.org/oclc/191953419}{various e-books}].

	\item Theodoret of Cyrus, \emph{Commentary on the Psalms} (trans. R.\,C. Hill; 2 vols; Washington, DC: Catholic University of America Press, 2000--2001) [BS 1430.T54 and \href{http://tyndale.worldcat.org/oclc/41649596}{various e-books}].

	\item Theodore of Mopsuestia, \emph{Commentary on Psalms 1--81} (trans. R.\,C. Hill; Atlanta: SBL, 2006) [BS 1430.53.T4813 2006 and an \href{http://ezproxy.mytyndale.ca:2048/login?url=http://hdl.handle.net/2027/heb.07760.0001.001}{e-book}].

	\item Cassiodorus, \emph{Explanation of the Psalms} (trans. P.G. Walsh; New York: Paulist Press, 1990--1991) [BR 60.A3 v.51--53 1990].

	\item Midrash Tehillim / \emph{Midrash on the Psalms, Translated from the Hebrew and Aramaic} (trans. William G. Braude; 2 vols.; New Haven: Yale University Press, 1959) [BM 517.T52 E5 1959].

  \end{enumerate}
 \item Medieval
  \begin{enumerate}

	\item Aquinas, \emph{Postilla super Psalmos / Commentary on the Psalms} (1272--1273). A Latin / English parallel edition for (most of) Psalms 1--54, a work in progress ed. by Stephen Loughlin, is \href{http://www4.desales.edu/~philtheo/loughlin/ATP/}{online as part of the Aquinas Translation Project}. See also: Thomas Ryan, \emph{Thomas Aquinas as Reader of the Psalms} (Notre Dame: University of Notre Dame Press, 2000) [BX 2350.65.R93 2000].

	\item \emph{Rashi’s Commentary on Psalms} (trans. Mayer I. Gruber; Leiden: Brill, 2004) [BS 1429.R3713 2007]. % See also: Hermann Hailperin, \emph{Rashi and the Christian Scholars} (Pittsburgh: University of Pittsburgh Press, 1963).

  \end{enumerate}
 \item Reformation Era
  \begin{enumerate}

	\item Desiderius Erasmus (1466--1536): \emph{Expositions of the Psalms} (Collected Works of Erasmus, Vol. 63--65; Toronto: University of Toronto Press, 1997, 2005, 2010) [\href{http://ezproxy.mytyndale.ca:2048/login?url=http://site.ebrary.com/lib/tyndale/docDetail.action?docID=10226282}{CWE 63: Pss 1, 2, 3, 4}; \href{http://ezproxy.mytyndale.ca:2048/login?url=http://site.ebrary.com/lib/tyndale/docDetail.action?docID=10218753}{CWE 64: Pss 88, 22, 28, 33}; CWE 65: Pss 38, 83, 14].

	\item Martin Luther (1483--1546): \emph{Werke}, 35 = \emph{Luther’s Works}, 10--14 [BR 330.E5P4 1955]. See also: J.S. Preus, \emph{From Shadow to Promise: Old Testament Interpretation from Augustine to the Young Luther} (Cambridge, Mass.: Belknap, 1969) [BR 333.5.B5 P7 1969].

	\item John Calvin (1509--1564): \emph{Commentary on the Psalms} (1557--, ET 1839--). All of Calvin's commentaries are available online, in English translation, at the \href{}{Christian Classics Ethereal Library (CCEL)}. Psalms: \href{http://www.ccel.org/ccel/calvin/calcom08.html}{1--35}, \href{http://www.ccel.org/ccel/calvin/calcom09.html}{36--66}, \href{http://www.ccel.org/ccel/calvin/calcom10.html}{67--92}, \href{http://www.ccel.org/ccel/calvin/calcom11.html}{93--119}, \href{http://www.ccel.org/ccel/calvin/calcom12.html}{119--150} [see also BS 1429.C34 1840 and Ref BS 485.C245 1979 vols. 4–6].

  \end{enumerate}
 \item Early Modern / Critical
  \begin{enumerate}

	\item E.\,W. Hengstenberg, \emph{Commentary on the Psalms} (trans. P. Fairbairn and J. Thomson; 3 vols.; Edinburgh: T\&T Clark, 1851--1858)
	[BS 1430.H46 and \href{http://tyndale.worldcat.org/oclc/21399344}{various e-books}].

	\item Franz Delitzsch, \emph{Biblical Commentary on the Psalms} (trans. Franics Bolton; 3 vols; Grand Rapids: Eerdmans, 1952)
	[BS 1430.D44 1952 and \href{http://tyndale.worldcat.org/oclc/677380663}{various e-books}].

	\item C.\,H. Spurgeon, \emph{The Treasury of David: An Expository and Devotional Commentary on the Psalms} (Nashville: T. Nelson, 1984)
	[BS 1430.S6 1984, 1976, 1940 and \href{http://www.spurgeon.org/treasury/treasury.htm}{online}].

	\item C.\,A. Briggs, \emph{A Critical and Exegetical Commentary on the Book of Psalms} (2 vols.; Edinburgh: T\&T Clark, 1906--1907)
	[Ref BS 491.I6 v.19a–19b, BS 1430 .B7 and \href{https://archive.org/details/criticalexegetic02briguoft}{online}].

	\item Hermann Gunkel, \emph{Die Psalmen} (Göttingen: Vandenhoeck \& Ruprecht, 1929). Any German readers? I can lend out my copy. See also: \emph{The Psalms: A Form-critical Introduction} (Philadelphia: Fortress, 1967) [BS 1430.2.G7813 1967].

  \end{enumerate}
 \item Modern
  \begin{enumerate}

	\item H.-J. Kraus, \emph{Psalms: A Continental Commentary} (trans. H.C. Oswald; 2 vols; Minneapolis: Fortress Press, 1988--1993) [BS 1430.3 .K725].

	\item A.\,A. Anderson, \emph{The Book of Psalms} (2 vols.; Grand Rapids: Eerdmans, 1981) [BS 1430.3.A63 1972; Ref BS 491.2.N48 v19 1981].

	\item M.\,J. Dahood, \emph{Psalms I, II, and III} (3 vols.; Garden City, NY: Doubleday, 1956--1970) [Ref BS 491 .2 .A52 v.19a 1965; … v.19b 1968; … v.19c 1970]. Stacks also.

	\item Word Commentary Series: P. Craigie, \emph{Psalms 1--50} (Waco, TX: Word Books, 1983) [Ref BS 491 .2 .W67 v.19 1983]; M. Tate, \emph{Psalms 51--100} (Dallas, TX: Word Books, 1990) [Ref BS 491 .2 .W67 v.20 1990]; L. Allen, \emph{Psalms 101--50} (rev. ed.; Nashville: Thomas Nelson, 2002) [Ref BS 491 .2 .W67 v.21 2002]. Stacks also.

	\item F.-L. Hossfeld and E. Zenger, \emph{Psalms 2: A Commentary on Psalms 51--100} (Hermeneia; Minneapolis: Fortress, 2005) [Ref BS 491.2.H47 v.19b 2005] and idem, \emph{Psalms 3: A Commentary on Psalms 101--150} (Hermeneia; Minneapolis: Fortress Press, 2011) [Ref BS 491.2.H47 v.19c 2011].

	\item Craig Broyles, \emph{Psalms} (New International Biblical Commentary 11; Peabody, Mass.: Hendrickson, 1999) [Ref BS 491.2.N47 v.11 1999 and BS 1430.3.B75 1999].

	\item You may nominate a commentator of your own, subject to my approval.

  \end{enumerate}
\end{enumerate}

\noindent Other Notable Literature

\begin{itemize}

	\item Ancient Christian Commentary on Scripture, OT Vols. 7--8:
	  Craig A. Blaising and Carmen Hardin, eds., \emph{Psalms 1--50} (Downers Grove: InterVarsity Press, 2008) [Ref BS 491.2.A523 v.7 2008] and
	  Quentin F. Wesselschmidt and Thomas C. Oden, eds., \emph{Psalms 51--150} (Downers Grove: InterVarsity Press, 2007) [Ref BS 491.2.A523 v.8 2007].

	\item H. Attridge and M. Fassler, eds., \emph{Psalms in Community: Jewish and Christian Textual, Liturgical, and Artistic Traditions} (Leiden: Brill, 2004) [BS 1435.P74 2003].

	\item Willaim Holladay, \emph{The Psalms through Three Thousand Years: Prayerbook of a Cloud of Witnesses} (Minneapolis: Fortress, 1993) [BS 1430.3.H65 1993].

	\item Susan Gillingham, \emph{Psalms Through the Centuries, Vol. 1} (Oxford: Blackwell, 2008) offers an \href{http://www.blackwellpublishing.com/pdf/9780631218555.pdf}{expanded online bibliography (PDF)}. See also \href{http://www.bbibcomm.net/}{www.bbibcomm.net}. Volume 2 has not yet appeared, but see her \emph{A Journey of Two Psalms: The Reception of Psalms 1 and 2 in Jewish and Christian Tradition} (Oxford: Oxford University Press, 2013) [BS 1430.52.G547 2013] and \emph{Jewish and Christian Approaches to the Psalms: Conflict and Convergence} (Oxford: Oxford University Press, 2013) [BS 1430.52.J49 2013].

	\item Sæbø, HB/OT: For help with specific periods and commentators in biblical reception history see Magne Sæbø et al., eds., \emph{Hebrew Bible, Old Testament: The History of its Interpretation} (3 vols.; Göttingen : Vandenhoeck \& Ruprecht, 1996--2015).

\end{itemize}

\end{document}
