% Copyright (c) 2015 by Daniel R. Driver.
% !TEX encoding = UTF-8 Unicode
% !TEX TS-program = XeLaTeX

\documentclass[titlepage]{article}

% This document presumes a file structure and set of inputs that are
% available at: git@github.com:danieldriver/syllabi.git

\newcommand\policy{../policy}
\newcommand\incl{../includes}
\input{\incl/variables}

\coursecode[2.1]{BSTH 3213}
\coursetitle{The Ten Commandments}

% Taught as RLGS 3113 in:
%   - Winter 2012
% Taught as BSTH 3213 in:
%   - Winter 2015

\professor{Daniel R. Driver}
\phone{416-226-6620 ext. 2201}
\email{ddriver@tyndale.ca}
\officehours{Mon. \& Thur., 2:30--3:30 \PM}

\semester{Winter 2016}
\meets{Mon. \& Wed.}% \meets{on}{at}{in}
      {8:15--9:35 \AM}
      {Bayview G310}
\website{classes.tyndale.ca}
\cdescription{% copy from tyndale.ca/registrar/calendar
	Explores the legal and cultic context of the Ten Commandments. The
	course will also address the significance of the Decalogue in
	Christian interpretation and the history of civilization. Students
	will become familiar with current scholarship on the Ten
	Commandments, especially in the context of Christian discourse.
	Prerequisites: \textsc{bsth} 101, 102, 201.
}% end of course description
\objectives{% recall Bloom's taxonomy: http://www.celt.iastate.edu/teaching/RevisedBlooms1.html
By the end of the course students should be able to:
	name the Ten Commandments in order;
	locate at least three biblical versions of the Ten Commandments;
	differentiate biblical versions by their contents;
	interpret each of the Commandments in their immediate literary context;
	integrate an understanding of the Ten Commandments with a broader view of biblical law;
	summarize the way different religious traditions count to Ten;
	compare the ways the Commandments have been interpreted in history;
	identify, evaluate, and report on contemporary connections with at least one of the Ten Commandments.
}% end of learning objectives

\input{\incl/preamble}

\begin{document}
\input{\incl/title}

\section{Required Texts \& Materials}
\label{texts}

All required textbooks are available in the Tyndale Bookstore.

\begingroup
\renewcommand{\section}[2]{}% temporarily remove the section heading
\begin{thebibliography}{3}% use the longest item in the bibliography

	\bibitem{Greenman-Larsen} Jeffrey P. Greenman and Timothy Larsen, eds.
	\emph{The Decalogue through the Centuries: From the Hebrew Scriptures to Benedict XVI}.
	Louisville: Westminster John Knox Press, 2012.
	ISBN 978-0664234904.

	\bibitem{Coogan} Michael Coogan.
    \emph{The Ten Commandments: A Short History of an Ancient Text}.
    New Haven: Yale University Press, 2014.
    ISBN 978-0300178715.

	\bibitem{VanHarn} Roger E. Van Harn, ed.
	\emph{The Ten Commandments for Jews, Christians, and Others}.
	Grand Rapids: Wm. B. Eerdmans, 2007.
	ISBN 978-0802829658.

\end{thebibliography}
\endgroup

\section{Supplementary Texts}
\label{supplementary}

All supplementary textbooks are held in reserve in the Tyndale library.
Other supplementary materials may be provided through the course website.

\begingroup
\renewcommand{\section}[2]{}% temporarily remove the section heading
\begin{thebibliography}{3}% use the longest item in the bibliography

	\bibitem{Braaten-Seitz} Carl E. Braaten and Christopher R. Seitz, eds.
	\emph{I Am the Lord Your God: Christian Reflections on the Ten Commandments}.
	Grand Rapids: Eerdmans, 2005
	ISBN 978-0802828125.

	\bibitem{Miller} Patrick Miller.
    \emph{The Ten Commandments: Interpretation: Resources for the Use of Scripture in the Church}.
    Louisville: Westminster John Knox, 2009.
    ISBN 978-0664230555.

\end{thebibliography}
\endgroup

\section{Course Outline}
\label{outline}

Readings should be completed before the start of the class for which
they are assigned. We will adhere to the schedule in
Table~\ref{schedule} (below) as closely as possible, though I reserve
the right to adjust it to suit the needs of the class.

%Readings should be completed before the start of the class for which
%they are assigned. Primary readings (from scripture) and required
%secondary texts (Heschel and Moberly) are compulsory. Any supplementary
%readings that I circulate (per Section~\ref{supplementary}) will be
%keyed to the session number (listed under \textbf{\S} in
%Table~\ref{schedule}), and should ideally be read before class as well.
%We will adhere to the schedule as closely as possible, though I reserve
%the right to adjust it to suit the needs of the class.

\setcolumncount{4}% set up \sessioncount, \unit{}, \noclass{}, and \reminder{memo}{date} macros
\begin{table}[htbp]% add p to put the schedule on its own page
  \centering
  \begin{tabular}{>{\sessioncount.}r@{ }llr}% make sure the column config agrees with \setcolumncount
	\toprule
	\sessionskip{\textbf{Week.}}&\textbf{Primary Focus}&\textbf{Secondary Reading}&\textbf{Dates}\\
	\midrule
		& Introductions  & Syllabus, Coogan ix--49, TAL 332     &   4, 6 Jan. \\
		& Introductions  & Coogan 50--93, Miller 1--12          & 11, 13 Jan. \\
		& First Word     & Coogan 94--141, Van Harn 1--21       & 18, 20 Jan. \\
		& Second Word    & Van Harn 23--45, Miller 13--62       & 25, 27 Jan. \\
		& Third Word     & Van Harn 47--67, Greenman 1--27      &   1, 3 Feb. \\
		& Fourth Word    & Van Harn 69--85, Greenman 29--46     &  8, 10 Feb. \\ [1ex]
	\noclass{Reading Week}                                      & 15--19 Feb. \\ [1ex]
		& Fifth Word     & Van Harn 87--111, Greenman 47--66    & 22, 24 Feb. \\
		& Sixth Word     & Van Harn 113--134, Greenman 67--96   & 29 Feb, 2 Mar. \\
		& Seventh Word   & Van Harn 135--156, Greenman 97--133  &  7, 9  Mar. \\
		& Eighth Word    & Van Harn 157--178, Greenman 135--167 & 14, 16 Mar. \\
		& Ninth Word     & Van Harn 179--198, Greenman 169--196 & 21, 23 Mar. \\
		& Tenth Word     & Van Harn 199--220, Greenman 197--227 & 28, 30 Mar. \\
	\reminder{\textbf{Final Exam} (as schedule by the Registrar)}{6--13 Apr.} \\
	\bottomrule
  \end{tabular}
  \caption{Schedule of Readings}
  \label{schedule}
\end{table}

See the Registrar's website for a list of other
\href{http://www.tyndale.ca/registrar/important-dates}{important dates}.
The last day to add a class, or to drop one without penalty, is
ordinarily the end of the term's second week.

\section{Evaluation}
\label{evaluation}

\subsection{Grade Structure for \ccode}
\label{structure}

\begin{enumerate}

	\item At various points throughout the semester I will announce
	\textbf{reading quizzes}. They are designed to ensure that you have
	read the assigned material carefully, and may be administered online
	(outside of class) or on paper (in class).

	\item Working in groups of two or three, students are to make a
	\textbf{creative presentation} on one of the Ten Commandments in the
	week in which that Commandment is under investigation. Generally
	this will take place on Wednesdays.

	\item A \textbf{review essay} on Coogan's \emph{The Ten
	Commandments} will be due at the start of the first class after
	reading week (22 February).

	\item A comprehensive \textbf{final paper} will give students an
	opportunity to explore one of the Ten Commandments in detail. It
	should be 10--12 pages in length and is due at the start of the
	final exam period. Students must present at 5 minute summary of
	their thesis to the rest of the class during the exam period.

\end{enumerate}

The breakdown for the semester's total work is shown in Table~\ref{distribution} (below).

\begin{table}[htbp]
  \centering
  {\lining
  \begin{tabular}{lr}
    \toprule
    Reading Quizzes & 25\% \\
    Presentations   & 15\% \\
    Review Essay    & 25\% \\
    Final Paper     & 35\% \\
    \bottomrule
  \end{tabular}}
  \caption{Distribution of Grades}
  \label{distribution}
\end{table}

\input{\policy/grades}

\section{Policy on Assignments \& Exams}
\label{policy}

\input{\policy/academic_calendar}
\input{\policy/assignments}
\input{\policy/exams}

\section{Student Expectations \& Guidelines}
\label{expectations}

\input{\policy/academic_integrity}
\input{\policy/attendance}
\input{\policy/technology}

\input{\policy/support}

\section{Course Bibliography}
\label{bibliography}

In addition to the required and supplementary texts listed above, see
especially: Henning Graf Reventlow and Yair Hoffman, eds.,
\emph{Decalogue in Jewish and Christian Tradition} (Library of Hebrew
Bible/Old Testament Studies; New York: T\&T Clark, 2010), which is
\href{http://ezproxy.mytyndale.ca:2048/login?url=http://search.ebscohost.com/login.aspx?direct=true&db=e000xna&AN=369752&site=ehost-live&scope=site}{available online}.

\end{document}
