% Copyright (c) 2015 by Daniel R. Driver.
% !TEX encoding = UTF-8 Unicode
% !TEX TS-program = XeLaTeX

\documentclass[titlepage]{article}

% This document presumes a file structure and set of inputs that are
% available at: git@github.com:danieldriver/syllabi.git

\newcommand\policy{../policy}
\newcommand\incl{../includes}
\input{\incl/variables}

\coursecode[1.0]{BSTH 4403}
\coursetitle[Topics in Biblical Theology]{Forgiveness}

\professor{Daniel R. Driver}
\phone{416.226.6620 x2201}
\email{ddriver@tyndale.ca}
\officehours{Mon. \& Wed., 1:30--3:30 \PM}

\semester{Winter 2015}
\meets{Mondays \& Wednesdays}% \meets{on}{at}{in}
      {3:45--5:05 \PM}
      {Ballyconnor 2082}
\website{classes.tyndale.ca}
\cdescription{% copy from tyndale.ca/registrar/calendar

	A seminar style course involves the advanced study of a particular
	topic or figure in biblical theology that will change from year to
	year. It can be taken more than once for credit, provided that the
	topics are different. Students will be expected to contribute to the
	seminar by doing research and presenting the results to the seminar.
	Prerequisites: \textsc{bsth} 101, 102, 201 and 270.

}% end of course description

\input{\incl/preamble}

\begin{document}
\input{\incl/title}

\section{Learning Outcomes}
\label{outcomes}

The basic goal of this course is to understand the current and historic
significance of forgiveness. By the end of the semester students should
be able to:
	define forgiveness;
	identify meaningful instances where it appears in art, literature,
	the Bible, theology, religion, politics, and other discourse;
	interpret and analyze such instances;
	compare and differentiate a variety of idioms for forgiveness,
	including ancient and modern, Jewish and Christian, religious and
	therapeutic, and so on;
	evaluate the utility of forgiveness and, where appropriate,
	criticize invocations of it that are maudlin, sentimental, or
	possibly even unethical;
	construct or explain models for the practice of forgiveness;
	produce a fine and well-supported thesis on forgiveness.

\section{Required Texts \& Materials}
\label{texts}

All required textbooks are available in the Tyndale Bookstore.

\begingroup
\renewcommand{\section}[2]{}% temporarily remove the section heading
\begin{thebibliography}{Hawthorne}% use the longest item in the bibliography

	\bibitem[Hawthorne]{hawthorne} Nathaniel Hawthorne. \emph{The
	Scarlet Letter}. Ed. Thomas E. Connolly. New York: Penguin Classics,
	2002.

	\bibitem[Horn]{horn} Dara Horn. \emph{A Guide for the Perplexed: A
	Novel}. New York: W. W. Norton \& Company, 2014.

    \bibitem[Jones]{jones} L. Gregory Jones. \emph{Embodying
    Forgiveness: A Theological Analysis}. Grand Rapids: Eerdmans, 1995.

	\bibitem[Konstan]{konstan} David Konstan. \emph{Before Forgiveness:
	The Origins of a Moral Idea}. Cambridge: Cambridge University Press,
	2012.

    \bibitem[Tutu]{tutu} Desmond Tutu. \emph{No Future Without
    Forgiveness}. New York: Image, 2000.

\end{thebibliography}
\endgroup

\section{Supplementary Texts}
\label{supplementary}

Students must have access to a Bible. In some weeks it will be the
primary object of study, while in others it will serve as a resource. I
recommend \emph{The New Oxford Annotated Bible with Apocrypha: New
Revised Standard Version} (Oxford: Oxford University Press, 2010) if you
need to acquire one. Many serviceable English translations of the Bible
exist, but the NRSV is a standard among biblical scholars. For this
class the ESV and NJPS are acceptable alternatives.

Early in the semester we will watch and discuss the documentary
\emph{Forgiving Dr. Mengele} (2006, dir. Bob Hercules and Cheri Pugh),
about Auschwitz survivor Eva Mozes Kor. I have asked the library to
acquire a copy of the DVD.

Articles and book chapters from the vast literature on forgiveness (see
Section~\ref{bibliography} for a start) may be recommended and placed on
the course website as the semester progresses. Within the first week
please make a special point to read an old mystery story and a famous
interview: G.\,K. Chesterton's ``The Chief Mourner of Marne,'' from
\emph{The Secret of Father Brown} (1927, repr. in \emph{The Father Brown
Omnibus} [New York: Dodd, Mead, 1951]); and Jacques Derrida's ``On
Forgiveness,'' either in Michael Hughes' 2001 translation \cite{Der01}
or the French original,
\href{http://hydra.humanities.uci.edu/derrida/siecle.html}{``Le Siècle
et le pardon''} (\emph{Le Monde des Débats} 9 [1999], repr. in \emph{Foi
et savoir, suivi de Le Siècle et le pardon} [Paris: Seuil, 2000]).

% See Mitchell Petersen's class at McMaster: http://socserv.socsci.mcmaster.ca/danahol/777/

\section{Evaluation}
\label{evaluation}

\subsection{Grade Structure for \ccode}
\label{structure}

\begin{enumerate}

	\item Each week of class will typically begin with a \textbf{reading
	quiz}. These are designed to ensure that you have read the assigned
	material carefully, and will frequently set a jumping-off point for
	seminar discussions. Quizzes may not be made up in the case of
	absence, though in special cases they may be taken in advance.

	\item Each week, after the Monday class but before 10 \AM\ on
	Wednesday, you are to post a brief (200 word) response to a prompt
	on the Moodle \textbf{discussion forum} (see \ref{mytyndale}). If
	quizzes gauge comprehension, the forum provides an opportunity to
	critique or construct knowledge, and to share or probe experiences.
	Aim to take risks. Be creative, thoughtful, honest, courteous, and
	punctual. If you have time before the class on Wednesdays, read and
	comment on the posts of your classmates. In the first weeks at least
	I will score posts on a scale of 0 to 3.

	\item In week 6 students are to present a \textbf{case study} to the
	class. In 12 minutes you must report on and analyze a specific
	instance of forgiveness in art, literature, film, history, theology,
	philosophy, or public discourse. Use half your time for description
	and summary, and half for analysis and critique. Presentations will
	be evaluated for the quality of the selection, and the depth of
	analysis. I will model the exercise with \cite{horn} (my selection;
	for other ideas see the first and last chapters of \cite{jones}, or
	the bibliography below [\ref{bibliography}]). Answer questions for
	your case like: how is forgiveness understood? how is it deployed?
	how meaningful is it?

	\item A comprehensive \textbf{final paper} is due at the start of
	the exam period as schedule by the Registrar (see
	Section~\ref{exams}). Write an essay entitled ``On Forgiveness''
	that explores relevant themes from the course. Bolster course
	readings and discussion with your own research. The final paper
	should be at least 12 pages, not including a bibliography of at
	least 12 articles or book chapters (a source per page on average).
	Be prepared to submit a draft for \textbf{peer review} on the last
	day of class, and to read a 1,000 word excerpt from your final
	submission in the exam period.

\end{enumerate}

The breakdown for the semester's total work is as follows:

\begin{table}[htbp]
  \centering
  {\lining
  \begin{tabular}{lr}
    \toprule
    Reading Quizzes & 20\% \\
    Forum Posts     & 20\% \\
    Case Study      & 15\% \\
    Peer Review     &  5\% \\
    Final Paper     & 40\% \\
    \bottomrule
  \end{tabular}}
  \caption{Distribution of Grades}
  \label{distribution}
\end{table}

\input{\policy/grades}

\section{Policy on Assignments \& Exams}
\label{policy}

\input{\policy/academic_calendar}
\input{\policy/assignments}
%\input{\policy/exams}
\subsection{Examinations}
\label{exams}

My examination policy follows that outlined in \SecAC; however, much of
the policy does not apply in this class because it requires a final
paper in lieu of a comprehensive exam.
\href{http://www.tyndale.ca/registrar/final-exam-schedule-and-policies}
{Apply to the Registrar} if an extension is required due to a documented
illness or a conflict with another exam (more than three in 24 hours).

\section{Student Expectations \& Guidelines}
\label{expectations}

\input{\policy/academic_integrity}
\input{\policy/attendance}
\input{\policy/technology}

\input{\policy/support}

\section{Course Outline}
\label{outline}

Readings should be completed before the start of the week for which they
are assigned. We will adhere to the schedule in Table~\ref{schedule} as
closely as possible, though I reserve the right to adjust it to suit the
needs of the class.

\setcolumncount{4}% set up \sessioncount, \unit{}, \noclass{}, and \reminder{memo}{date} macros
\begin{table}[htb]% add p to put the schedule on its own page
  \centering
  \begin{tabular}{>{\sessioncount.}r@{ }llr}% make sure the column config agrees with \setcolumncount
    \toprule
    \sessionskip{\textbf{Wk}.}&\textbf{Topic}&\textbf{Reading (chapters)}&\textbf{Date}\\
    \midrule
    & False Forgiveness         & Chesterton, Derrida                  &   5, 7 Jan.   \\
    & Credible Forgiveness?     & Konstan 1, Jones 2                   & 12, 14 Jan.   \\
    & Before Forgiveness        & Konstan 2–3                          & 19, 21 Jan.   \\
    & OT Ritual and Prayer      & Konstan 4, 1 Kings 8                 & 26, 28 Jan.   \\
    & Forgiveness in Genesis?   & Genesis 25–50                        &   2, 4 Feb.   \\
    & \textbf{Case Studies} \& a Novel & Horn (all)                    &  9, 11 Feb.   \\ [1ex]
    \noclass{Reading Week}                                             & 16--20 Feb.   \\ [1ex]
    & Jesus and Forgiveness     & Mark 2; Luke 7, 15; Matt 18; Jones 7 & 23, 25 Feb.   \\
    & ``Our Father'' in the Church & Origen, Gregory, Ephraim, etc.    &   2, 4 Mar.   \\
    & Medieval Forgiveness      & Konstan 5, TBA                       &  9, 11 Mar.   \\
    & Puritan Forgiveness       & Konstan 6, Hawthorne (all)           & 16, 18 Mar.   \\
    & Tutu's Social Theology    & Tutu (all)                           & 23, 25 Mar.   \\
    & Practicing Forgiveness    & Jones 4–6                            &     30 Mar.   \\
    \reminder{\textbf{Peer Review} (bring a significant draft to the last class)}{1 Apr.} \\ [1ex]
    \noclass{Reading Days}                                             & 6--7 Apr.     \\
    \reminder{\textbf{Final Paper} (due at start of the exam period, TBA)}{8--15 Apr.} \\
    \bottomrule
  \end{tabular}
  \caption{Schedule of Readings}
  \label{schedule}
\end{table}

See the Registrar's website for a list of other
\href{http://www.tyndale.ca/registrar/important-dates}{important dates}.
The last day to add a class, or to drop one without penalty, is
ordinarily the end of the term's second week.

\section{Course Bibliography}
\label{bibliography}

In addition to various introductory articles on ``Forgiveness'' in the
\emph{Oxford Encyclopedia of Bible \& Theology} (OEBT),
\emph{Encyclopedia of the Bible \& its Reception} (EBR), \emph {Religion
Past \& Present} (RPP = RGG), and \emph{Anchor Bible Dictionary} (ABD),
refer to the following titles.

\begingroup
\renewcommand{\section}[2]{}% temporarily remove the section heading
\begin{thebibliography}{99}

\bibitem{And09} Anderson, Gary A. \textit{Sin: A History}. New Haven: Yale University Press, 2009.
\bibitem{Bas07} Bash, Anthony. \textit{Forgiveness and Christian Ethics}. Cambridge/New York: Cambridge University Press, 2007.
\bibitem{Bas13} ———. “Did Jesus Discover Forgiveness?” \textit{Journal of Religious Ethics} 41/3 (2013): 382--399.
\bibitem{Bod06} Boda, Mark, and Gordon T. Smith. \textit{Repentance in Christian Theology}. Collegeville, Minn.: Liturgical Press, 2006.
\bibitem{Der01} Derrida, Jacques. \textit{On Cosmopolitanism and Forgiveness}. Trans. Michael Hughes. London/New York: Routledge, 2001.
\bibitem{Gre83} Greenberg, Moshe. \textit{Biblical Prose Prayer as a Window to the Popular Religion of Ancient Israel}. Berkeley: University of California Press, 1983.
\bibitem{Gri07} Griswold, Charles L. \textit{Forgiveness: A Philosophical Exploration}. Cambridge/New York: Cambridge University Press, 2007.
\bibitem{GriKon12} ———, and David Konstan. \textit{Ancient Forgiveness: Classical, Judaic, and Christian}. Cambridge/New York: Cambridge University Press, 2012.
\bibitem{Hag12} Hägerland, Tobias. \textit{Jesus and the Forgiveness of Sins: An Aspect of His Prophetic Mission}. Cambridge/New York: Cambridge University Press, 2012.
\bibitem{Har03} Harrison, James R. \textit{Paul’s Language of Grace in Its Graeco-Roman Context}. Tübingen: Mohr Siebeck, 2003.
\bibitem{Hof94} Hofius, Otfried. “Jesu Zuspruch der Sündenvergebung: Exegetische Erwägungen zu Mk 2,5b.” \textit{Jahrbuch für Biblische Theologie} 9 (1994): 125--143.
\bibitem{Hol12} Holmgren, Margaret. \textit{Forgiveness and Retribution: Responding to Wrongdoing}. Cambridge/New York: Cambridge University Press, 2012.
\bibitem{Jan05} Jankélévitch, Vladimir. \textit{Forgiveness}. Chicago: University of Chicago Press, 2005.
\bibitem{Jon95} Jones, L. Gregory. \textit{Embodying Forgiveness: A Theological Analysis}. Grand Rapids, Mich.: Eerdmans, 1995.
\bibitem{JonMus10} ———, and Célestin Musekura. \textit{Forgiving as We’ve Been Forgiven: Community Practices for Making Peace}. Downers Grove, Ill.: IVP Books, 2010.
\bibitem{Kon10} Konstan, David. \textit{Before Forgiveness: The Origins of a Moral Idea}. Cambridge/New York: Cambridge University Press, 2010.
\bibitem{Lam02} Lamb, Sharon, and Jeffrie G. Murphy. \textit{Before Forgiving: Cautionary Views of Forgiveness in Psychotherapy}. Oxford/New York: Oxford University Press, 2002.
\bibitem{Lui03} Luijten, Eric. \textit{Sacramental Forgiveness as a Gift of God: Thomas Aquinas on the Sacrament of Penance}. Leuven: Peeters, 2003.
\bibitem{Mai94} Maier, Johann. “Sühne und Vergebung in der jüdischen Liturgie.” \textit{Jahrbuch für Biblische Theologie} 9 (1994): 145--171.
\bibitem{Mou98} Moule, C. F. D. \textit{Forgiveness and Reconciliation: And Other New Testament Themes}. London: SPCK, 1998.
\bibitem{Mus10} Musekura, Célestin. \textit{An Assessment of Contemporary Models of Forgiveness}. New York: P. Lang, 2010.
\bibitem{Pet12} Pettigrove, Glen. \textit{Forgiveness and Love}. Oxford: Oxford University Press, 2012.
\bibitem{Ram11} Ramelli, Ilaria. “Unconditional Forgiveness in Christianity? Some Reflections on Ancient Christian Sources and Practices.” In \textit{The Ethics of Forgiveness: A Collection of Essays}, ed. Christel Fricke, 30--48. London/New York: Routledge, 2011.
\bibitem{Sch02} Schimmel, Solomon. \textit{Wounds Not Healed By Time: The Power of Repentance and Forgiveness}. Oxford/New York: Oxford University Press, 2002.
\bibitem{Tut99} Tutu, Desmond. \textit{No Future Without Forgiveness}. New York: Doubleday, 1999.
\bibitem{TutAbr04} ———, and Douglas Abrams. \textit{God Has a Dream: A Vision of Hope for Our Time}. New York: Doubleday, 2004.
\bibitem{Vol05} Volf, Miroslav. \textit{Free of Charge: Giving and Forgiving in a Culture Stripped of Grace}. Grand Rapids, Mich.: Zondervan, 2005.

\end{thebibliography}
\endgroup

\end{document}
