% Copyright (c) 2015 by Daniel R. Driver.
% !TEX encoding = UTF-8 Unicode
% !TEX TS-program = XeLaTeX

\documentclass[titlepage]{article}

% This document presumes a file structure and set of inputs that are
% available at: git@github.com:danieldriver/syllabi.git

\newcommand\policy{../policy}
\newcommand\incl{../includes}
\input{\incl/variables}

\coursecode[1.0-WIP]{BSTH 4403: Topics in Biblical Theology}
\coursetitle[Cross-listed as \textsc{bsth} 3153: Writings]{Ecclesiastes}

\professor{Daniel R. Driver}
\phone{416.226.6620 x2201}
\email{ddriver@tyndale.ca}
\officehours{Mon. \& Wed., 2:30--3:30 \PM}

\semester{Fall 2015}
\meets{Fridays}% \meets{on}{at}{in}
      {8:15--11:05 \AM}
      {Bayview G205}
\website{classes.tyndale.ca}
\cdescription{% copy from tyndale.ca/registrar/calendar

	\textsc{bsth} 4403: A seminar style course involves the advanced
	study of a particular topic or figure in biblical theology that will
	change from year to year. It can be taken more than once for credit,
	provided that the topics are different. Students will be expected to
	contribute to the seminar by doing research and presenting the
	results to the seminar. Prerequisites: \textsc{bsth} 101, 102, 201
	and 270.

	\textsc{bsth} 3153: Survey of especially the wisdom literature of
	the Old Testament, which may cover Job, Proverbs, Ecclesiastes and
	Song of Songs and should address the role of wisdom in Israelite
	religion and culture. Comparison will be made with wisdom texts in
	the Apocrypha and Ancient Near East. Other texts from the Writings
	may also be included. Prerequisites: \textsc{bsth} 101, 102, 201.

}% end of course description

\input{\incl/preamble}

\begin{document}
\input{\incl/title}

\section{Learning Outcomes}
\label{outcomes}

% A Model of Learning Objectives
% Adapted from http://www.celt.iastate.edu/teaching/RevisedBlooms1.html
%
% A learning objective should contain a *subject* (a verb related to
% cognitive process) and an *object* (a noun identifying the knowledge
% or skill sought). Statements should be precise and measurable, e.g.,
% "By the end of this course, students will be able to <verb> <noun>."
%
% Anderson and Krathwohl name four *classes of knowledge* that students
% can be expected to acquire. Terms move from the concrete to the
% abstract:
%
%   1. factual           (basic elements, details, terminology)
%   2. conceptual        (interrelationship of basic elements)
%   3. procedural        (skills, methods, techniques, criteria)
%   4. metacognitive     (strategy, context and conditions, self-knowledge)
%
% Metacognitive knowledge is a special case. It concerns one's own
% "cognition and about oneself in relation to various subject matters"
% (Anderson and Krathwohl, 2001, p.44).
%
% A&K also identify 19 *cognitive processes*, arranged in six categories
% (a 2001 revision of Bloom's 1957 taxonomy) that progress from lower
% order to higher order thinking skills (from LOTS to HOTS):
%
%   1. remember
%      * recognizing     (identifying)
%      * recalling       (retrieving)
%   2. understand
%      * interpreting    (clarifying, paraphrasing, representing, translating)
%      * exemplifying    (illustrating, instantiating)
%      * classifying     (categorizing, subsuming)
%      * summarizing     (abstracting, generalizing)
%      * inferring       (concluding, extrapolating, interpolating, predicting)
%      * comparing       (contrasting, mapping, matching)
%      * explaining      (constructing models)
%   3. apply
%      * executing       (carrying out)
%      * implementing    (using)
%   4. analyze
%      * differentiating (discriminating, distinguishing, focusing, selecting)
%      * organizing      (finding coherence, integrating, outlining, parsing, structuring)
%      * attributing     (deconstructing)
%   5. evaluate
%      * checking        (coordinating, detecting, monitoring, testing)
%      * critiquing      (judging)
%   6. create
%      * generating      (hypothesizing)
%      * planning        (designing)
%      * producing       (constructing)
%
% If you reference a List of Measurable Verbs Used to Assess Learning
% Outcomes, remember that A&K reverse Bloom's 6th and 5th categories.

The learning outcomes for this course are in part a function of each
student's ability to meet specific objectives. By the
end of the course students should be able to:
	list biblical books classified with the Writings (in the Tanak) and wisdom literature;
	understand differences in the way this literature is classified;
	give examples of extra-biblical parallels to wisdom literature;
	locate Ecclesiastes relative to other Solomonic literature;
	recognize quotes from Ecclesiastes by chapter;
	name major commentators on Ecclesiastes, ancient and modern;
	report on specific commentators verbally, to the rest of the class;
	articulate interpretive options in reading Ecclesiastes;
	defend their own preferred readings in writing, with detailed textual support.

\section{Required Texts \& Materials}
\label{texts}

All required textbooks are available in the Tyndale Bookstore.

\begingroup
\renewcommand{\section}[2]{}% temporarily remove the section heading
\begin{thebibliography}{Christianson}% use the longest item in the bibliography

	\bibitem[Johnson]{Johnson} Samuel Johnson, ed. by Thomas Keymer.
	\emph{The History of Rasselas, Prince of Abissinia} (new edition).
	Oxford / New York: Oxford University Press, 2009.
	ISBN 978-0199229970.

	\bibitem[Christianson]{Christianson} Eric S. Christianson.
    \emph{Ecclesiastes Through the Centuries} (paperback).
    Chichester, West Sussex: Wiley-Blackwell, 2012.
	ISBN 978-0470674918.

	\bibitem[Dell]{Dell} Katharine Dell.
	\emph{Interpreting Ecclesiastes: Readers Old and New}.
	Winona Lake, Indiana: Eisenbrauns, 2013.
	ISBN 978-1575062815.

\end{thebibliography}
\endgroup

\section{Supplementary Texts}
\label{supplementary}

Students must have access to a Study Bible. I recommend \emph{The New
Oxford Annotated Bible with Apocrypha: New Revised Standard Version}
(Oxford University Press, 2010) or \emph{The Jewish Study Bible: Second
Edition} (Oxford University Press, 2014) if you need to acquire one.
Many serviceable English translations of the Bible exist, but the NRSV
and NJPS are standard among biblical scholars. For this class the ESV is
an acceptable alternative.

Articles and book chapters from the vast literature on Ecclesiastes in
reception, and in the context of the Writings and wisdom literature, may
be recommended and placed on the course website as the semester
progresses. Students are encouraged to pursue secondary literature on
their own as well.

\section{Evaluation}
\label{evaluation}

\subsection{Grade Structure for BSTH 4403/3153}% \ccode doesn't work with the cross-listing
\label{structure}

\begin{enumerate}

	\item Each class will typically begin with a \textbf{reading quiz}.
	These are designed to ensure that you have read the assigned
	material carefully, and will frequently set a jumping-off point for
	seminar discussions. Quizzes may not be made up in the case of
	absence, though in special cases they may be taken in advance.

	\item The last part of each class will be devoted to a
	\textbf{seminar-style discussion} of one chapter of Ecclesiastes.
	Each student will be assigned a commentator for a period of 3 weeks,
	and they are responsible to report on that commentator and bring
	their insight to bear on the discussion. How should you prepare?

	\begin{enumerate}

		\item Read the seminar text closely and carefully. Look for
		distinctive language, themes and images, and stay alert to
		intertextual connections between the main passage and other
		biblical literature. Jot down your observations.

		\item Consult your designated commentary. It should be read
		after you have got a sense for the chapter on its own. One good
		approach might be to read the chapter through twice, making some
		preliminary notes, and then to read your commentator and fill
		out your preliminary notes.

		\item Notes will be collected near the end of the semester, and
		I may ask to see them sooner if there is any doubt about the
		adequacy of your preparation. Remember that you are the resident
		authority on your designated commentator.

	\end{enumerate}

	\item In weeks 7 and 8 students are to present a \textbf{case study}
	to the class. In 12 minutes you must report on and analyze a
	specific instance of the reception of Ecclesiasted in art,
	literature, film, history, theology, philosophy, or public discourse
	(3153 students may use Johnson's \emph{Rasselas} as their case
	study). Use half your time for description and summary, and half for
	analysis and critique. Presentations will be evaluated for the
	quality of the selection, and the depth of analysis.

	\item A comprehensive \textbf{final paper} is due at the start of
	the exam period as schedule by the Registrar (see
	Section~\ref{exams}).

	\begin{enumerate}

		\item For \textbf{4403} students are to write an exegetical
		analysis of one chapter of Ecclesiastes. In 16--20 pages, these
		papers must advance a thesis about the text and must
		demonstrate, through careful citation, a thorough awareness of
		relevant commentary and scholarly literature.

		\item For \textbf{3153} students must give a more general
		account of Ecclesiastes either in the context of the Writings or
		of wisdom literature. In 10--12 pages, these papers must cite
		assigned textbooks and other literature as appropriate, and
		should make plentiful reference to the text of Ecclesiastes.

		\item The instructor may set deadlines for drafts in the second
		part of the semester, and may host a peer review or offer bonus
		points for visits to the writing centre. All studens in this
		class should be prepared to read a 1,000 word excerpt from your
		final submission in the exam period.

	\end{enumerate}

\end{enumerate}

The breakdown for the semester's total work is as follows:

\begin{table}[htbp]
  \centering
  {\lining
  \begin{tabular}{lr}
    \toprule
    Reading Quizzes        & 30\% \\
    Case Study             & 10\% \\
    Seminar Contributions  & 30\% \\
    Final Paper            & 30\% \\
    \bottomrule
  \end{tabular}}
  \caption{Distribution of Grades}
  \label{distribution}
\end{table}

\input{\policy/grades}

\section{Policy on Assignments \& Exams}
\label{policy}

\input{\policy/academic_calendar}
\input{\policy/assignments}
\input{\policy/exams}

\section{Student Expectations \& Guidelines}
\label{expectations}

\input{\policy/academic_integrity}
\input{\policy/attendance}
\input{\policy/technology}

\input{\policy/support}

\section{Course Outline}
\label{outline}

Readings should be completed before the start of the class for which
they are assigned. We will adhere to the schedule as closely as
possible, though I reserve the right to adjust it to suit the needs of
the class.

\setcolumncount{4}% set up \sessioncount, \unit{}, \noclass{}, and \reminder{memo}{date} macros
\begin{table}[htb]% add p to put the schedule on its own page
  \centering
  \begin{tabular}{>{\sessioncount.}r@{ }llr}% make sure the column config agrees with \setcolumncount
	\toprule
	\sessionskip{\textbf{\S}.}&\textbf{Seminar Text}&\textbf{Secondary Reading}&\textbf{Date}\\
	\midrule
	& Ecclesiastes \thesession & Christianson 17--86, 87--155             & 11 Sept. \\
	& Ecclesiastes \thesession & Christianson 156--163, Dell 9--36        & 18 Sept. \\
	& Ecclesiastes \thesession & Christianson 164--179, Dell 37--56       & 25 Sept. \\
	& Ecclesiastes \thesession & Christianson 180--183, Keymer on Johnson &  2 Oct.  \\
	& Ecclesiastes \thesession & Christianson 183--185, Johnson Ch 1--9   &  9 Oct.  \\
	& Ecclesiastes \thesession & Christianson 184--187, Johnson Ch 10--19 & 16 Oct.  \\
	\noclass{Reading Day}                                                 & 23 Oct.  \\
	& Ecclesiastes \thesession & Christianson 188--201 + Case Studies     & 30 Oct.  \\
	& Ecclesiastes \thesession & Christianson 201--205 + Case Studies     &  6 Nov.  \\
	& Ecclesiastes \thesession & Christianson 206--215, Dell 59--67       & 13 Nov.  \\
	& Ecclesiastes \thesession & Christianson 216--224, Dell 68--75       & 20 Nov.  \\
	& Ecclesiastes \thesession & Christianson 225--246, Dell 76--83       & 27 Nov.  \\
	& Ecclesiastes \thesession & Christianson 247--263, Dell 84--95       &  4 Dec.  \\
	\reminder{\textbf{Final Exam} (as schedule by the Registrar)}{9--16 Dec.}        \\
	\bottomrule
  \end{tabular}
  \caption{Schedule of Readings}
  \label{schedule}
\end{table}

See the Registrar's website for a list of other
\href{http://www.tyndale.ca/registrar/important-dates}{important dates}.
The last day to add a class, or to drop one without penalty, is
ordinarily the end of the term's second week.

\section{Course Bibliography}
\label{bibliography}

Refer to the detailed bibliographies in the back of \cite{Christianson}
and \cite{Dell}.

\end{document}
