% Copyright (c) 2018 by Daniel R. Driver.
% !TEX encoding = UTF-8 Unicode
% !TEX TS-program = XeLaTeX

\documentclass[titlepage]{article}

% This document presumes a file structure and set of inputs that are
% available at: git@github.com:danieldriver/syllabi.git

\newcommand\policy{../policy}
\newcommand\incl{../includes}
\input{\incl/variables}

%\onlinetrue % \Int{true}{false}
\coursecode[3.1.1]{HB 2201}
\coursetitle[Hebrew Bible]{Beginning Biblical Hebrew I}

% Taught as HEBR 2013 in:
%   - Fall 2009
%   - Fall 2011
%   - Fall 2013
%   - Fall 2015
% Taught as HB 2201 in:
%   - Fall 2018

\professor{Daniel R. Driver}
\phone{902-425-7051}
\email{ddriver@astheology.ns.ca}
\officehours{Thursdays, 12:30--2:00 \PM}

\semester{Fall Term 2018}
\meets{Thursdays}% \meets{on}{at}{in}
      {2:00--4:30 \PM}
      {Classroom 3}
\website{danieldriver.com}
\cdescription[none. The course is required for HB 2202 and advanced biblical Hebrew]{% copy from the current Academic Calendar; [] for prereqs
	An introduction to the basic principles of biblical Hebrew with
	emphasis on morphology, phonology, and syntax, this course is for
	students who want to study the Old Testament in Hebrew. Students
	will learn basic Hebrew grammar, develop a rudimentary biblical
	Hebrew vocabulary, and begin to read the Hebrew Bible with one eye
	on the window it opens into ancient Israel and another on its
	historic role as as scripture in Judaism and Christianity. This
	course is suitable preparation for further study in religion,
	theology, or classics. (It is open to undergraduate and graduate
	students from other universities. Please contact the AST Registrar
	to enroll as a Letter of Permission student.)
}% end of course description
\objectives{% recall Bloom's taxonomy: http://www.celt.iastate.edu/teaching/RevisedBlooms1.html
	The basic goal of this course is to become proficient in the
	rudiments of biblical Hebrew. The introductory course is designed
	for two semesters of study, and it is presumed that students will
	take the course for the entire academic year. In the first semester
	students will learn everything from the alphabet to the basics of
	Hebrew nouns and verbs. In the second semester the emphasis will
	fall on less regular paradigms (learned inductively) and more
	complicated syntax. The steady acquisition of vocabulary will be
	emphasized across both semesters.

	Language learning is hard work. It can also be fun and gratifying.
	To aid in the enjoyment, we will sing songs together, memorize and
	recite passages of scripture, and assist one another in a variety of
	ways as we undertake the necessary drills and repetitions.
}% end of learning objectives

\input{\incl/preamble}

\begin{document}
\input{\incl/title}

  \section{Learning Objectives}
  \label{objectives}

  \edobject

\section{Required Texts \& Materials}
\label{texts}

The following texts are required. Students are strongly encouraged to
purchase their own copies.

\begingroup
\renewcommand{\section}[2]{}% temporarily remove the section heading
\begin{thebibliography}{BBH}% use the longest item in the bibliography

    \bibitem[BBH]{bbh}
    John A. Cook and Robert D. Holmstedt.
    \emph{Beginning Biblical Hebrew: A Grammar and Illustrated Reader}.
    Grand Rapids: Baker Academic, 2013. ISBN 978-0801048869. A helpful
    set of study aids are available \href{http://www.bakerpublishinggroup.com/books/beginning-biblical-hebrew/5629/students/esources}{online at bakeracademic.com}.

    \bibitem[TM]{tm}
    Takamitsu Muraoka.
    \emph{A Biblical Hebrew Reader: With an Outline Grammar}.
    Leuven: Peeters, 2017. ISBN 978-9042934900.

    \bibitem[BHS]{bhs}
    \emph{Biblia Hebraica Stuttgartensia}.
    Stuttgart: Deutsche Bibel\-ge\-sell\-schaft, 1997. ISBN 978-1598561630.
    A paperback edition, marketed to students, is also available.
    Students will be asked to have a criticial edition of the Hebrew
    Bible by the start of the Winter semester. The instructor will
    provide photocopies in the interim.

\end{thebibliography}
\endgroup

\section{Supplementary Texts}
\label{supplementary}

The following reference works are worth owning and consulting.
\cite{rlgs} in particular contains sound advice on core skills like
reading religious texts, writing essays and reviews, revising essays,
making oral presentations, and learning languages.

\begingroup
\renewcommand{\section}[2]{}% temporarily remove the section heading
\begin{thebibliography}{Making Sense}% use the longest item in the bibliography

	\bibitem[Making Sense]{rlgs} Northey, Margot, Bradford A. Anderson, and Joel N. Lohr.
	\emph{Making Sense in Religious Studies: A Student's Guide to Research and Writing}.
	3rd ed. Toronto: Oxford University Press, 2019. ISBN 978-0199026838.

	\bibitem[SBL2]{sbl2} Collins, Billie Jean, et al.
	\emph{The SBL Handbook of Style}.
	2nd ed. Atlanta: SBL Press, 2014. ISBN 978-1589839649. See the free
	\href{https://www.sbl-site.org/assets/pdfs/pubs/SBLHSsupp2015-02.pdf}{Student Supplement}.

\end{thebibliography}
\endgroup

\section{Course Outline}
\label{outline}

We will adhere to the schedule in \autoref{schedule} as closely as
possible, though the professor reserves the right to adjust it to suit
the needs of the class.

\setcolumncount{4}% set up \sessioncount, \unit{}, \noclass{}, and \reminder{memo}{date} macros
\begin{table}[htbp]% set to `p' to put the schedule on its own page
  \centering%\addfontfeature{ItalicFont=SBLBibLit}
  \begin{tabular}{@{}r<{.}@{ }llr}
    \toprule
    \bfseries L & \textbf{BBH Grammar Lesson} & \textbf{TM} & \textbf{Due Date} \\
    \midrule
    1   & \texthebrew{שׁלום}, The Consonants                          & \S1   & 13 Sept. \\
    2   & The Vowels                                                 & & \\
    3   & \texthebrew{שׁוא} (Shəva)                                   & & \\
    4   & \texthebrew{דגשׁ} (Dagesh)                                  & & \\ [1ex]
    5   & Subject Pronouns: Singular                                 & \S3–4 & 20 Sept. \\
    7   & Copular Clauses                                            & & \\
    6   & Nouns: Singular                                            & & \\ [1ex]
    8   & The Article and the Interrogative \texthebrew{ה}           & \S5–7 & 27 Sept. \\
    9   & \texthebrew{ל} of Possession: Singular                     & & \\
    r-1 & \texthebrew{מקרא א} (Reading 1)                            & & \\ [1ex]
    10  & Nouns: Plural and Dual                                     & \S8   & 4 Oct. \\
    11  & Subject Pronouns: Plural                                   & & \\ [1ex]
    12  & \texthebrew{ישׁ} and \texthebrew{אין}                        & \S9–10a & 11 Oct. \\
    13  & Conjunction \texthebrew{ו} and Prepositions \texthebrew{בּ},
         \texthebrew{כּ}, \texthebrew{ל}, \texthebrew{מן}                & & \\ [1ex]
    14  & \texthebrew{שׁאלות} (Questions)                             & & 18 Oct. \\
    r-2 & \texthebrew{מקרא ב} (Genesis 3\texthebrew{א})              & & \\
    \sessionskip{\rarr} & \textbf{Midterm Exam} (last half of class) & & \\ [1ex]
    \noclass{AST Fall Term Break}                                    & 25 Oct.  \\ [1ex]
    15  & Verbs: A Preview                                           & \S11 & 1 Nov. \\
    16  & \texthebrew{קל} Perfect Conjugation: Singular              &  & \\ [1ex]
    17  & \texthebrew{ל} of Possession: Plural                       & \S12–15 & 8 Nov. \\
    18  & Word Order                                                 & & \\
    r-3 & \texthebrew{מקרא ג} (Genesis 22\texthebrew{א})             & & \\ [1ex]
    19  & \texthebrew{קל} Perfect Conjugation: Plural                & \S16–17 & 15 Nov. \\
    20  & \texthebrew{סמיכות} (Bound Nouns)                           & & \\ [1ex]
    21  & The Irreal Use of the Perfect Conjugation                  & \S18–19 & 22 Nov. \\
    22  & Attached Pronouns: Singular                                & & \\
    23  & \texthebrew{קל} Imperfect Conjugation: Singular            & & \\ [1ex]
    r-4 & \texthebrew{מקרא ד} (Genesis 37\texthebrew{א})             &  & 29 Nov. \\
    24  & The Infinitive                                             & \S20 & \\
    25  & The Adverbial Infinitive                                   & & \\ [1ex]
    26  & Objects                                                    & \S21–22 & 6 Dec. \\
    r-5 & \texthebrew{מקרא ה} (Genesis 3\texthebrew{ב})              & & \\
    \sessionskip{\rarr} & \textbf{Final Exam} (last half of class)   & & \\
    \bottomrule
  \end{tabular}
  \caption{Schedule of Lessons \& Readings}
  \label{schedule}
\end{table}

See the AST website for a list of other \href{http://www.astheology.ns.ca/students/academic-dates.html}{important dates}.

\section{Evaluation}
\label{evaluation}

The grade structure for \ccode has the following elements.

\begin{enumerate}
 \item
    Students are expected to complete all lessons and exercises from
    \cite{bbh}, and to study and master all sections (\S) from
    \cite{tm}. \textbf{Quizzes} based on the weekly assignments will be
    given regularly. Some of these may come directly from \cite{bbh}.
 \item
   A cumulative \textbf{midterm exam} will be given in the last half of
   the sixth class.
 \item
   A comprehensive \textbf{final exam} will be given in the last half of
   the twelfth class.
\end{enumerate}

The breakdown for the semester's total work is shown in
\autoref{distribution}.

\begin{table}[htbp]
  \centering
  {\lining
  \begin{tabular}{lr}
    \toprule
    Quizzes      & 40\% \\
    Midterm Exam & 30\% \\
    Final Exam   & 30\% \\
    \bottomrule
  \end{tabular}}
  \caption{Distribution of Grades}
  \label{distribution}
\end{table}

\input{\policy/grades}
\input{\policy/other}


\section{Bibliography}
\label{bib}

Among the many Hebrew grammars and resources, note the following
especially:

\begin{itemize}
  \item Guides \& Aids

    \begin{itemize}
      \item
        Van Pelt, Miles. \emph{English Grammar to Ace Biblical Hebrew}.
        Grand Rapids: Zondervan, 2010. At AST: PE 1130 H5 V35 2010
      \item
        Einspahr, Bruce. \emph{Index to Brown, Driver \& Briggs Hebrew Lexicon}.
        Chicago: Moody Press, 1976. At AST: PJ 4833 B683 E35
      \item
        Landes, George M. \emph{Building Your Biblical Hebrew
        Vocabulary: Learning Words by Frequency and Cognate}.
        Atlanta: SBL, 2001. At AST: PJ 4845 L25 2001
      \item
        Scott, W.\,R., and H.\,P. Rüger. \emph{A Simplified Guide to BHS:
        Critical Apparatus, Masora, Accents, Unusual Letters \& Other
        Markings}. 3rd edition. N. Richland Hills, TX: BIBAL, 2007.
        At AST: BS 715 1977f
      \item
        Kelley, Page H., Daniel S. Mynatt, and Timothy G. Crawford.
        \emph{The Masorah of Biblia Hebraica Stuttgartensia:
        Introduction and Annotated Glossary}.
        Grand Rapids: Eerdmans, 1998. At AST: BS 718 K38 1998
    \end{itemize}

  \item Introductory Grammars

    \begin{itemize}
      \item
        Kittel, Bonnie, Vicki Hoffer, and Rebecca Abts Wright.
        \emph{Biblical Hebrew: Text and Workbook} [and Audio CD].
        2nd edition. New Haven: Yale, 2004.
      \item
        Martin, J.\,D. \emph{Davidson’s Introductory Hebrew Grammar}.
        27th edition. Edinburgh: T\&T Clark, 1993. At AST: PJ 4567 D37 1962
      \item
        Pratico, Gary and Miles Van Pelt. \emph{Basics of Biblical Hebrew Grammar}.
        Grand Rapids: Zondervan, 2001. At AST: PJ 4567.3 P73 2007
      \item
        Seow, C.\,L. \emph{A Grammar for Biblical Hebrew}.
        Nashville: Abingdon, 1995. At AST: PJ 4567 S424 1995
      \item
        Weingreen, J. \emph{A Practical Grammar for Classical Hebrew}.
        Oxford: Clarendon, 1959. At AST: PJ 4567 W4 1959
    \end{itemize}


  \item Syntaxes \& Reference Grammars

    \begin{itemize}
      \item
      	Arnold, Bill T., and John H. Choi. \emph{A Guide to Biblical Hebrew Syntax}.
      	Cambridge: Cambridge University Press, 2003. At AST: PJ 4701 A76 2003
      \item
      	Waltke, Bruce K., and M. O’Connor. \emph{An Introduction to Biblical Hebrew Syntax}.
      	Winona Lake, IN: Eisenbrauns, 1990.
      \item
        Williams, Ronald J., and  Beckman, John C. \emph{Williams' Hebrew Syntax}.
        Toronto: University of Toronto Press, 2007. At AST: PJ 4701 W5 2007
      \item
        Gesenius, Wilhelm, E. Kautsch and A.\,E. Cowley. \emph{Hebrew Grammar}.
        Oxford: Clarendon, 1910. \textbf{GKC} remains a standard Hebrew
        reference grammar in English, even though Cowley's translation
        -- of the 28th german edition -- is now over 100 years old. At
        AST: PJ 4564 G5 1910
      \item
      	Joüon, P., and T. Muraoka. \emph{A Grammar of Biblical Hebrew}.
      	2nd edition. Subsidia Biblica 27. Rome: Pontifical Biblical
      	Institute, 2008. One of the most complete and up-to-date
      	Hebrew grammars in English, \textbf{JM} (1st ed. 1991) was
      	revised from a French work first published by Paul Joüon in
      	1923. At AST: PJ 4567 J7613 1993
    \end{itemize}

  \item Lexicons

    \begin{itemize}
      \item
        Brown, Francis, S.\,R. Driver and Charles A. Briggs. \emph{The
        Brown-Driver-Briggs Hebrew and English Lexicon}. Peabody, Mass:
        Hendrickson, 2004. The \textbf{BDB} was originally published in 1906.
        On \href{https://archive.org/details/hebrewenglishlex00geseuoft}{archive.org}
        and at AST: PJ 4833 B68 1996
      \item
        Köhler, Ludwig, and Walter Baumgartner. \emph{The Hebrew
        and Aramaic Lexicon of the Old Testament}. Leiden: Brill,
        1994--2000.
        At AST: PJ 4833 K61813 1994
      \item
        Holladay, William L. \emph{A Concise Hebrew and Aramaic Lexicon
        of the Old Testament, Based Upon the Lexical Work of Ludwig
        Koehler and Walter Baumgartner}.
        Grand Rapids: Eerdmans, 1971.
        At AST: PJ 4833 H6 1971
      \item
        Clines, David J.\,A. \emph{The Dictionary of Classical Hebrew}.
        Sheffield: Sheffield Academic Press, 1993--2011.
        At AST: PJ 4833 D53 1993
    \end{itemize}

\end{itemize}


\end{document}
