% Copyright (c) 2021 by Daniel R. Driver.
% !TEX encoding = UTF-8 Unicode
% !TEX TS-program = XeLaTeX

\documentclass[titlepage]{article}

% This document presumes a file structure and set of inputs that are
% available at: git@github.com:danieldriver/syllabi.git

\newcommand\policy{../policy}
\newcommand\incl{../includes}
\input{\incl/variables}

%\onlinetrue % \Int{true}{false}
\coursecode[1.0]{HB 3117(Hyb)}
\coursetitle[Hebrew Bible]{Creation and Canon}

% Taught as HB 3117 in:
%   - Fall 2021 (Hyb)

\professor{Daniel R. Driver}
\phone{902-425-7051}
\email{ddriver@astheology.ns.ca}
\officehours[Microsoft Teams]{Tuesdays, 1:00--3:00 \PM}

\semester{Fall Term 2021}
\meets{Mondays}% \meets{on}{at}{in}
      {4:00--6:30 \PM}% if online, it prints "From 9:00 AM"
      {Classroom 3/Teams}% if online, it prints "Brightspace" with link
\website{danieldriver.com}
\cdescription[RM 1000 or GTRS 6000; BF 1001]{% copy from the current Academic Calendar; [] for prereqs
	A study of creation across the Christian Bible, with particular
	focus on the HB/OT, this course will explore why the topic of
	creation has been sidelined in biblical studies and biblical
	theology, and how, thanks in part to the ecological crisis, it is
	getting new attention. Major headings in the course are creation,
	counter-creation, de-creation, and re-creation. Minor themes include
	sabbath, sea monsters, land, city, wisdom, and praise.
}% end of course description
\objectives{% recall Bloom's taxonomy: https://www.celt.iastate.edu/teaching/effective-teaching-practices/revised-blooms-taxonomy/
	By the end of the course students should be able to articulate a theology of creation.
	In particular, they should be able to:
		understand a variety of methods and approaches to the theme;
		analyze a proposal stipulating rules for Christian speech about creation;
		identify a number of primary texts, both inside and outside the Bible;
		contextualize and discuss many of those texts informally;
		name and evaluate with ecumenical sensitivity a range of scholarly interprations, including by Jews, Christians, and others;
		formally exegete at least one biblical creation text;
		begin to construct, or to know how to begin to construct, a more complete biblical theology of creation.
}% end of learning objectives

\input{\incl/preamble}

\begin{document}
\input{\incl/title}

  \section{Learning Objectives}
  \label{objectives}

  \edobject

\section{Required Texts \& Materials}
\label{texts}

The following texts are required. Students are strongly encouraged to
purchase their own copies. Library copies that are not reference works
will be placed on a 2-hour reserve.

\begingroup
\renewcommand{\section}[2]{}% temporarily remove the section heading
\begin{thebibliography}{Levenson}% use the longest item in the bibliography

	\bibitem[NRSV]{nrsv} M.\,D. Coogan, ed.
    \emph{New Oxford Annotated Bible with Apocrypha: NRSV}. 5th ed.
    Oxford: Oxford University Press, 2018.
    ISBN 978-0190276072.

	\bibitem[Myths]{myths} Stephanie Dalley, ed.
	\emph{Myths from Mesopotamia: Creation, The Flood, Gilgamesh, and Others}. Rev. ed.
	Oxford: Oxford University Press, 2000.
	ISBN: 978-0199538362.

	\bibitem[Levenson]{jl} Jon D. Levenson.
	\emph{Creation and the Persistence of Evil: The Jewish Drama of Divine Omnipotence}.
	Princeton: Princeton University Press, 1988 (repr. 1994).
	ISBN: 978-0691029504.

	\bibitem[Tanner]{kt} Kathryn Tanner.
	\emph{God and Creation in Christian Theology: Tyranny or Empowerment?}
	Oxford: Basil Blackwell, 1988 (repr. Minneapolis: Fortress Press, 2005).
	ISBN: 978-0800637378.

\end{thebibliography}
\endgroup

The NJPS is a good alternative study Bible: Adele Berlin and Marc Zvi
Brettler, eds., \emph{The Jewish Study Bible: Second Edition} (Oxford:
Oxford University Press, 2014). \href{https://danieldriver.com/courses/hb-3117/}{See
my website for links to required and recommended books, and a discussion
of options for a Bible.}

\section{Supplementary Texts}
\label{supplementary}

Supplementary readings will be recommended throughout the semester and
may be placed on reserve or made available through the course website.

The following titles are especially worth owning and consulting.
\cite{ed} explores the theology and ethics of land use. \cite{ms}
develops a suggestive reading of Genesis 1 within a comparative
framework. We will read excerpts from both books. Beyond the course
theme, \cite{rlgs} contains sound advice on core skills like reading
religious texts, writing essays and reviews, revising essays, making
oral presentations, and learning languages. Finally, \cite{sbl2} will
help you format your papers appropriately.

\begingroup
\renewcommand{\section}[2]{}% temporarily remove the section heading
\begin{thebibliography}{Making Sense}% use the longest item in the bibliography

	\bibitem[Davis]{ed} Ellen F. Davis.
	\emph{Scripture, Culture, and Agriculture: An Agrarian Reading of the Bible}.
	New York: Cambridge University Press, 2009.
	ISBN: 978-0521732239.

	\bibitem[Smith]{ms} Mark S. Smith.
	\emph{The Priestly Vision of Genesis 1}.
	Minneapolis: Fortress, 2010.
	ISBN: 978-0800663735.

	\bibitem[Making Sense]{rlgs} Northey, Margot, Bradford A. Anderson, and Joel N. Lohr.
	\emph{Making Sense in Religious Studies: A Student's Guide to Research and Writing}.
	3rd ed. Toronto: Oxford University Press, 2019. ISBN 978-0199026838.

	\bibitem[SBL2]{sbl2} Collins, Billie Jean, et al.
	\emph{The SBL Handbook of Style}.
	2nd ed. Atlanta: SBL Press, 2014. ISBN 978-1589839649.
	Designed to augment \href{http://www.chicagomanualofstyle.org/home.html}{\emph{Chicago Style}}
	(the standard at AST), there is also a free
	\href{https://www.sbl-site.org/assets/pdfs/pubs/SBLHSsupp2015-02.pdf}{Student Supplement for SBL2}.

\end{thebibliography}
\endgroup


\section{Course Outline}
\label{outline}

We will adhere to the schedule in \autoref{schedule} as closely as
possible, though the professor reserves the right to adjust it to suit
the needs of the class.

\newcommand\HBFB[1]{\cite[#1]{hbfb}}

\setcolumncount{4}% set up \sessioncount, \unit{}, \noclass{}, and \reminder{memo}{date} macros
\begin{table}[htbp]% set to `p' to put the schedule on its own page
  \centering
  \begin{tabular}{>{\sessioncount.}r@{ }llr}% make sure the column config agrees with \setcolumncount
	\toprule
	\sessionskip{\textbf{\S}.}&\textbf{Primary}&\textbf{Secondary}&\textbf{Due}\\
	\midrule

	\unit{Creation} \\

		& Genesis 1--2         &                            & 13 Sep. \\
		& Psalms 8; 19; 104    & \cite[chs 1--2]{kt}        & 20 Sep. \\
		& Prov 8; Wis of Sol 6 & \cite[chs 3--end]{kt}      & 27 Sep. \\
		& Isaiah 40--55        & \cite[ch 1]{ms}            &  4 Oct. \\
	\noclass{Thanksgiving}                                  & 11 Oct. \\
	\noclass{Reading Week}                                  & 18 Oct. \\
	\reminder{A first short paper is \textbf{due} by the end of week five}{} \\ [1ex]% NB I moved this back from wk 6 to wk 5 because of the unusual two week break in F21. Perhaps move back to wk 6 next time.

	\unit{Counter-Creation} \\

		& Genesis 3--5         & \cite[chs 1--4]{jl}        & 25 Oct. \\
		& \cite[pp 1--153]{myths}   & \cite[chs 5--9]{jl}   &  1 Nov. \\
		& \cite[pp 154--315]{myths} & \cite[chs 10--12]{jl} &  8 Nov. \\ [1ex]

	\unit{De-Creation} \\

		& Genesis 6--9         & self-directed              & 15 Nov. \\
		& Job; Psalms 74; 89   & self-directed              & 22 Nov. \\
		& Ecclesiastes 1--12   & self-directed              & 29 Nov. \\
	\reminder{A second short paper is \textbf{due} by the end of week eleven}{} \\ [1ex]

	\unit{Re-Creation} \\

		& Gen 10--14; Exod 1--15; 39--40 & self-directed    &  6 Dec. \\
		& Psalms 51; 146--150  & \cite[ch 9]{ed}            & 13 Dec. \\ [1ex]

	\reminder{End of Term: Final marks are due for all courses}{16 Dec.} \\

	\bottomrule
  \end{tabular}
  \caption{Schedule of Readings}
  \label{schedule}
\end{table}

See the AST website for a list of other \href{http://www.astheology.ns.ca/students/academic-dates.html}{important dates}.

\section{Evaluation}
\label{evaluation}

The grade structure for \ccode has the following elements.

\begin{enumerate}

	\item \textbf{Writing prompts} will be given throughout the
	semester. They are low-risk writing exercises designed to encourage
	careful reading of the assigned material, and to help explore its
	significance. Prompt responses are not marked, though points may be
	deducted if the exercise is not taken seriously. Prompts will
	usually be given live, near the beginning of each class. However, we
	may shift to online submissions if the format seems preferable
	(depending, in part, on how hybrid engagement works). If the prompts
	move to online forums, responses should not exceed 300 words.

	\item Two \textbf{short papers} will facilitate student engagement
	with the art of biblical interpretation. One is keyed to a
	theological theme, the other to a biblical text. Each should be
	about 3,000 words in length. The first paper is due at the end of
	the fifth week of class; the second is due at the end of the
	eleventh week.

	% I moved the first paper from wk 6 to wk 5 because of the unusual
	% two-week break in F21. Perhaps move it back to wk 6 next time.

	\begin{enumerate}

		\item A \textbf{theological essay} invites reflection on the
		parameters for Christian discourse about creation. How can and
		should we speak of the God of creation? The primary interlocutor
		for this paper is \cite{kt}. She outlines a number of rules for
		faithful speech about the transcendence and creative agency of
		God. Is her thesis persuasive? Is it right? How does it help?
		What are its limitations? Other sources may be engaged, if
		desired, but \cite{kt} must be engaged fully.

		You might think of this paper as a \emph{review essay} (note:
		this is not the same thing as a book report). Devote the first
		half of the paper to a summary the argument under review. Devote
		the second half of the paper to critical analysis and evaluation
		of the same. Be specific. In your analysis, select and discuss
		concrete examples from the work. Be fair, too, but do not fail
		to take a position. The paper needs to develop a
		\textbf{thesis}. See me and \cite[chs 3, 5–7, 11]{rlgs} for
		guidance.

		\item An \textbf{exegetical essay} provides an opportunity for
		direct work with the biblical text. The first task is to
		identify an appropriate text. Select a suitably short passage
		from the HB/OT. Then, conduct an analysis and explication of it.
		Interact with the assigned literature and at least five other
		sources or commentators. (Note that secondary reading from week
		eight is self-directed; you may also ask for suggestions.)
		Advance a \textbf{thesis} that relates to the chosen text. See
		me and \cite[chs 3, 5, 8, 11]{rlgs} for guidance.

	\end{enumerate}

	\item Before the last day of class, each student will upload a brief
	(5--7 minute) \textbf{video presentation} that summarizes and
	synthesizes their work in this course. First, by way of
	\emph{summary}, describe and contextualize the results of your
	exegetical paper. What text did you select and why? What did you
	discover about it through research and study? In a single sentence,
	what was your thesis? Second, by way of \emph{synthesis}, what might
	your exegetical work contribute to a renewed Christian theology of
	creation? You may revisit Tanner's argument here, if desired.
	Alternatively, how might your findings sharpen our understanding of
	the Bible's creation traditions?

	In essence, in this video you are distilling and representing the
	introduction and conclusion to your exegetical essay, but with a
	wider outlook and in a different medium. Elaborate with a view to
	the broad theme of creation. Answer the question: So what? Videos
	should be sharable by URL (try YouTube or Vimeo), and posted to
	Teams for the benefit of the class, to be viewed and discussed
	asynchronously. Finally, be sure not to exceed the time limit;
	points will be deducted for overlong submissions. To keep to time
	you will probably need to edit your video (recommended), or else to
	plan and rehearse your presentation well enough to capture it in a
	single take.

\end{enumerate}

The breakdown for the semester's total work is shown in
\autoref{grade-dist}.

\begin{table}[htbp]
  \centering
  {\lining
  \begin{tabular}{lr}
    \toprule
    Reading Prompts    & 20\% \\
    Review Essay       & 30\% \\
    Exegetical Essay   & 30\% \\
    Video Presentation & 20\% \\
    \bottomrule
  \end{tabular}}
  \caption{Distribution of Grades}
  \label{grade-dist}
\end{table}

%AST's \href{http://www.astheology.ns.ca/students/resources.html}{Academic
%Calendar} provides guidelines and detailed criteria for academic
%assessment. Marks are assigned by letter grade using these benchmarks.

\input{\policy/grades}
\input{\policy/other}

%\section{Bibliography}
%\label{bib}
%
%Literature on creation is vast. See the professor for suggestions on further reading.

\end{document}
