% Copyright (c) 2024 by Daniel R. Driver.
% !TEX encoding = UTF-8 Unicode
% !TEX TS-program = XeLaTeX

\documentclass[titlepage]{article}

% This document presumes a file structure and set of inputs that are
% available at: git@github.com:danieldriver/syllabi.git

\newcommand\policy{../policy}
\newcommand\incl{../includes}
\input{\incl/variables}

%\onlinetrue % \Int{true}{false}
\coursecode[2.1]{HB 3114}
\coursetitle{The Twelve Prophets}

% Taught as RLGS 3143 in:
%   - Winter 2010
%   - Winter 2013
% Taught as HB 3114 in:
%   - Winter 2018
%   - Winter 2024

\professor{Daniel R. Driver}
\phone{902-425-7051}
\email{daniel.driver@astheology.ns.ca}
\officehours{Thursdays, 1:00--3:00 \PM}

\semester{Winter Term 2024}
\meets{Thursdays}% \meets{on}{at}{in}
      {4:00--6:30 \PM}
      {Classroom 3/Teams}
\website[https://danieldriver.com/courses/hb-3114/]{danieldriver.com}
\cdescription{% copy from the current Academic Calendar
	To better understand the origins and impact of the Book of the
	Twelve, this course will look at its redactional history and
	editorial shaping, its final canonical forms, and its effects as
	biblical prophecy. It will introduce current issues in scholarly
	debate about the Twelve while also exploring ways that they meet the
	ancient expectation that their “bones” can “send forth new life”
	amidst the people of God (Sirach 49:10).
}% end of course description
%\objectives{% recall Bloom's taxonomy: http://www.celt.iastate.edu/teaching/RevisedBlooms1.html
%By the end of the course students should be able to:
%}% end of learning objectives

\input{\incl/preamble}

\begin{document}
\input{\incl/title}

%  \section{Learning Objectives}
%  \label{objectives}
%
%  \edobject

\section{Required Texts \& Materials}
\label{texts}

In addition to \textbf{the Bible in a modern translation} such as the
NJPS or NRSV, the following text is required. Students are strongly
encouraged to purchase their own copies. AST Library copies will be
placed on a two-hour reserve.

\begingroup
\renewcommand{\section}[2]{}% temporarily remove the section heading
\begin{thebibliography}{Theodoret}% use the longest item in the bibliography

	\bibitem[Heschel]{Heschel} Heschel, Abraham J.
	\emph{The Prophets}.
	New York: Harper \& Row, 1962. Repr., New York: Perennial Classics, 2001.
	\textsc{isbn} 978-0060936990. \href{https://amzn.to/46qhye3}{Order online.}

	\bibitem[Theodoret]{Theodoret} Theodoret of Cyrus.
	\emph{Commentary on the Twelve Prophets}. Vol. 3 of \emph{Commentaries on the Prophets}.
	Translated by Robert C. Hill.
	Brookline, MA: Holy Cross Orthodox Press, 2006.
	\textsc{isbn} 978-1885652768. \href{https://amzn.to/47kYajz}{Order online.}

%	\bibitem[Two Sides]{Two} Ehud Ben Zvi and James D. Nogalski.
%	\emph{Two Sides of a Coin: Juxtaposing Views on Interpreting the Book of the Twelve / the Twelve Prophetic Books}.
%	Piscataway, NJ: Gorgias Press, 2009.
%	\textsc{isbn} 978-1607243038.

%	\bibitem[Seitz]{Seitz} Christopher R. Seitz.
%	\emph{The Goodly Fellowship of the Prophets: The Achievement of Association in Canon Formation}.
%	Grand Rapids: Baker Academic, 2009.
%	\textsc{isbn} 978-0801038839.

%	\bibitem[Jerome]{Jerome1} Jerome; Thomas P. Scheck, trans.
%	\emph{Commentaries on the Twelve Prophets, Vol. 1 (Ancient Christian Texts)}.
%	Downers Grove: IVP Academic, 2016.
%	\textsc{isbn} 978-0830829163.

\end{thebibliography}
\endgroup

\section{Supplementary Texts}
\label{supplementary}

Supplementary readings will be recommended throughout the semester.
Excerpts from this literature may be placed on reserve or made available
for download through the course website. Outstanding students will also
pursue leads on their own, using library databases and pursuing notes
and bibliographies in the required reading.

The following titles are notable in relation to the main texts. They are
not required.

\begingroup
\renewcommand{\section}[2]{}% temporarily remove the section heading
\begin{thebibliography}{3}% use the longest item in the bibliography

	\bibitem{Bickerman} Bickerman, Elias.
	\emph{Four Strange Books of the Bible: Jonah, Daniel, Koheleth, Esther}.
	New York: Schocken, 1967.

	\bibitem{Sabbath} Heschel, Abraham Joshua.
	\emph{The Sabbath: Its Meaning for Modern Man}.
	New York: Farrar, Straus and Giroux, 1951.

	\bibitem{Hill} Hill, Robert C.
	\emph{Reading the Old Testament in Antioch}. Bible in Ancient Christianity 5.
	Leiden: Brill, 2005. Link: \href{https://ast.primo.exlibrisgroup.com/view/action/uresolver.do?operation=resolveService&package_service_id=785748290007188&institutionId=7188&customerId=7185&VE=true}{AST eBook}.

	\bibitem{Nogalski-Sweeney} Nogalski, James D., and Marvin A. Sweeney, eds.
	\emph{Reading and Hearing the Book of the Twelve}. SBL Symposium Series.
	Atlanta: SBL, 2000.

	\bibitem{Redditt-Schart} Redditt, Paul L., and Aaron Schart, eds.
	\emph{Thematic Threads in the Book of the Twelve}.
	Berlin: Walter de Gruyter, 2003.

	\bibitem{Watts-House} Watts, James W., and Paul R. House, eds.
	\emph{Forming Prophetic Literature: Essays on Isaiah and the Twelve in Honor of John D.W. Watts}.
	Sheffield: Sheffield Academic, 1996.

\end{thebibliography}
\endgroup

\section{Course Outline}
\label{outline}

We will adhere to the schedule in \autoref{schedule} as closely as
possible, though the professor reserves the right to adjust it to suit
the needs of the class.

\setcolumncount{4}% set up \sessioncount, \unit{}, \noclass{}, and \reminder{memo}{date} macros
\begin{table}[htbp]% set to `p' to put the schedule on its own page
  \centering
  \begin{tabular}{>{\sessioncount.}r@{ }llr}% make sure the column config agrees with \setcolumncount
	\toprule
	\sessionskip{\textbf{\S}.}&\textbf{Primary}&\textbf{Secondary}&\textbf{Date}\\
	\midrule
		& None: Introductions & Syllabus & 11 Jan. \\
		& Hosea 1             & Theodoret 1--42, Heschel 47--61   & 18 Jan. \\
		& Hosea 2--3          & Theodoret 42--48, Heschel 61--75  & 25 Jan. \\
		& Hosea 4--6          & Theodoret 48--57, Heschel 3--19   &  1 Feb. \\
		& Hosea 7--9          & Theodoret 57--67, Heschel 19--31  &  8 Feb. \\
		& Hosea 10--14        & Theodoret 67--83, Heschel         & 15 Feb. \\
	\reminder{Essay 1: Due by the end of Week Six}{18 Feb.} \\
	\noclass{Reading Week (Tuesday to Friday)}                    & 22 Feb. \\
		& Joel 1              & Theodoret 85--90, Heschel         & 29 Feb. \\
		& Joel 2--end         & Theodoret 90--102, Heschel        &  7 Mar. \\
	\noclass{Attend Grad Projects in lieu of regular class}       & 14 Mar. \\
		& Amos 1--2           & Theodoret 103--10, Heschel 32--39 & 21 Mar. \\
		& Amos 3--4           & Theodoret 110--16, Heschel 39--46 & 28 Mar. \\
		& Amos 5--6           & Theodoret 116--22, Heschel        &  4 Apr. \\
	\reminder{Essay 2: Due by the end of Week Eleven}{7 Apr.} \\
		& Amos 7--9           & Theodoret 122--28, Heschel        & 11 Apr. \\
	\reminder{End of Term: Final marks are due for all courses}{17 Apr.} \\
	\bottomrule
  \end{tabular}
  \caption{Schedule of Readings}
  \label{schedule}
\end{table}

See the AST website for a list of other \href{http://www.astheology.ns.ca/students/academic-dates.html}{important dates}.

\section{Evaluation}
\label{evaluation}

\subsection{Grade Structure for \ccode}
\label{structure}

\begin{enumerate}

	\item Weekly \textbf{seminar discussions} will facilitate close work
	with text and interpretation in select books from the Twelve.
	Students should come to class fully prepared to discuss the assigned
	material, which will ordinarily include one to four chapters of
	biblical material per week, plus some commentary on those chapters.
	Commentary available for study and preparation is by no means
	limited to the assigned works of \cite{Theodoret} and
	\cite{Heschel}. Also, Heschel does not follow the text sequentially;
	his book should be read beyond the assigned pages in a self-directed
	manner.

	\item At some point in the semester, each student should read and
	report back to the class about some recent scholarship on the book
	of the Twelve. This \textbf{reading report} should be scheduled
	between weeks two and twelve, to the extent possible with only one
	student per week. The reading should be drawn from the literature in
	\autoref{supplementary} or \autoref{bib}, selected in consultation
	with the professor.

	\item A \textbf{first essay} will be due at the end of the sixth
	week of class (Sunday, 18 February 2024). It should be 4,000 words
	long, plus or minus 250 words. It should answer the following
	question: \emph{How does the book of Hosea speak to the goodness of
	God and the sovereignty of God?}

	\item A \textbf{second essay} will be due at the end of the eleventh
	week of class (Sunday, 7 April 2024). It should be 4,000 words long,
	plus or minus 250 words. It should answer the following question:
	\emph{How does the presentation of God develop in the first part of
	the book of the Twelve?} Note that this question is not a repeat of
	the first one. Rather, it builds on the first paper by examining the
	character and presentation of God in the literary context that
	follows Hosea. If this question does not appeal, students are
	invited to propose an alternate question to the professor. The
	professor reserves the right to turn down the proposal or to make a
	counterproposal.
	
\end{enumerate}

The breakdown for the semester's total work is shown in
\autoref{grade-dist}.

\begin{table}[htbp]
  \centering
  {\lining
  \begin{tabular}{lr}
    \toprule
    Weekly Seminars & 10\% \\
    Reading Report  & 10\% \\
    Essay 1         & 40\% \\
    Essay 2         & 40\% \\
    \bottomrule
  \end{tabular}}
  \caption{Distribution of Grades}
  \label{grade-dist}
\end{table}

\input{\policy/grades}
\input{\policy/other}

\section{Further Bibliography}
\label{bib}

Access and study the following resources:

Schart, Aaron. “Bibliography on the Book of the Twelve Prophets.” This database with nearly all literature on the Book of the Twelve since 2010 is maintained at \url{https://www.zotero.org/groups/twelveprophets/items}.

Sweeney, Marvin A. “Book of the Twelve Prophets.” In \emph{Oxford Bibliographies: Biblical Studies}, \href{https://go.openathens.net/redirector/astheology.ns.ca?url=https://www.oxfordbibliographies.com/view/document/obo-9780195393361/obo-9780195393361-0016.xml}{https://www.oxfordbibliographies.com/view/document/obo-9780195393361/obo-9780195393361-0016.xml} (last modified 30 March 2015). AST students can sign in with their OpenAthens credentials.

\end{document}
