% Copyright (c) 2017 by Daniel R. Driver.
% !TEX encoding = UTF-8 Unicode
% !TEX TS-program = XeLaTeX

\documentclass[titlepage]{article}

% This document presumes a file structure and set of inputs that are
% available at: git@github.com:danieldriver/syllabi.git

\newcommand\policy{../policy}
\newcommand\incl{../includes}
\input{\incl/variables}

\coursecode[3.1.0]{HB 3112}
\coursetitle[Hebrew Bible]{Psalms in Interpretation}

% Taught as RLGS 3263 (T&I: Psalms in the Christian Tradition) in:
%   - Fall 2008
%   - Winter 2011
% Taught as BSTH 3142 (T&I: Psalms in Interpretation) in:
%   - Fall 2014
% Taught as HB 3112 in:
%   - Winter 2017

\professor{Daniel R. Driver}
\phone{902-425-7051}
\email{ddriver@astheology.ns.ca}
\officehours{Tuesdays, 1:30--3:30 \PM}

\semester{Winter Term 2017}
\meets{Tuesdays}% \meets{on}{at}{in}
      {9:00--11:30 \AM}
      {One (1)}
\website{astheology.ns.ca}
\cdescription{% copy from the current Academic Calendar
	The Psalms of the Hebrew Bible/Old Testament have a special part in
	the life of the synagogue and church. A major goal of this course is
	therefore to gain perspective on how the Psalter has fed and
	informed Jewish and Christian faith in various periods: in biblical
	times, Rabbinic and Patristic periods, the Middle Ages, the
	Reformation, the Enlightenment, and finally the early and late
	modern periods. By interacting with recent research into the shape
	and shaping of the Psalter we will also consider the anthology’s
	arrangement. Study will generally occur in one of two modes. First,
	secondary reading and class discussion will look at hermeneutical
	and historical factors involved in reading and understanding the
	Psalter. Second, seminars will help put theory into practice by
	featuring about a dozen particular psalms in connection with their
	reception history.
}% end of course description
\objectives{% recall Bloom's taxonomy: http://www.celt.iastate.edu/teaching/effective-teaching-practices/revised-blooms-taxonomy
	By the end of the course students should be able to:
		report on at least three distinct periods in the reception of the Psalter;
		analyze key differences between ancient and modern interpreters, and a variety of Jewish and Christian interpreters;
		interpret a psalm afresh while interacting with its past readers;
		recite at least twelve verses of a psalm from memory;
		respond creatively to a psalm in a way that engages with and illuminates the text.
}% end of learning objectives

\input{\incl/preamble}

\begin{document}
\input{\incl/title}

\section{Learning Objectives}
\label{objectives}
\edobject

\section{Required Texts \& Materials}
\label{texts}

The following texts are required. Students are strongly encouraged to
purchase their own copies. Library copies that are not reference works
will be placed on a 2-hour reserve.

\begingroup
\renewcommand{\section}[2]{}% temporarily remove the section heading
\begin{thebibliography}{Shape \& Shaping}% use the longest item in the bibliography

	\bibitem[NRSV]{nrsv} M.\,D. Coogan, ed.
    \emph{New Oxford Annotated Bible with Apocrypha: NRSV}. 4th ed.
    Oxford / New York: Oxford University Press, 2010.
    \textsc{isbn} 978-0195289602.

%	\bibitem[NJPS]{njps}
%	Adele Berlin and Marc Zvi Brettler, eds.
%	\emph{The Jewish Study Bible: Second Edition}.
%	Oxford / New York: Oxford University Press, 2014.
%	\textsc{isbn} 978-0199978465.

	\bibitem[Shape \& Shaping]{NdeCW} Nancy L. deClaissé-Walford.
	\emph{The Shape and Shaping of the Book of Psalms: The Current State of Scholarship}.
	Atlanta: SBL Press, 2014.
	\textsc{isbn} 978-1628370010.

	\bibitem[Two Psalms]{SGill} Susan Gillingham.
	\emph{A Journey of Two Psalms: The Reception of Psalms 1 and 2 in Jewish and Christian Tradition}.
	Oxford: Oxford University Press, 2014.
	\textsc{isbn} 978-0199652419.

%	\bibitem[tk]{tk} tk.
%	\emph{tk}.
%	tk: tk, 20tk.
%	\textsc{isbn} 978-tk.

\end{thebibliography}
\endgroup

An acceptable alternative study Bible is the NJPS: Adele Berlin and Marc
Zvi Brettler, eds., \emph{The Jewish Study Bible: Second Edition}
(Oxford / New York: Oxford University Press, 2014). A reference copy is
available in the library, and it is well worth consulting.

\section{Supplementary Texts}
\label{supplementary}

Supplementary readings will be recommended throughout the semester.
Excerpts from this literature may either be placed on reserve or made
available for download through the course website. Outstanding students
will also pursue leads on their own, making maximum use of notes and
bibliographies in the required textbooks.

%The following articles or book chapters represent a range of scholarly
%and theological interest in the Psalms. They will either be available
%for download through the course website, or kept on reserve in the
%library. Students are not strictly required to read the supplementary
%material; then again, students who choose not to read it should not
%expect to get an A for the course.
%
%\begin{enumerate}
%
%  \item Katharine Dell, “Psalms,” pages 37--51 in M. Lieb et al., eds., \emph{The Oxford Handbook of the Reception History of the Bible} (Oxford: Oxford University Press, 2011). [\href{http://ezproxy.mytyndale.ca:2048/login?url=http://www.oxfordhandbooks.com/view/10.1093/oxfordhb/9780199204540.001.0001/oxfordhb-9780199204540-e-4}{online}]
%
%  \item James Kugel, “The Psalms of David,” pages 458–473 in \emph{How to Read the Bible: A Guide to Scripture, Then and Now} (New York/Toronto: Free Press, 2007).
%
%  \item Hermann Gunkel, “The Religion of the Psalms,” pages 134–167 in \emph{Water for a Thirsty Land} (Minneapolis: Fortress, 2001). German original published in 1922.
%
%  \item John O’Keefe, “‘A Letter that Killeth’: Toward a Reassessment of Antiochene Exegesis, or Diodore, Theodore and Theodoret on the Psalms,” \emph{Journal of Early Christian Studies} 8/1 (2000): 83–104.
%
%  \item Brevard Childs, “Psalm Titles and Midrashic Exegesis,” \emph{Journal of Semitic Studies} 16/2 (1971): 137--150. See also his “Psalm 8 in the Context of the Christian Canon,” pages 151–163 in \emph{Biblical Theology in Crisis} (Philadelphia: Westminster, 1970).
%
%  \item Michael Cameron, ``Hearing Voices: Christ at Prayer `in the Psalm and on the Cross,'\,'' pages 164--212 in \emph{Christ Meets Me Everywhere: Augustine's Early Figurative Exegesis} (Oxford: Oxford University Press, 2012).
%
%  \item Jonathan Magonet, “Through Rabbinic Eyes: Psalm 23,” pages 47–61 in \emph{A Rabbi Reads the Psalms} (2nd ed.; London: SCM, 2004).
%
%  \item Alan Cooper, ``Ps 24:7-10: Mythology and Exegesis,'' \emph{Journal of Biblical Literature} 102/1 (1983): 37--60. [\href{http://www.jstor.org/stable/3260745}{online}]
%
%  \item C.\,S. Lewis, ``\,`Sweeter than Honey,'\,'' pages 54--65 in \emph{Reflections on the Psalms} (London: Geoffrey Bles, 1958).
%
%  \item Joseph Addison, ``Saturday, September 20, 1712,'' \emph{The Spectator} 489 (available on \href{http://www.gutenberg.org/files/12030/12030-h/SV3/Spectator3.html#section489}{Project Gutenberg}). Also read his \href{http://www.bartleby.com/101/433.html}{poetic paraphrase of Psalm 19}.
%
%  \item J. Clinton McCann, “Books I–III and the Editorial Purpose of the Hebrew Psalter,” pages 93–107 in J.\,C. McCann, ed., \emph{The Shape and Shaping of the Psalter} (JSOTSup 159; Sheffield: Sheffield Academic Press, 1993).
%
%  \item Gerald Wilson, “Shaping the Psalter: A Consideration of Editorial Linkage in the Book of Psalms,” pages 72–82 in J.\,C. McCann, ed., \emph{The Shape and Shaping of the Psalter} (JSOTSup 159; Sheffield: Sheffield Academic Press, 1993).
%
%  \item Gerald Sheppard, “Theology and the Book of Psalms,” \emph{Interpretation} 46 (1992): 143–155.
%
%  \item Hans-Joachim Kraus, “The Psalms in the New Testament,” pages 177–203 in \emph{Theology of the Psalms} (Minneapolis: Augsburg, 1986). German original published in 1979.
%
%  \item Christopher R. Seitz, ``Theological Use of the Old Testament: Recent New Testament Scholarship and the Psalms as Christian Scripture,'' pages 137--156 in C. Seitz, \emph{The Character of Christian Scripture: The Significance of a Two-Testament Bible} (Grand Rapids: Baker Academic, 2011).
%
%  \item Craig A. Evans, “Praise and Prophecy in the Psalter and in the New Testament,” pages 551--579 in P. Flint and P. Miller, eds., \emph{The Book of Psalms} (Leiden: Brill, 2005).
%
%  \item Adele Berlin, “Psalms and the Literature of Exile: Psalms 137, 44, 69, and 78,” pages 65--86 in P. Flint and P. Miller, eds., \emph{The Book of Psalms} (Leiden: Brill, 2005).
%
%  \item Erhard Gerstenberger, “Theologies in the Book of Psalms,” pages 603–625 in P. Flint and P. Miller, eds., \emph{The Book of Psalms} (Leiden: Brill, 2005).
%
%  \item Rolf Rendtorff, “The Psalms of David: David in the Psalms,” pages 53–64 in P. Flint and P.~Miller, eds., \emph{The Book of Psalms} (Leiden: Brill, 2005).
%
%\end{enumerate}

\begin{multicols}{3}[Major modern commentaries on the Psalms include:]%
\footnotesize\noindent
E. Hengstenberg (\textsuperscript{2}1849--52)\\
J. Olshausen (1853)\\
H. Hupfeld (1855--62)\\
W.\,M.\,L. de Wette (\textsuperscript{5}1856)\\
F. Delitzsch (1871)\\
J.\,J.\,S. Perowne (\textsuperscript{7}1890)\\
J. Wellhausen (\textsuperscript{3}1898)\\
A.\,F. Kirkpatrick (1891--1901)\\
C.\,A. Briggs (1906--07)\\
B. Duhm (\textsuperscript{2}1922)\\
H. Gunkel (\textsuperscript{4}1926)\\
R. Kittel (\textsuperscript{5-6}1929)\\
E.\,W. Barnes (1931)\\\
H. Schmidt (1934)\\
W.\,O.\,E. Oesterley (1939)\\
A. Cohen (1945)\\
H. Lamparter (1958)\\
A. Weiser (1962)\\
E.\,J. Kissane (\textsuperscript{2}1964)\\
A. Deissler (1965)\\
M.\,J. Dahood (1966--70)\\
H.-J. Kraus (\textsuperscript{4}1972)\\
A.\,A. Anderson (1972)\\
D. Kidner (1975)\\
J. Rogerson, J. McKay (1977)\\
L. Jacquet (1975--79)\\
P. Craigie, L. Allen (1983)\\
C. Stuhlmueller (1985)\\
E. Gerstenberger (1988)\\
M. Girard (1984--1996)\\
J. Day (1990)\\
M. Tate (1990)\\
A.\,C. Feuer (\textsuperscript{3}1991)\\
J.\,L. Mays (1994)\\
K. Seybold (1996)\\
C. Broyles (1999)\\
F.-L. Hossfeld,\par E. Zenger (1993--2008)\\
J.-L. Vesco (2006)\\
W. Brueggemann,\par W. Bellinger (2014)\\
M. Oeming, J. Vette (2000--16)
\end{multicols}

%\begin{multicols}{2}[Commentaries on the Psalms in the AST library include:]%
%\footnotesize\noindent
% REVISE THE FOLLOWING (taken from my Genesis syllabus)
%Targums: {\scshape BS 709.2 B5 1987 vv. 1A, 1B, 6} (c. 150--?)\\
%Didymus the Blind: {\scshape BS 1235 D4913 2016} (d. 398)\\
%Augustine of Hippo: {\scshape BS 1235 A8413 1991} (d. 430)\\
%Bede, the Venerable: {\scshape BS 1235 B43 2008} (d. 735)\\
%ACCS, Genesis 1--11: {\scshape BS 1235.3 G46 2001}\\
%ACCS, Genesis 12--50: {\scshape BS 1235.53 G46 2002}\\
%RCS, Genesis 1--11: {\scshape BS 1235.53 G455 2012}\\
%Luther, Martin: {\scshape BR 330 E5 1955 vv.1--8} (d. 1546)\\
%Calvin, John: {\scshape BS 1235 C293 1948} (d. 1564)\\
%Patrick, Simon: {\scshape BS 1235 P36 1695}\\
%Henry, Matthew: {\scshape BS 490 H4 1961} (d. 1714)\\
%Hershon, Paul Isaac: {\scshape BS 1235 H47} (1883)\\
%Delitzsch, Franz: {\scshape BS 1235 D4} (1888)\\
%Skinner, John: {\scshape BS 1235 S45 1917, 1963} (1930)\\
%Richardson, Alan: {\scshape BS 1235 R66 1959}\\
%Cassuto, Umberto: {\scshape BS 1235.3 C3} (1961)\\
%Herbert, Arthur: {\scshape BS 1235.3 H4} (1962)\\
%Speiser, E. A.: {\scshape BS 1233 S64 1964}\\
%Kidner, Derek: {\scshape BS 1235.3 K47} (1967)\\
%von Rad, Gerhard: {\scshape BS 1235.3 R3213 1972}\\
%Plaut, Gunther: {\scshape BS 1225.3 P55 v. 1} (1974)\\
%Vawter, Bruce: {\scshape BS 1235.3 V38 1977}\\
%Davidson, Robert: {\scshape BS 1235.3 D3 1973, 1979}\\
%Leibowitz, Nehama: {\scshape BS 1235.3 L413 1981}\\
%Wenham, Gordon : {\scshape BS 491.2 W67 1982}\\
%Brueggemann, Walter: {\scshape BS 1235.3 B78} (1982)\\
%Maher, Michael: {\scshape BS 1235.3 M346 1982}\\
%Westermann, Claus: {\scshape BS 1235.3 W43213 1986, 1987, 1994}\\
%Sarna, Nahum: {\scshape BS 1235.3 S325 1989}\\
%Hamilton, Victor: {\scshape BS 1235.3 H32 1990, 1995}\\
%Scullion, John: {\scshape BS 1235.3 S37 1992}\\
%Fox, Everett: {\scshape BS 1223 A3 F68 1995}\\
%Hamilton, Victor: {\scshape BS 1235.3 H323 1995}\\
%Hartley, John: {\scshape BS 1235.3 H37 2000}\\
%Towner, Sibley: {\scshape BS 1235.3 T69 2001}\\
%Walton, John: {\scshape BS 1235.53 W35 2001}\\
%Cotter, David: {\scshape BS 1235.52 C68 2003}\\
%Briscoe, Stuart: {\scshape BS 1151.2 C66 2004}\\
%McKeown, James: {\scshape BS 1235.53 M35 2008}\\
%Arnold, Bill: {\scshape BS 1235.53 A76 2009}\\
%Goldingay, John: {\scshape BS 1235.53 G65 2010}\\
%Reno, Russell: {\scshape BS 1235.53 R46 2010}\\
%Cook, Joan: {\scshape BS 1235.53 C66 2011}\\
%De La Torre, Miguel: {\scshape BS 1235.53 D4 2011}\\
%Coleson, Joseph: {\scshape BS 1235.53 C64 2012}\\
%Longman, Tremper: {\scshape BS 1235.53 L66 2016}
%\end{multicols}

\section{Course Outline}
\label{outline}

We will adhere to the schedule in \autoref{schedule} as closely as
possible, though the professor reserves the right to adjust it to suit
the needs of the class.

\setcolumncount{5}% set up \sessioncount, \unit{}, \noclass{}, and \reminder{memo}{date} macros
\begin{table}[htbp]% set to `p' to put the schedule on its own page
  \centering
  \begin{tabular}{>{\sessioncount.}r@{ }lccr}% make sure the column config agrees with \setcolumncount
	\toprule
	\sessionskip{\textbf{\S}.}&\textbf{Seminar}&\textbf{\cite{SGill}}&\textbf{\cite{NdeCW}}&\textbf{Date}\\
	\midrule

		& Psalm 1   & Chap. \thesession & deClaissé-Walford      & 10 Jan. \\
		& Psalm 2   & Chap. \thesession & Wittman                & 17 Jan. \\
		& Psalm 8   & Chap. \thesession & Nasuti, McCann         & 24 Jan. \\
		& Psalm 19  & Chap. \thesession & Gerstenberger, Gericke & 31 Jan. \\
		& Psalm 22  & Chap. \thesession & Jones, Petrany         &  7 Feb. \\
		& Psalm 49  & Chap. \thesession & Botha, K. Jacobson     & 14 Feb. \\
	\noclass{Term Break (Monday to Friday)}                      & 21 Feb. \\
		& Psalm 88  & Chap. \thesession & Ndoga, Magonet         & 28 Feb. \\
	\noclass{Grad Projects (Tuesday and Wednesday)}              &  7 Mar. \\
		& Psalm 90  & Chap. \thesession & Tucker                 & 14 Mar. \\
		& Psalm 110 & Chap. \thesession & Wallace                & 21 Mar. \\
		& Psalm 118 & Chap. \thesession & Flint                  & 28 Mar. \\
	\reminder{Exegetical essays are \textbf{due} by the start of the last class}{} \\
		& Psalm 147 & Chap. \thesession & R. Jacobson            &  4 Apr. \\

	\reminder{End of Term: Final marks are due for all courses}{12 Apr.} \\

	\bottomrule
  \end{tabular}
  \caption{Schedule of Readings}
  \label{schedule}
\end{table}

See the AST website for a list of other \href{http://www.astheology.ns.ca/students/academic-dates.html}{important dates}.

\section{Evaluation and Grade Structure}
\label{evaluation}

\begin{enumerate}

	\item The professor will set \textbf{reading prompts} throughout the
	semester, as often as once a week. Prompts will consist of questions
	drawn from the secondary reading, and so presuppose that students
	have read the assigned material carefully. Points may be deducted if
	it becomes evident that the reading has not been taken seriously.

	\item Students are to \textbf{memorize 12 verses of a psalm} and
	recite them to the professor privately, in his office, before the
	end of tenth week of class. Any psalm (or combination of psalms) is
	allowed unless you have memorized it before.

	\item Students must \textbf{creatively represent one psalm} in the
	class immediately following that psalm’s workshop (e.g., Psalm 2 in
	Week 3). Engage as many of the senses as possible, using whatever
	you can find or create. Be inventive! The only conditions are (a)
	that you explain or demonstrate a connection with the text studied
	and (b) that your presentation last between 5 and 8 minutes (plus 2
	minutes for questions).

	\item The last half of each week's class will be devoted to a
	\textbf{seminar-style discussion} of an individual psalm. Students
	will select a commentator for a period of 3--4 weeks, during which
	time they are responsible to report on the the author's commentary
	and bring its insight to bear on the seminar discussions. How should
	you prepare?

	\begin{enumerate}

		\item Read the primary seminar text closely and carefully. Look
		for distinctive words, themes, and images in the psalm, and stay
		alert to intertextual connections between it and other biblical
		literature. Jot down your observations.

		\item Consult your designated commentary. It should be read
		carefully, too, but after you have got a sense for the psalm on
		its own. One good approach might be to read the psalm twice,
		make some preliminary notes, and then study your commentator and
		fill out your preliminary notes.

		\item Augment your knowledge of each commentary you study by
		reading about its place in reception history. Key recourses are
		listed in \autoref{horbib}, below (see especially Magne Sæbø's
		comprehensive reference work, \emph{HB/OT}). Remember that you
		will be the resident authority on your chosen commentator.

	\end{enumerate}

	\item Students are to compose an \textbf{exegetical essay} on one of
	the psalms from the seminar. Consider all the perspectives brought
	to bear in class on a psalm of your choice, noting anything useful
	for your discussion, and then dig deeper into the text and its
	history. Your work should be aided by the preliminary researches of
	your classmates, but you will need to read more widely on your own;
	the seminar is only a starting point. You are expected to develop a
	strong thesis, and to interact with a healthy representation of
	secondary literature. The final paper is be due at the start of the
	last class.

\end{enumerate}

The breakdown for the semester's total work is shown in
\autoref{grade-dist}.

\begin{table}[htbp]
  \centering
  {\lining
  \begin{tabular}{lr}
    \toprule
    Reading Promtps         & 15\% \\
    Psalm Memorization      & 10\% \\
    Creative Representation & 15\% \\
    Seminar Contributions   & 20\% \\
    Final Paper             & 40\% \\
    \bottomrule
  \end{tabular}}
  \caption{Distribution of Grades}
  \label{grade-dist}
\end{table}

\input{\policy/grades}
\input{\policy/other}

\section{Additional Bibliography}
\label{bibliography}

For the weekly Psalms seminar, students should focus on a commentator
from the list below and give a short (5 minute) overview of the
interpretation of the psalm in question. Be sure to work with three
different commentators over the semester, from at least two different
major periods. (For those with the language skills, registering notes on
Hebrew, Aramaic, Greek, or Latin versions can be one selection.) The
goal is to gain maximum insight into the message of the Psalms by close
attention to text, translation, and commentary.

\subsection{Ancient Sources}
\label{oldbib}

\begin{enumerate}

 \item Versions
  \begin{enumerate}

	\item John R. Kohlenberger, III, ed., \emph{The Comparative Psalter: Hebrew-Greek-English} (Oxford: Oxford University Press, 2007)[Ref BS 1419 2007]. Very useful, but not to be mistaken for a critical edition or a full account of ancient versions.

	\item The Septuagint/Old Greek (LXX/OG) is available in \href{http://ccat.sas.upenn.edu/ioscs/editions.html}{two main editions}, each with major and minor editions. A. Rahlfs produced the Göttingen Septuagint's \emph{editio maior} of \emph{Psalmi cum Odis} in 1931 (3rd ed., 1979).

	\item Vulgate/Jerome: Biblia Sacra Latina [\href{https://www.biblegateway.com/versions/?action=getVersionInfo&vid=4}{online}].

	\item Targumim: \emph{The Aramaic Bible, Vol. 16: The Targum of the Psalms} (trans. David M. Stec; Collegeville, Minn: Liturgical Press, 2004) [BS 709.2 B5 1987 vol.16]. Also, \href{http://targum.info/targumic-texts/targum-psalms/}{Edward Cook's translation is available online}.

  \end{enumerate}
 \item Early Church / Synagogue
  \begin{enumerate}

	\item John Chrysostom, \emph{Commentary on the Psalms} (trans. R.\,C. Hill; 2 vols.; Brookline, Mass.: Holy Cross Orthodox Press, 1998) [BS 1430.3 J63 1998].

	\item Augustine, \emph{Expositions of the Psalms} (trans. M. Boulding; 6 vols.; Hyde Park, N.Y.: New City Press, 2000--2004). Older English translations of \emph{Enarrationes in Psalmos} appear in the Ancient Christian Writers series (trans. S. Hebgin, F. Corrigan; Westminster, Md., Newman Press, 1960--) and in \href{http://www.ccel.org/ccel/schaff/npnf108.toc.html}{P. Schaff's NPNF translation, first printed 1847--57 and now online}. For the Latin original see Corpus Scriptorum Ecclesiasticorum Latinorum (CSEL), vols. 93--95.

	\item Diodore of Tarsus, \emph{Commentary on Psalms 1--51} (trans. R.\,C. Hill; Atlanta: SBL, 2005) [BR 65 D393 D5613 2005].

	\item Theodoret of Cyrus, \emph{Commentary on the Psalms} (trans. R.\,C. Hill; 2 vols; Washington, DC: Catholic University of America Press, 2000--2001).

	\item Theodore of Mopsuestia, \emph{Commentary on Psalms 1--81} (trans. R.\,C. Hill; Atlanta: SBL, 2006).

	\item Cassiodorus, \emph{Explanation of the Psalms} (trans. P.\,G. Walsh; New York: Paulist Press, 1990--1991) [BR 60 A35 no. 51--53].

	\item Midrash Tehillim / \emph{Midrash on the Psalms, Translated from the Hebrew and Aramaic} (trans. W.\,G. Braude; 2 vols.; New Haven: Yale University Press, 1959).

  \end{enumerate}
 \item Medieval
  \begin{enumerate}

	\item Aquinas, \emph{Postilla super Psalmos / Commentary on the Psalms} (1272--1273). A Latin--English parallel edition for (most of) Psalms 1--54, ed. by Stephen Loughlin, is \href{http://www4.desales.edu/~philtheo/loughlin/ATP/}{online as part of the Aquinas Translation Project}. See also: Thomas Ryan, \emph{Thomas Aquinas as Reader of the Psalms} (Notre Dame: University of Notre Dame Press, 2000).

	\item \emph{Rashi’s Commentary on Psalms} (trans. Mayer I. Gruber; Leiden: Brill, 2004) [BS 1429 R3713 2007].% See also: Hermann Hailperin, \emph{Rashi and the Christian Scholars} (Pittsburgh: University of Pittsburgh Press, 1963).

  \end{enumerate}
 \item Reformation Era
  \begin{enumerate}

	\item Desiderius Erasmus (1466--1536): \emph{Expositions of the Psalms} (Collected Works of Erasmus, Vol. 63--65; Toronto: University of Toronto Press, 1997, 2005, 2010) [CWE 63: Pss 1, 2, 3, 4; CWE 64: Pss 88, 22, 28, 33; CWE 65: Pss 38, 83, 14].

	\item Martin Luther (1483--1546): \emph{Werke}, 35 = \emph{Luther’s Works}, 10--14 [BR 330 E5 1955]. See also: J.\,S. Preus, \emph{From Shadow to Promise: Old Testament Interpretation from Augustine to the Young Luther} (Cambridge, Mass.: Belknap, 1969).

	\item John Calvin (1509--1564): \emph{Commentary on the Psalms} (1557--, ET 1839--). All of Calvin's commentaries are available online, in English translation, at the \href{http://www.ccel.org/}{Christian Classics Ethereal Library}: Psalms \href{http://www.ccel.org/ccel/calvin/calcom08.html}{1--35}, \href{http://www.ccel.org/ccel/calvin/calcom09.html}{36--66}, \href{http://www.ccel.org/ccel/calvin/calcom10.html}{67--92}, \href{http://www.ccel.org/ccel/calvin/calcom11.html}{93--119}, \href{http://www.ccel.org/ccel/calvin/calcom12.html}{119--150}. See also: Herman J. Selderhuis, \emph{Calvin's Theology of the Psalms} (Grand Rapids: Baker Academic, 2007).

  \end{enumerate}
 \item Early Modern / Modern / Critical
  \begin{enumerate}

	\item Select an example from \autoref{supplementary} or nominate an early modern or modern commentator of your own discovery.

	\item If you have language skills beyond English this is an opportunity to put them to use. See the first pages of F.-L. Hossfeld and E. Zenger, \emph{Psalms 2: A Commentary on Psalms 51--100} (Minneapolis: Fortress, 2005) and \emph{Psalms 3: A Commentary on Psalms 101--150} (Minneapolis: Fortress Press, 2011), for lists of commentaries in an array of European languages.

  \end{enumerate}

\end{enumerate}

\subsection{Other Literature on the Psalms and Reception History}
\label{horbib}

\begin{itemize}

	\item Ancient Christian Commentary on Scripture, OT Vols. 7--8:
	  Craig A. Blaising and Carmen Hardin, eds., \emph{Psalms 1--50} (Downers Grove: InterVarsity Press, 2008) and
	  Quentin F. Wesselschmidt and Thomas C. Oden, eds., \emph{Psalms 51--150} (Downers Grove: InterVarsity Press, 2007).

	\item Willaim Holladay, \emph{The Psalms through Three Thousand Years: Prayerbook of a Cloud of Witnesses} (Minneapolis: Fortress, 1993).

	\item H. Attridge and M. Fassler, eds., \emph{Psalms in Community: Jewish and Christian Textual, Liturgical, and Artistic Traditions} (Leiden: Brill, 2004).

	\item Susan Gillingham, \emph{Psalms Through the Centuries, Vol. 1} (Oxford: Blackwell, 2008) offers an \href{http://www.blackwellpublishing.com/pdf/9780631218555.pdf}{expanded online bibliography (PDF)}. Volume 2 has not yet appeared, but see her \emph{A Journey of Two Psalms: The Reception of Psalms 1 and 2 in Jewish and Christian Tradition} (Oxford: Oxford University Press, 2013) and \emph{Jewish and Christian Approaches to the Psalms: Conflict and Convergence} (Oxford: Oxford University Press, 2013).

	\item M. Sæbø, \emph{HB/OT}: For help with specific periods and commentators in biblical reception history see Magne Sæbø, ed., \emph{Hebrew Bible/Old Testament: The History of Its Interpretation} (3 vols.; Göttingen: Vandenhoeck \& Ruprecht, 1996--2015).

\end{itemize}

\end{document}