% Copyright (c) 2018 by Daniel R. Driver.
% !TEX encoding = UTF-8 Unicode
% !TEX TS-program = XeLaTeX

\documentclass[titlepage]{article}

% This document presumes a file structure and set of inputs that are
% available at: git@github.com:danieldriver/syllabi.git

\newcommand\policy{../policy}
\newcommand\incl{../includes}
\input{\incl/variables}

%\onlinetrue % \Int{true}{false}
\coursecode[3.0]{HB 3113(Int)}
\coursetitle{The Ten Commandments}

% Taught as RLGS 3113 in:
%   - Winter 2012
% Taught as BSTH 3213 in:
%   - Winter 2015
% Taught as HB 3113(Int) in:
%   - Winter 2018

\professor{Daniel R. Driver}
\phone{902-425-7051}
\email{ddriver@astheology.ns.ca}
\officehours{Tuesdays, 2:00--4:00 \PM}

\semester{Winter Term 2018}
\meets{Mondays}% \meets{on}{at}{in}
      {From 9:00 \AM}
      {Online}
\website{astheology.ns.ca}
\cdescription{% copy from the current Academic Calendar
	As the first words spoken by God at Sinai and the leading terms of a
	covenant sealed with blood, the Ten Commandments are well known as
	the preeminent instance of biblical law. Less well appreciated is
	the complex legal and cultic context that gave rise to multiple
	versions of the Decalogue in ancient Israel, as seen in Exodus 20,
	Deuteronomy 5, Exodus 34, and Leviticus 19.

	This course examines the ancient origins of the Ten Commandments as
	a premier example of the Bible’s legal traditions. It also considers
	the weight that these laws have held for Jews, Christians, and
	others through an exploration of the Decalogue’s reception history,
	which includes modes of expression as diverse as liturgy, biblical
	commentary, fine art, film, and popular culture. Finally, with ample
	time to consider a commandment per week, the course invites students
	to reflect creatively on the ethical trajectory of the commandments,
	their place in contemporary religious life, and their stature in and
	beyond the Christian Church. \emph{Prerequisite: \textsc{BF} 1001.}
}% end of course description
\objectives{% recall Bloom's taxonomy: http://www.celt.iastate.edu/teaching/RevisedBlooms1.html
By the end of the course students should be able to:
	know the Ten Commandments in order;
	locate at least three versions of the Ten Commandments in the Bible;
	differentiate biblical versions by their contents;
	interpret each of the Commandments in their immediate literary context;
	integrate an understanding of the Ten Commandments with a broader view of biblical law;
	summarize the way different religious traditions count to Ten;
	compare the ways the Commandments have been interpreted in history;
	identify, evaluate, and report on contemporary connections with at least one of the Ten Commandments.
}% end of learning objectives

\input{\incl/preamble}

\begin{document}
\input{\incl/title}

  \section{Learning Objectives}
  \label{objectives}

  \edobject

\section{Required Texts \& Materials}
\label{texts}

The following texts are required. Students are strongly encouraged to
purchase their own copies. \href{http://danieldriver.com/courses/hb-3113/#required-texts-winter-2018}{Links to help you order the correct editions} are on the professor's website.

\begingroup
\renewcommand{\section}[2]{}% temporarily remove the section heading
\begin{thebibliography}{Reflections}% use the longest item in the bibliography

	\bibitem[Reflections]{Reflections} Carl E. Braaten and Christopher R. Seitz, eds.
	\emph{I Am the Lord Your God: Christian Reflections on the Ten Commandments}.
	Grand Rapids: Eerdmans, 2005.
	\textsc{isbn} 978-0802828125.

	\bibitem[Coogan]{Coogan} Michael Coogan.
    \emph{The Ten Commandments: A Short History of an Ancient Text}.
    New Haven: Yale University Press, 2014.
    \textsc{isbn} 978-0300178715.

	\bibitem[Centuries]{Centuries} Jeffrey P. Greenman and Timothy Larsen, eds.
	\emph{The Decalogue through the Centuries: From the Hebrew Scriptures to Benedict XVI}.
	Louisville: Westminster John Knox, 2012.
	\textsc{isbn} 978-0664234904.

	\bibitem[Miller]{Miller} Patrick D. Miller.
    \emph{The Ten Commandments (Interpretation)}.
    Louisville: Westminster John Knox, 2009.
    \textsc{isbn} 978-0664230555.

\end{thebibliography}
\endgroup

If you do not have access to a good study Bible, I recommend either the
NRSV (Michael Coogan, ed.) or the NJPS (Adele Berlin and Marc Zvi
Brettler, eds.), both published by Oxford University Press.

\section{Supplementary Texts}
\label{supplementary}

The following titles may be referenced as supplementary texts. They are
not required. Other supplementary materials may be provided through the
course website.

\begingroup
\renewcommand{\section}[2]{}% temporarily remove the section heading
\begin{thebibliography}{3}% use the longest item in the bibliography

	\bibitem{VanHarn} Roger E. Van Harn, ed.
	\emph{The Ten Commandments for Jews, Christians, and Others}.
	Grand Rapids: Eerdmans, 2007.
	\textsc{isbn} 978-0802829658.

	\bibitem{Heschel} Abraham Heschel.
	\emph{The Sabbath: Its Meaning for Modern Man}.
	New York: Farrar, Straus and Giroux, 1951 (repr. 2005).
	\textsc{isbn} 978-0374529758.

\end{thebibliography}
\endgroup

\section{Course Outline}
\label{outline}

We will adhere to the schedule in \autoref{schedule} as closely as
possible, though the professor reserves the right to adjust it to suit
the needs of the class.

Note that readings are listed by the textbook's key word and chapter
number, except in the case of \cite{Reflections}, where readings are
listed by the author's surname.

\setcolumncount{6}% set up \sessioncount, \unit{}, \noclass{}, and \reminder{memo}{date} macros
\begin{table}[htbp]% add p to put the schedule on its own page
  \centering
  \begin{tabular}{>{\sessioncount.}r@{ }llllr}% make sure the column config agrees with \setcolumncount
	\toprule
	\sessionskip{\textbf{\S.}}&\textbf{Topic}&\textbf{Exposition}&\textbf{History}&\textbf{Reflections}&\textbf{Date}\\
	\midrule
		& Introduction &              & Coogan 1        &              &  8 Jan. \\
		& First Word   & Miller Intro & Coogan 2–4      & D.\,B. Hart  & 15 Jan. \\
		& Second Word  & Miller 1     & Coogan 5–6      & C. Seitz     & 22 Jan. \\
		& Third Word   & Miller 2     & Coogan 7–end    & E. Radner    & 29 Jan. \\
		& Fourth Word  & Miller 3     & Centuries 1     & M. Bockmuehl &  5 Feb. \\
		& Fifth Word   & Miller 4     & Centuries 2–3   & P. Turner    & 12 Feb. \\
	\reminder{Review Essay: Due before midnight at the end of Week Six}{16 Feb.} \\
	\noclass{Reading Week}                                             & 19 Feb. \\
		& Sixth Word   & Miller 5     & Centuries 4–5   & W. Cavanaugh & 26 Feb. \\
		& Seventh Word & Miller 6     & Centuries 6–7   & R. Jenson    &  5 Mar. \\
		& Eighth Word  & Miller 7     & Centuries 8–9   &              & 12 Mar. \\
		& Ninth Word   & Miller 8     & Centuries 10–11 & Hütter; Braaten & 19 Mar. \\
		& Tenth Word   & Miller 9     & Centuries 12    & R.\,R. Reno  & 26 Mar. \\
	\reminder{Final Paper: Due before midnight at the end of Week Eleven}{30 Mar.} \\
	\noclass{Easter}                                                &  2 Apr. \\
		& Conclusion   & Miller –end  & Centuries 13    & Wilken; Meilaender & 9 Apr. \\
	\bottomrule
  \end{tabular}
  \caption{Schedule of Readings}
  \label{schedule}
\end{table}

See the AST website for a list of other \href{http://www.astheology.ns.ca/students/academic-dates.html}{important dates}.

\section{Evaluation}
\label{evaluation}

\subsection{Grade Structure for \ccode}
\label{structure}

\begin{enumerate}

	\item I will set \textbf{discussion prompts} for each of the Ten
	Commandments. They are intended to help you engage with the assigned
	reading material, and with your classmates. Prompt responses should
	be about 250 words long, and are due by the start of each class (9
	\AM\ Atlantic Time). You must also read through all other responses
	and post another 50 words or so as you interact with some (not all)
	classmates. Start your own thread by morning, and respond to other
	threads by the end of the class day.

	\item Students are to make a \textbf{creative presentation} on one
	of the Ten Commandments in the week in which that Commandment is
	under investigation. If you want to address the first commandment,
	for example, you need to complete your work for week two. The
	presentation may take the form of a podcast or video, and it may be
	anything that merits the adjective “creative” -- an interview, a
	dramatic piece, some form of engagement with culture, or anything
	else suitable that you envision. It should last 15 to 20 minutes,
	and it should feel like it deserves 25\% of your final grade. The
	only strict requirement is that the work be sharable by URL. (Try
	SoundCloud or YouTube.)

	\item A \textbf{review essay} on Coogan's \emph{The Ten
	Commandments} will be due at the end of the sixth week of class
	(Friday, 16 February 2018). It should be 2,500 words long, plus or
	minus 10\%. Roughly one third of the essay should be a summary of
	the work, while the remaining two thirds should be critical
	engagement and evaluation.

	\item A comprehensive \textbf{final paper} will give students an
	opportunity to explore one of the Ten Commandments in detail,
	complete with a thesis that involves original exposition and
	theological reflection. It is due at the end of the eleventh week of
	class (Friday, 30 March 2018). It should be 3,500 words long, plus
	or minus 10\% (the total count includes footnotes but not the final
	bibliography).

\end{enumerate}

The breakdown for the semester's total work is shown in
\autoref{grade-dist}.

\begin{table}[htbp]
  \centering
  {\lining
  \begin{tabular}{lr}
    \toprule
    Weekly Prompts & 25\% \\
    Presentation   & 25\% \\
    Review Essay   & 25\% \\
    Final Paper    & 25\% \\
    \bottomrule
  \end{tabular}}
  \caption{Distribution of Grades}
  \label{grade-dist}
\end{table}

\input{\policy/grades}
\input{\policy/other}

\end{document}
