% Copyright (c) 2018 by Daniel R. Driver.
% !TEX encoding = UTF-8 Unicode
% !TEX TS-program = XeLaTeX

\documentclass[titlepage]{article}

% This document presumes a file structure and set of inputs that are
% available at: git@github.com:danieldriver/syllabi.git

\newcommand\policy{../policy}
\newcommand\incl{../includes}
\input{\incl/variables}

%\onlinetrue % \Int{true}{false}
\coursecode[2.0.2]{HB 3114}
\coursetitle{The Twelve Prophets}

% Taught as RLGS 3143 in:
%   - Winter 2010
%   - Winter 2013
% Taught as HB 3114 in:
%   - Winter 2018

\professor{Daniel R. Driver}
\phone{902-425-7051}
\email{ddriver@astheology.ns.ca}
\officehours{Tuesdays, 2:00--4:00 \PM}

\semester{Winter Term 2018}
\meets{Tuesdays}% \meets{on}{at}{in}
      {9:00--11:30 \AM}
      {Classroom 3}
\website{astheology.ns.ca}
\cdescription{% copy from the current Academic Calendar
	Ben Sira writes of “the bones of the Twelve Prophets,” asking that
	they may “send forth new life from where they lie, for they
	comforted the people of Jacob and delivered them with confident
	hope” (Sirach 49:10). It is a tantalizingly early reference to the
	association of Twelve Prophets brought together in the Hebrew
	Bible’s last book of Prophets, a collection later known as The Book
	of the Twelve. It is also a pregnant anticipation of the manifold
	ways in which the words of these prophets have spoken far beyond
	their original circumstances.

	To better understand the origins and impact of The Book of the
	Twelve, this course will look at its redactional history and
	editorial shaping, its final canonical forms, and its effects as
	biblical prophecy. It will introduce current issues in scholarly
	debate about The Twelve while also exploring ways that The Twelve
	meet the ancient expectation that they can “send forth new life”
	amidst the people of God. In broad terms, the course offers an
	encounter with several individual texts embedded in a wider biblical
	tradition, and an opportunity to see how together “the goodly
	fellowship of the Prophets” witnesses to long-term works of
	providence as judgment and mercy converge in “the great and terrible
	Day of the Lord” (Malachi 4:5).
	\emph{Prerequisite: \textsc{BF} 1001.}
}% end of course description
%\objectives{% recall Bloom's taxonomy: http://www.celt.iastate.edu/teaching/RevisedBlooms1.html
%By the end of the course students should be able to:
%}% end of learning objectives

\input{\incl/preamble}

\begin{document}
\input{\incl/title}

%  \section{Learning Objectives}
%  \label{objectives}
%
%  \edobject

\section{Required Texts \& Materials}
\label{texts}

The following texts are required. Students are strongly encouraged to
purchase their own copies. \href{http://danieldriver.com/courses/hb-3114/#required-texts-winter-2018}{Links to help you order the correct editions} are on the professor's website.

\begingroup
\renewcommand{\section}[2]{}% temporarily remove the section heading
\begin{thebibliography}{Theodoret}% use the longest item in the bibliography

	\bibitem[Two Sides]{Two} Ehud Ben Zvi and James D. Nogalski.
	\emph{Two Sides of a Coin: Juxtaposing Views on Interpreting the Book of the Twelve / the Twelve Prophetic Books}.
	Piscataway, NJ: Gorgias Press, 2009.
%	\textsc{isbn} 978-1607243038.

	\bibitem[Seitz]{Seitz} Christopher R. Seitz.
	\emph{The Goodly Fellowship of the Prophets: The Achievement of Association in Canon Formation}.
	Grand Rapids: Baker Academic, 2009.
%	\textsc{isbn} 978-0801038839.

	\bibitem[Jerome]{Jerome1} Jerome; Thomas P. Scheck, trans.
	\emph{Commentaries on the Twelve Prophets, Vol. 1 (Ancient Christian Texts)}.
	Downers Grove: IVP Academic, 2016.
%	\textsc{isbn} 978-0830829163.

	\bibitem[Theodoret]{Theodoret} Theodoret; Robert C. Hill, trans.
	\emph{Theodoret of Cyrus: Commentary on the Twelve Prophets}.
	Brookline, MA: Holy Cross Orthodox Press, 2006.
%	\textsc{isbn} 978-1885652768.

\end{thebibliography}
\endgroup

If you do not have access to a good study Bible, I recommend either the
NRSV (Michael Coogan, ed.) or the NJPS (Adele Berlin and Marc Zvi
Brettler, eds.), both published by Oxford University Press.

\section{Supplementary Texts}
\label{supplementary}

The following titles may be referenced as supplementary texts. They are
not required. Other supplementary materials may be provided through the
course website.

\begingroup
\renewcommand{\section}[2]{}% temporarily remove the section heading
\begin{thebibliography}{3}% use the longest item in the bibliography

	\bibitem{Bickerman} Elias Bickerman.
	\emph{Four Strange Books of the Bible: Jonah, Daniel, Koheleth, Esther}.
	New York: Schocken Books, 1967.

	\bibitem{Hill} Hill, Robert C.
	\emph{Reading the Old Testament in Antioch}. Bible in Ancient Christianity 5.
	Leiden: Brill, 2005. Link: \href{http://ezproxy.astheology.ns.ca:2048/login?url=http://search.ebscohost.com/login.aspx?direct=true&db=nlebk&AN=173885&site=ehost-live&scope=site}{AST eBook}.

	\bibitem{Jerome2} Jerome; Thomas P. Scheck, ed.
	\emph{Commentaries on the Twelve Prophets, Vol. 2 (Ancient Christian Texts)}.
	Downers Grove: IVP Academic, 2017.

	\bibitem{Nogalski} James D. Nogalski.
	\emph{The Book of the Twelve (2 Volumes)}. Smyth \& Helwys Bible commentary.
	Macon, GA: Smyth \& Helwys, 2011. AST Reserve: BS 1560 N64/N635 2011

	\bibitem{Nog17} James D. Nogalski.
	\emph{The Book of the Twelve and Beyond: Collected Essays of James D. Nogalski}.
	Atlanta: SBL, 2017. Link: \href{http://ezproxy.astheology.ns.ca:2048/login?url=http://search.ebscohost.com/login.aspx?direct=true&db=nlebk&AN=1557940&site=ehost-live&scope=site}{AST eBook}

	\bibitem{Nogalski-Sweeney} James D. Nogalski and Marvin A. Sweeney, eds.
	\emph{Reading and Hearing the Book of the Twelve}. SBL Symposium Series.
	Atlanta: SBL, 2000.

	\bibitem{Redditt-Schart} Paul L. Redditt and Aaron Schart, eds.
	\emph{Thematic Threads in the Book of the Twelve}.
	Berlin: Walter de Gruyter, 2003.

	\bibitem{Sweeney} Marvin A. Sweeney.
	\emph{The Twelve Prophets (2 Volumes)}. Berit Olam commentary.
	Collegeville, MN: Liturgical, 2000. AST Reserve: BS 1560 S94 2000, Vols 1 \& 2

	\bibitem{Watts-House} James W. Watts and Paul R. House, eds.
	\emph{Forming Prophetic Literature: Essays on Isaiah and the Twelve in Honor of John D.W. Watts}.
	Sheffield: Sheffield Academic, 1996.

\end{thebibliography}
\endgroup

\section{Course Outline}
\label{outline}

We will adhere to the schedule in \autoref{schedule} as closely as
possible, though the professor reserves the right to adjust it to suit
the needs of the class.

\setcolumncount{3}% set up \sessioncount, \unit{}, \noclass{}, and \reminder{memo}{date} macros
\begin{table}[htbp]% add p to put the schedule on its own page
  \centering
  \begin{tabular}{>{\sessioncount.}r@{ }lr}% make sure the column config agrees with \setcolumncount
	\toprule
	\sessionskip{\textbf{\S.}}&\textbf{Seminar Text} (Commentaries follow suit)&\textbf{Date}\\
	\midrule
		& None: Introductions, overview of The XII &  9 Jan. \\
		& The entire Book of the XII, from Hosea to Malachi & 16 Jan. \\
		& Jonah 1–2                                         & 23 Jan. \\
		& Jonah 3–4                                         & 30 Jan. \\
	\reminder{Review Essay 1: Due by the end of Week Four}{2 Feb.} \\
		& Micah 1–4                                         &  6 Feb. \\
		& Micah 5–7                                         & 13 Feb. \\
	\noclass{Reading Week}                                  & 20 Feb. \\
		& Nahum 1–2                                         & 27 Feb. \\
		& None: Attend Grad Projects in lieu of regular class & 6 Mar. \\
	\reminder{Review Essay 2: Due by the end of Week Eight}{9 Mar.} \\
		& Nahum 3                                           & 13 Mar. \\
		& Habakkuk 1–2                                      & 20 Mar. \\
		& Habakkuk 3                                        & 27 Mar. \\
	\reminder{Final Paper: Due by the end of Week Eleven}{30 Mar.} \\
		& The entire Book of the XII, from Hosea to Malachi & 3 Apr. \\
	\bottomrule
  \end{tabular}
  \caption{Schedule of Readings}
  \label{schedule}
\end{table}

See the AST website for a list of other \href{http://www.astheology.ns.ca/students/academic-dates.html}{important dates}.

\section{Evaluation}
\label{evaluation}

\subsection{Grade Structure for \ccode}
\label{structure}

\begin{enumerate}

	\item Weekly \textbf{seminar discussions} will facilitate close work
	with text and interpretation in select books from The XII.  Students
	should come to class fully prepared to discuss the assigned
	material, which will ordinarily include one to three chapters of
	primary material per week, plus commentary on those chapters.
	Commentary includes \cite{Jerome1} and \cite{Theodoret} at a
	minimum, but will ideally be extended to other ancient and modern
	readers. The quality of participation will be assessed across the
	semester.

	\item A \textbf{first review essay}, on \cite{Two}, will be due at
	the end of the fourth week of class (Friday, 2 February 2018). It
	should be 2,500 words long, plus or minus 10\%. The first third of
	the essay should be a summary of the work, while the remaining two
	thirds should be devoted to critical engagement and evaluation.

	\item A \textbf{second review essay}, on \cite{Seitz}, will be due
	at the end of the eighth week of class (Friday, 9 March 2018). It
	should be 2,500 words long, plus or minus 10\%. The first third of
	the essay should be a summary of the work, while the remaining two
	thirds should be devoted to critical engagement and evaluation.

	\item A comprehensive \textbf{final paper} will give students an
	opportunity to explore one aspect of the Book of the XII, or a short
	passage from a prophetic book within The XII, in detail. The paper
	must have a thesis that involves original exposition of and
	theological reflection on a biblical text. It is due at the end of
	the eleventh week of class (Friday, 30 March 2018). It should be
	3,500 words long, plus or minus 10\% (the total count includes
	footnotes but not the final bibliography).

\end{enumerate}

The breakdown for the semester's total work is shown in
\autoref{grade-dist}.

\begin{table}[htbp]
  \centering
  {\lining
  \begin{tabular}{lr}
    \toprule
    Weekly Seminars & 25\% \\
    Review Essay 1  & 20\% \\
    Review Essay 2  & 20\% \\
    Final Paper     & 35\% \\
    \bottomrule
  \end{tabular}}
  \caption{Distribution of Grades}
  \label{grade-dist}
\end{table}

\input{\policy/grades}
\input{\policy/other}

\end{document}
