% Copyright (c) 2018 by Daniel R. Driver.
% !TEX encoding = UTF-8 Unicode
% !TEX TS-program = XeLaTeX

\documentclass[titlepage]{article}

% This document presumes a file structure and set of inputs that are
% available at: git@github.com:danieldriver/syllabi.git

\newcommand\policy{../policy}
\newcommand\incl{../includes}
\input{\incl/variables}

%\onlinetrue % \Int{true}{false}
\coursecode[3.5-WIP]{BF 1001}
\coursetitle[Biblical Foundations]{Hebrew Bible/Old Testament}

% Taught as RLGS 1013 in:
%   - Fall 2008
%   - Winter 2009
%   - Fall 2009
%   - Winter 2010
%   - Fall 2010
%   - Winter 2011 (Fall 2011 was covered by Joel Lohr in a course release)
%   - Winter 2012
%   - Fall 2012
%   - Winter 2013
% Taught as BSTH 1013 in:
%   - Fall 2013
%   - Winter 2014
%   - Fall 2014
%   - Winter 2015
%   - Fall 2015
%   - Winter 2016
% Taught as BF 1001 in:
%   - Fall 2016
%   - Fall 2017
%   - Fall 2017(Int - online section run parallel to campus course)
%   - Fall 2018

\professor{Daniel R. Driver}
\phone{902-425-7051}
\email{ddriver@astheology.ns.ca}
\officehours{Mondays, 3:45--4:30 \PM}

\semester{Fall Term 2018}
\meets{\Int{Thursdays}{Mondays}}% \meets{on}{at}{in}
      {1:00--3:30 \PM}
      {Classroom 3}
\website{astheology.ns.ca}
\cdescription{% copy from the current Academic Calendar
	The First Testament of Christian Scripture, also called the Hebrew
	Bible or Old Testament, is a fundamental part of Christian tradition
	and durable rule of faith and practice. Students in this course will
	therefore be introduced to historical and literary data important
	for understanding the origins of the Hebrew Bible and its subsequent
	function as Old Testament Scripture in a variety of cultural and
	religious contexts.

	The broad sweep of biblical tradition will be presented through a
	survey of representative books from the Law, the Prophets, and the
	Writings. To help foster an ecumenical outlook, primary readings
	from the Bible will be supplemented by case studies of classic
	Jewish and Christian readings of biblical texts. Students will
	develop their exegetical skills by studying these examples, and so
	learn to appreciate the diverse literary, canonical, cultural,
	historical, hermeneutical, and theological elements involved in
	biblical interpretation. In addition, the course will consider some
	ways that the Hebrew Bible/Old Testament can feature in the practice
	of ministry and in the spiritual practice of faith communities.
}% end of course description
\objectives{% recall Bloom's taxonomy: http://www.celt.iastate.edu/teaching/RevisedBlooms1.html
	By the end of the course students should be able to:
		name major Old Testament people and events;
		locate a few important biblical sites on a map;
		give key dates for Israel's history and summarize the succession of superpowers in the Ancient Near Eastern political theatre from Egypt to Greece;
		recognize and cite examples of most genres of biblical literature;
%		defend a decision to pronounce or circumlocute the divine name;
		understand the general shape of the Masoretic Text tradition and differentiate it from other canonical orders;
		report on parallel and divergent material across the Law and the Prophets, such as the uses of the Divine Name or the rationales for sabbath observance;
		classify a variety of ancient and modern approaches to the Bible, including traditional “plain sense” and figural reading strategies as well as historical criticism and its legacy.

	Students should also be able to identify settings in which the
	Scriptures of Israel are read (notably the synagogue, church, and
	academy), employ terminology appropriate to these communities,
	recognize where their own biographies place them in relation to the
	Hebrew Bible/Old Testament and its uses, and monitor and test their
	individual attitudes and assumptions. They should be able to extend
	their awareness of the Bible's contemporary readers to the Bible's
	long history of reception. Finally, students should begin to infer
	what Jesus meant in speaking of ``the law of Moses, the prophets,
	and the psalms'' (Luke 24:44), and so learn to hear claims about New
	Testament fulfilment of scripture in light of the unique voice that
	the Old Testament retains along side of the New in Christian
	Scripture.
}% end of learning objectives

\input{\incl/preamble}

\begin{document}
\input{\incl/title}

  \section{Learning Objectives}
  \label{objectives}

  \edobject

\section{Required Texts \& Materials}
\label{texts}

The following texts are required. Students are strongly encouraged to
purchase their own copies. Library copies that are not reference works
have been placed on a 2-hour reserve.

\begingroup
\renewcommand{\section}[2]{}% temporarily remove the section heading
\begin{thebibliography}{Irenaeus}% use the longest item in the bibliography

	\bibitem[NRSV]{nrsv} M.\,D. Coogan, ed.
    \emph{New Oxford Annotated Bible with Apocrypha: NRSV}. 5th ed.
    Oxford / New York: Oxford University Press, 2018.
    ISBN 978-0190276089.

	\bibitem[HBFB]{hbfb} J. Kaminsky and J. Lohr.
	\emph{The Hebrew Bible for Beginners: A Jewish and Christian Introduction}.
	Nashville: Abingdon Press, 2015.
	ISBN 978-1426775635.

%	\bibitem[Heschel]{heschel} Abraham Heschel.
%	\emph{The Sabbath: Its Meaning for Modern Man}.
%	New York: Farrar, Straus and Giroux, 1951 (repr. 2005).
%	ISBN 978-0374529758.

%	\bibitem[Irenaeus]{irenaeus} St Irenaeus of Lyons.
%	\emph{On the Apostolic Preaching}.
%	Trans. John Behr.
%	Crestwood, NY: St Vladimir’s Seminary Press, 1997.
%	ISBN 978-0881411744.

\end{thebibliography}
\endgroup

An acceptable alternative study Bible is the NJPS: Adele Berlin and Marc
Zvi Brettler, eds., \emph{The Jewish Study Bible: Second Edition}
(Oxford / New York: Oxford University Press, 2014). A reference copy is
available in the library, and it is well worth consulting.

\section{Supplementary Texts}
\label{supplementary}

Supplementary readings will be recommended throughout the semester.
Excerpts from this literature will either be placed on reserve or made
available through the course website. Give this material some good
attention and effort. Some readings may have assignments attached to
them, but even if not, the selections represent some of the best
contemporary readers of the HB/OT, and you will not want to miss out on
their hermeneutical and theological insights.

In addition, the following reference works are worth owning and
consulting. First, \cite{rlgs} includes sound advice on things like
reading religious texts, writing essays and book reviews, making oral
presentations, and learning languages. Second, \cite{sbl2} is a standard
reference in the field, useful to beginning students and specialists in
biblical studies alike.

\begingroup
\renewcommand{\section}[2]{}% temporarily remove the section heading
\begin{thebibliography}{9}% use the longest item in the bibliography

	\bibitem{rlgs} Northey, Margot, Bradford A. Anderson, and Joel N. Lohr.
	\emph{Making Sense in Religious Studies: A Student's Guide to Research and Writing}.
	3rd ed. Don Mills, ON: Oxford University Press, 2019. ISBN 978-0199026838.

	\bibitem{sbl2} Collins, Billie Jean, et al.
	\emph{The SBL Handbook of Style}.
	2nd ed. Atlanta: SBL Press, 2014. % ISBN 978-1589839649.
	Designed to augment \href{http://www.chicagomanualofstyle.org/home.html}{\emph{The Chicago Manual of Style}},
	which is the standard at AST, there is also a free
	“\href{https://www.sbl-site.org/assets/pdfs/pubs/SBLHSsupp2015-02.pdf}{Student Supplement for \emph{The SBL Handbook of Style}, Second Edition}.”

\end{thebibliography}
\endgroup



\section{Course Outline}
\label{outline}

We will adhere to the schedule in \autoref{schedule} as closely as
possible, though the professor reserves the right to adjust it to suit
the needs of the class.

\newcommand\HBFB[1]{\cite[#1]{hbfb}}

\setcolumncount{5}% set up \sessioncount, \unit{}, \noclass{}, and \reminder{memo}{date} macros
\begin{table}[htbp]% set to `p' to put the schedule on its own page
  \centering
  \begin{tabular}{>{\sessioncount.}r@{ }lllr}% make sure the column config agrees with \setcolumncount
	\toprule
	\sessionskip{\textbf{\S}.}&\textbf{Primary (chapters)}&\textbf{Secondary (pgs)}&\textbf{Supplement (author)}&\textbf{Due}\\
	\midrule

	\unit{Law / Torah / Pentateuch} \\

		& Genesis 1--11        & \HBFB{1--26}    & Ellen Davis           & \Int{14}{12} Sep. \\
		& Genesis 12--50       & \HBFB{27--64}   & Jon Levenson          & \Int{21}{19} Sep. \\
		& Exodus 1--34         & \HBFB{65--83}   & C. Mathews McGinnis   & \Int{28}{26} Sep. \\
		& Leviticus 1--16      & \cite[all]{heschel} & Gary Anderson     & \Int{ 5}{ 3} Oct. \\
		& Deuteronomy          & \HBFB{85--99}   & R.W.L. Moberly        & \Int{12}{10} Oct. \\ [1ex]

	\unit{Prophets: Former \textit{\&} Latter} \\

	\reminder{First paper is \textbf{due} before midnight on the sixth day of class}{}       \\
		& Joshua, Judges       & \HBFB{103--121} & Phyllis Trible        & \Int{19}{17} Oct. \\
		& 1 \& 2 Samuel        & \HBFB{123--143} & Stephen Chapman       & \Int{26}{24} Oct. \\
	\noclass{Term Break (Monday to Friday)}                              & \Int{2 Nov.}{31 Oct.} \\
		& 1 \& 2 Kings         & \cite[all]{irenaeus} & Robert Alter     & \Int{ 9}{ 7} Nov. \\ [1ex]

		& Isaiah 1--12, 36--40 & \HBFB{145--168} & Brevard Childs        & \Int{16}{14} Nov. \\
		& Hosea--Jonah         & \HBFB{169--184} & Christopher Seitz     & \Int{23}{21} Nov. \\ [1ex]

	\unit{Writings: Wisdom \textit{\&} Praise} \\

	\reminder{Second paper is \textbf{due} before midnight on the eleventh day of class}{}   \\
		& Psalms 1--8, 90, 110, 118 & \HBFB{187--202} & Gerald Sheppard  & \Int{30}{28} Nov. \\
		& Ecclesiastes         & \HBFB{203--246} & Katharine Dell        & \Int{ 7}{ 5} Dec. \\ [1ex]

	\reminder{End of Term: Final marks are due for all courses}{15 Dec.} \\

	\bottomrule
  \end{tabular}
  \caption{Schedule of Readings}
  \label{schedule}
\end{table}

See the AST website for a list of other \href{http://www.astheology.ns.ca/students/academic-dates.html}{important dates}.

\section{Evaluation}
\label{evaluation}

\subsection{Grade Structure for \ccode}
\label{structure}

\begin{enumerate}

	\item I will set \textbf{reading prompts} throughout the semester.
	They are designed to ensure that you have read the assigned material
	carefully, and to help you explore its significance. Prompt
	responses submitted online should be between 250 and 300 words long.

%	\item Students are to \textbf{memorize ten verses from the Psalms}
%	in the King James Version and recite them to me privately by the
%	last day of class. You may select ten verses from one psalm, one
%	verse from ten psalms, or any combination in between.

	\item Two \textbf{short papers} will facilitate student reflection
	on two extended works of biblical interpretation, one by
	\cite{heschel} and one by \cite{irenaeus}. Each should be 3,000
	words long. They are due on the sixth and eleventh days of class,
	respectively.

	\begin{enumerate}

		\item The \textbf{first paper} will articulate and evaluate
		multiple rationales for sabbath observance by interacting with
		biblical and post-biblical traditions. The latter must include,
		but need not be limited to, Heschel's \emph{The Sabbath}.

		\item The \textbf{second paper} will explore Irenaeus' use of
		the Old Testament as Christian scripture by: succinctly
		summarizing \emph{On the Apostolic Preaching}, selecting a
		characteristic example of biblical interpretation in that work,
		and then developing and defending a coherent thesis about that
		instance of interpretation.

	\end{enumerate}

\Int{
	\item Each student will \textbf{make an online presentation} on one
	of the twelve supplementary articles. It may take the form of a
	podcast or YouTube video, and should be sharable by URL. The
	discussion, which should last 20 minutes, should begin with a brief
	(5~min) summary of the article. The balance of the time should be
	spent helping other readers elaborate, reflect on, test, challenge,
	or extend the main ideas presented there.
}{
	\item Each student will \textbf{lead a seminar} on one of the twelve
	supplementary articles. The discussion, which should last 30
	minutes, should begin with a brief (5~min) summary of the article.
	The balance of the time should be spent helping the class elaborate,
	reflect on, test, challenge, or extend the main ideas presented
	there.
}

\end{enumerate}

The breakdown for the semester's total work is shown in
\autoref{grade-dist}.

\begin{table}[htbp]
  \centering
  {\lining
  \begin{tabular}{lr}
    \toprule
    Reading Prompts & 25\% \\
%    Memorization    & 10\% \\
    First Paper     & 25\% \\
    Second Paper    & 25\% \\
    \Int{Online}{Seminar} Presentation & 25\% \\
    \bottomrule
  \end{tabular}}
  \caption{Distribution of Grades}
  \label{grade-dist}
\end{table}

\input{\policy/grades}
\input{\policy/other}

\end{document}
