% Copyright (c) 2022 by Daniel R. Driver.
% !TEX encoding = UTF-8 Unicode
% !TEX TS-program = XeLaTeX

\documentclass[titlepage]{article}

% This document presumes a file structure and set of inputs that are
% available at: git@github.com:danieldriver/syllabi.git

\newcommand\policy{../policy}
\newcommand\incl{../includes}
\input{\incl/variables}

\coursecode[1.2.0]{HB/ST 3001}
\coursetitle[Hebrew Bible/Systematic Theology]{Christian Doctrine and\\[.8ex] the Old Testament}

% Taught as RLGS 4483 (a remote antecedent) at Tyndale UC in:
%   - Winter 2009 ("Biblical Theological Themes: The Old Testament as Christian Scripture")
% Taught as HB/ST 3001 (largely a new course) at AST in:
%   - Summer 2017 (Session 3: July 17-21 and 24-28)

\professor{Daniel R. Driver}
\phone{902-425-7051}
\email{ddriver@astheology.ns.ca}
\officehours{Daily, 12:15--12:45 \PM}

\semester{Summer Term 2017}
\meets{Mon–Fri, July 17–28}% \meets{on}{at}{in}
      {9:00--12:00 \AM}
      {Flahiff Room (Library)}
\website{danieldriver.com/courses/}
\cdescription{% copy from the current Academic Calendar
	What is the relationship of scripture and theology? Some answers to
	this question start with the Bible, while others begin with
	Christian doctrine, while still others call for a dialectical
	movement between canon and creed. However it is approached, the
	question presents a number of challenges.

	To illustrate the problem in general, and to outline some possible
	solutions, this course highlights a variety of current approaches to
	the Old Testament as the scripture of the Church. Students will
	encounter work by an array of biblical and theological specialists
	who transgress the conventional limits of their disciplines. They
	will study the views of Catholics, Protestants, Jews, and those who
	disavow religious affiliation. Because the Hebrew Bible is Jewish
	scripture in the first instance, students will consider why some
	Jews are not interested in biblical theology, and what it means for
	the Church to adhere to the Scriptures of Israel. Specific doctrines
	under consideration include: creation, sin, election, incarnation
	(the body of God), divine impassibility, Christology, Mariology, law
	and gospel, death and resurrection, and the afterlife.
}% end of course description
\objectives{% review Bloom's taxonomy: http://www.celt.iastate.edu/teaching/effective-teaching-practices/revised-blooms-taxonomy
            % or try this new one at Rice: http://cte.rice.edu/blogarchive/2017/2/23/taxonomy
	This course aims to do two things. (1) To offer an overview of the ecumenical core of Christian eucharistic theology. (2) To introduce and discuss some of the different perspectives on the Eucharist that shape ecumenical relations today.

	Inconveniently for us, early Christians didn’t write with us in mind. Almost all early Christian texts are written for “insiders” by “insiders”. There are no “So you’ve decided to become a Christian” pamphlets with detailed descriptions of their practices. If there were, we would have a much better sense of how they understood the bread they broke and the cup they drank. Instead, all we have are tantalising snippets – most of which you’ll read – from the early Church where they refer to their eucharistic practices. But how are we to understand these snippets? They make reference to Jewish and New Testament foundations, and so, before you read them, you’ll get acquainted with some of these sources. But from these scant sources you’ll be invited, in dialog with each other and the instructors, to develop your understanding of the Eucharist. What is it? A memorial meal? A symbolic re-enactment of the last supper? Golgotha continued as the hand of God reached out from the Triune life to weave us into union with God and each other? What is it? Does it do anything to you? If so, under what conditions is its potency greatest? Why do Roman Catholics ask non-Roman Catholics to refrain from taking communion at Roman Catholic Masses? Is this not ecumenical elitism – a refusal of the very unity the Eucharist symbolises (or instantiates)? We will be asking all these questions. We will be doing so in dialog with a subtheme of this course – the past and future of eucharistic sharing at AST. AST was at the forefront of post Vatican II Christian ecumenism and eucharistic sharing was commonplace. What needs to be in place for this to happen again? Is the eucharist an instrument for bringing about Christian unity? Is it a sacramental consummation of ontological unity – the sign of Christian oneness? Or, Is it an act of friendship between diverse and different strands of Christianity?

	In addition to exploring the Eucharist \emph{per se}, and the eucharist in ecumenical perspective, there is also an opportunity for each student to investigate particular aspects of eucharistic and/or ecumenical theology via the two main papers you will be writing in fulfillment of course requirements. Touch base with the instructors when something “grabs you”. We will be able to recommend readings as you follow your ideas where they lead.


	They should become familiar with
		a few major narratives about the relationship of Bible and Theology, and with
		different theories about how to frame knowledge of God (in terms apophatic and kataphatic, for example).
	They should be able to analyze and evaluate doctrinal claims
		by biblical scholars and theologians who use the OT as a core theological resource.
	Students should also develop curiosity about the role of Hebrew scripture in
		communities beyond the church, including in the academy and especially the synagogue.
		Their creativity and confidence in expressing their own ideas about the Scriptures of Israel should grow,
		even as they learn to do so with appropriate humility and charity.
	Finally, students should experience a process of discovery in dialogue with
		biblical traditions ancient and strange as they come to terms with their own ways
		of thinking and speaking about the God of Israel.
}% end of learning objectives

\input{\incl/preamble}

\begin{document}
\input{\incl/title}

\section{Learning Objectives}
\label{objectives}
\edobject

\section{Required Texts \& Materials}
\label{texts}

The following texts are required. Students are encouraged to purchase
their own copies. Library copies that are not already reference works
will be placed on a 1-hour reserve.

\begingroup
\renewcommand{\section}[2]{}% temporarily remove the section heading
\begin{thebibliography}{MacDonald}% use the longest item in the bibliography

	\bibitem[NRSV]{nrsv} M.\,D. Coogan, ed.
    \emph{New Oxford Annotated Bible with Apocrypha: NRSV}. 4th ed.
    Oxford / New York: Oxford University Press, 2010.
%    \textsc{isbn} 978-0195289602.

	\bibitem[Anderson]{anderson} Gary A. Anderson.
	\emph{Christian Doctrine and the Old Testament: Theology in the Service of Biblical Exegesis}.
	Grand Rapids: Baker Academic, 2017.
%	\textsc{isbn} 978-0801098253.

	\bibitem[MacDonald]{macdonald} Neil B. MacDonald.
	\emph{Metaphysics and the God of Israel: Systematic Theology of the Old and New Testaments}.
	Grand Rapids: Baker Academic, 2006.
%	\textsc{isbn} 978-0801032431.
	For those who are unable to find copies of this book for resale, the library's reserve copy should suffice to meet the needs of the class.

%	\bibitem[tk]{tk} tk.
%	\emph{tk}.
%	tk: tk, 20tk.
%	\textsc{isbn} 978-tk.

\end{thebibliography}
\endgroup

An acceptable alternative study Bible is the NJPS: Adele Berlin and Marc
Zvi Brettler, eds., \emph{The Jewish Study Bible: Second Edition}
(Oxford / New York: Oxford University Press, 2014). A reference copy is
available in the library, and it is well worth consulting.

\section{Supplementary Texts}
\label{supplementary}

Supplementary readings will be recommended throughout the course. In
particular, students are asked to explore relevant church statements
about Christian scripture, particularly the Old Testament. Resources
from the founding churches of AST include the following.

\begin{enumerate}

\item RCC: Roman Catholic Church

	\begin{enumerate}
	\item \href{}{\emph{Divino Afflante Spiritu}, the encyclical from Pope Pius XII [\href{http://www.bc.edu/schools/stm/crossroads/resources/deathofjesus/intro/the_catholic_approachtothebible.html}{overview}] (1943)}
	\item \href{}{\emph{Dei Verbum}, Vatican II's Dogmatic Constitution on Divine Revelation (1965)}
	\item PBC = Pontifical Biblical Commission: \emph{L'interprétation de la Bible dans l'Église}, \href{http://www.catholic-resources.org/ChurchDocs/PBC_Interp.htm}{The Interpretation of the Bible in the Church} (April 15, 1993)
	\item PBC: \emph{Le peuple juif et ses Saintes Écritures dans la Bible chrétienne}, \href{http://www.vatican.va/roman_curia/congregations/cfaith/pcb_documents/rc_con_cfaith_doc_20020212_popolo-ebraico_en.html}{The Jewish People and Their Sacred Scriptures in the Christian Bible} (May 24, 2001)
	\end{enumerate}

\item ACC: Anglican Church of Canada (one of 38 Provinces in the Anglican Communion)

	\begin{enumerate}
	\item Articles VI–VII of \href{https://www.churchofengland.org/prayer-worship/worship/book-of-common-prayer/articles-of-religion.aspx}{The Thirty-nine Articles of Religion} (1562)
	\item \href{http://anglicansonline.org/basics/Chicago_Lambeth.html}{The Chicago-Lambeth Quadrilateral} (1886, 1888)
	\item Paragraphs 52–62 of \href{http://www.anglicancommunion.org/resources/document-library.aspx?author=The+Windsor+Process&language=English}{The Windsor Report} [\href{http://www.anglicancommunion.org/media/68225/windsor2004full.pdf}{PDF}] (18 October 2004)
	\item \href{http://www.anglicancommunion.org/media/98131/Final-Report-for-the-web.pdf}{Bible in the Life of the Church (BILC) Project Report} (2012)
	\end{enumerate}

\item UCC: United Church of Canada

	\begin{enumerate}
	\item The UCC requires its ministers to be in ``\href{http://www.united-church.ca/community-faith/welcome-united-church-canada/what-we-believe}{essential agreement}'' with four doctrinal statements that are ``\href{http://www.united-church.ca/community-faith/welcome-united-church-canada/faith-statements}{subordinate to the primacy of scripture}'' (\href{https://commons.united-church.ca/Documents/What%20We%20Believe%20and%20Why/Theology%20and%20Mission%20of%20the%20Church/Our%20Words%20of%20Faith.pdf#search=study}{GC 41 2012 - 005}):
		\begin{enumerate}
			\item\href{http://www.united-church.ca/community-faith/welcome-united-church-canada/twenty-articles-doctrine-1925}{Twenty Articles of Doctrine} (1925)
			\item\href{http://www.united-church.ca/community-faith/welcome-united-church-canada/statement-faith-1940}{A Statement of Faith} (1940)
			\item\href{http://www.united-church.ca/community-faith/welcome-united-church-canada/new-creed}{A New Creed} (1968)
			\item\href{http://www.united-church.ca/community-faith/welcome-united-church-canada/song-faith}{A Song of Faith} (2006)
		\end{enumerate}
	\item \href{https://ecumenism.net/archive/docu/1992_ucc_authority_interpretation_scripture.pdf}{\emph{The Authority and Interpretation of Scripture: A Statement of the United Church of Canada}} (Toronto: UC Publishing House, 1992) [BS 480 U65 1992 -- \textbf{on reserve}]
	\item See also R.\,C. Fennell's series “How Does the United Church Interpret the Bible?” in \href{http://touchstonecanada.ca}{\emph{Touchstone}}, a Canadian journal of theology and heritage:
		\begin{enumerate}
			\item\href{http://touchstonecanada.ca/wp-content/uploads/2013/08/Article2_2008-051.pdf}{Part I, 1904–1940s: Tradition and Resistance} (26.2 [2008]: 13--24)
			\item\href{http://touchstonecanada.ca/wp-content/uploads/2013/08/3rdArticle_2008-09.pdf}{Part II, 1950s–1990s: Tradition and Liberation} (26.3 [2008]: 31--42)
			\item\href{http://touchstonecanada.ca/wp-content/uploads/2013/08/Touchstone_May_2011.pdf}{Part III: A Song of Faith} (29.2 [2011]: 21--29)
		\end{enumerate}
	\end{enumerate}

\end{enumerate}


\section{Course Outline}
\label{outline}

We will adhere to the schedule in \autoref{schedule} as closely as
possible, though the professor reserves the right to adjust it to suit
the needs of the class.

\setcolumncount{6}% set up \sessioncount, \unit{}, \noclass{}, and \reminder{memo}{date} macros
\begin{table}[htbp]% set to `p' to put the schedule on its own page
  \centering
  \begin{tabular}{>{\sessioncount.}r@{ }lcccr}% make sure the column config agrees with \setcolumncount
	\toprule
	\sessionskip{\textbf{\S}.}&\textbf{Topic}&\textbf{Anderson}&\textbf{MacDonald}&\textbf{OT Text}&\textbf{Date}\\
	\midrule

		& Approaches          & 1    & 1    & 1 Sam 4–6      & 17 July \\
		& Impassibility       & 2    & 2--4 & Jonah 1--4     & 18 July \\
		& Creation            & 3    & 5--6 & Gen 1--3       & 19 July \\
	\reminder{Articles of Faith \textbf{due} at the start of class four}{} \\
		& Original Sin        & 4    &      & Exod 32--34    & 20 July \\
		& Election            & 5    & 7--8 & Gen 12, 15, 17 & 21 July \\
	\noclass{Weekend}                                        & 22--23 July \\
		& Christology         & 6    & 9    & 1 Kings 8      & 24 July \\
		& Mariology           & 7    &      & 1 Sam 1--2     & 25 July \\
		& Faith \& Works      & 8--9 & 10   & Tobit 1--4     & 26 July \\
		& Atonement           & 10   & 11   & Tobit 12--14   & 27 July \\
	\reminder{Paper is \textbf{due} at the start of class ten}{}  \\
		& Accordance          &      &      & 2 Kings 17     & 28 July \\
	\reminder{End of Term: Final marks are due to the Registrar}{7 Aug.} \\

	\bottomrule
  \end{tabular}
  \caption{Schedule of Readings}
  \label{schedule}
\end{table}

See the AST website for a list of other \href{http://www.astheology.ns.ca/students/academic-dates.html}{important dates}.

\section{Evaluation and Grade Structure}
\label{evaluation}

Given the small class size this term, I have adopted a tutorial format
for \ccode.

\begin{enumerate}

	\item Each week you will write a 1000–1200 word essay responding to
	a prompt.

	\item Essays should interact thoughtfully with both primary and
	secondary sources, and should be \textbf{thesis-driven}. Your essay
	must argue a thesis, and not simply describe what you have learned
	or what others have argued. At the tutorial, you should know what
	you think about the question, and should be able to summarize the
	argument of your essay in one sentence.

	\item Reading preparation should always give priority of attention
	to the assigned primary texts. Secondary literature will be
	important in lending guidance to the essay, but scholarly opinions
	should always be assessed on the basis of how helpful they are in
	explaining the primary text.

	\item By email or Teams, please send me your essay as a Microsoft
	Word document by 4pm the day before class. Essays received on time
	will receive written feedback. Late essays are not guaranteed
	written feedback. If you do not provide an essay at all, class may
	be cancelled. Essays will not be accepted after class (with rare
	exceptions).

	\item Written feedback will be returned by email or on Teams
	following discussion in the tutorial. Marks will not be assigned to
	the essays initially, and only in two cases later. Instead,
	affirmation and redirection will be provided as needed.

	\item Select two of your best essays to revise and resubmit for a
	formal mark. Both essays must be submitted before the last day of
	class. You can opt to submit them early.

\end{enumerate}

The breakdown for the semester's total work is shown in
\autoref{grade-dist}.

\begin{table}[htbp]
  \centering
  {\lining
  \begin{tabular}{lr}
    \toprule
    Completion of All Essays      & 70\% \\
    Assessment of Selected Essays & 30\% \\
    \bottomrule
  \end{tabular}}
  \caption{Distribution of Grades}
  \label{grade-dist}
\end{table}

% Evaluation scheme from Summer 2017 intensive
%
%\begin{enumerate}% 200*7+250*8 = 3400 words, plus the annotated articles
%
%	\item Before each class, complete the assigned reading and write a
%	200--250 word (one page) \textbf{reading response}. Use the exercise
%	to elaborate, reflect on, test, challenge, or extend an idea from
%	the reading that you find noteworthy. Type your responses, write in
%	complete sentences, and combine those sentences into one or two
%	healthy paragraphs. Due at the start of \textbf{each class}, unless
%	it is the first class or another graded assignment is due. Students
%	who submit fewer than 6 responses cannot earn an “A” for the course.
%
%	\item On one sheet of paper, annotate a list of between 7 and 12
%	essential \textbf{articles of faith} that Christians associate with
%	Old Testament scripture. For guidance on what counts as “essential”
%	you may consult various catechisms (Catholic, Lutheran), creeds
%	(Apostles', Nicene, New), and other official documents (Articles,
%	Encyclicals, Statements). In your annotations, cite OT texts that
%	seem to speak to each of the doctrines you select, whether for or
%	against or both. Due at the start of \textbf{class four}.
%
%	\item A \textbf{final paper} allows you to explore one Christian
%	Doctrine of your choice in terms of its relationship to Old
%	Testament scripture. The paper must have a clear thesis and be at
%	least 2,000 words (eight pages) long. It should interact with the
%	assigned reading and cite at least four secondary sources in total.
%	Due at the start of the \textbf{last class}.
%
%\end{enumerate}
%
%Note that this course is an intensive. Its format is highly condensed.
%In a two week period students are expected to attend 30 hours of class
%and to spend a further 50 hours \emph{or more} in independent study.
%Students are therefore encouraged not to have other major commitments
%during the course session so that they can have the best chance of
%success.
%
%The breakdown for the course's total work is shown in
%\autoref{grade-dist}.
%
%\begin{table}[htbp]
%  \centering
%  {\lining
%  \begin{tabular}{lr}
%    \toprule
%    Reading Responses  & 35\% \\
%    Annotated Articles & 20\% \\
%    Final Paper        & 45\% \\
%    \bottomrule
%  \end{tabular}}
%  \caption{Distribution of Grades}
%  \label{grade-dist}
%\end{table}

\input{\policy/grades}
\input{\policy/other}

\end{document}
