% Copyright (c) 2016 by Daniel R. Driver.
% !TEX encoding = UTF-8 Unicode
% !TEX TS-program = XeLaTeX

\documentclass[titlepage]{article}

% This document presumes a file structure and set of inputs that are
% available at: git@github.com:danieldriver/syllabi.git

\newcommand\policy{../policy}
\newcommand\incl{../includes}
\input{\incl/variables}

\coursecode[4.0]{HB 2201} % rething version number; 4.0 was for HEBR 2013 at Tyndale, Fall 2015
\coursetitle{Beginning Biblical Hebrew I}

\professor{Daniel R. Driver}
\phone{416.226.6620 x2201}
\email{ddriver@tyndale.ca}
\officehours{Mon. \& Wed., 2:30--3:30 \PM}

\semester{Fall 2015}
\meets{Mondays \& Thursdays}% \meets{on}{at}{in}
      {11:15 \AM--12:35 \PM}
      {Bayview E221}
\website{classes.tyndale.ca}
\cdescription{% copy from tyndale.ca/registrar/calendar
	An introduction to the basic principles of biblical Hebrew with
	emphasis on morphology, phonology, and syntax. Exclusion:
	\textsc{hebr} 101.
}% end of course description
\objectives{% recall Bloom's taxonomy: http://www.celt.iastate.edu/teaching/RevisedBlooms1.html

	The basic goal of this course is to become proficient in the
	rudiments of Biblical Hebrew. The introductory course is designed
	for two semesters of study, and it is presumed that students will
	take the course for the entire academic year. In the first semester
	students will learn everything from the alphabet to the basics of
	Hebrew nouns and verbs. In the second semester the emphasis will
	fall on less regular paradigms (learned inductively) and more
	complicated syntax. The steady acquisition of vocabulary will be
	emphasized across both semesters.

	Language learning is work, but it can also be fun and gratifying. To
	aid in the enjoyment, we will sing songs together, memorize and
	recite passages of scripture, and assist one another in a variety of
	ways as we undertake the necessary drills and repetitions.

}% end of learning objectives

\input{\incl/preamble}

\begin{document}
\input{\incl/title}

\section{Required Texts \& Materials}
\label{texts}

All required textbooks are available in the Tyndale Bookstore.

\begingroup
\renewcommand{\section}[2]{}% temporarily remove the section heading
\begin{thebibliography}{BBH}% use the longest item in the bibliography

    \bibitem[BBH]{bbh}
    John A. Cook and Robert D. Holmstedt.
    \emph{Beginning Biblical Hebrew: A Grammar and Illustrated Reader}.
    Grand Rapids: Baker Academic, 2013. Note that this textbook includes a significant set of study aids at
    <\href{http://www.bakerpublishinggroup.com/books/beginning-biblical-hebrew/342630/students/esources}{www.bakeracademic.com}>.

    \bibitem[TM]{tm}
    Takamitsu Muraoka.
    \emph{A Biblical Hebrew Reader: With an Outline Grammar}.
    Leuven: Peeters, 2017. ISBN 978-9042934900.

    \bibitem[BHS]{bhs}
    \emph{Biblia Hebraica Stuttgartensia}.
    Stuttgart: Deutsche Bibel\-ge\-sell\-schaft, 1997. ISBN 978-1598561630.
    A paperback edition, marketed to students, is also available.
    Students will be asked to have a criticial edition of the Hebrew
    Bible by the start of the Winter semester. The instructor will
    provide photocopies in the interim.

\end{thebibliography}
\endgroup

\section{Supplementary Texts}
\label{supplementary}

There are many Hebrew grammars and resources. Below are some to which
I may refer, or which I judge to be especially helpful to beginning
students.

\begin{itemize}
  \item Guides

    \begin{itemize}
      \item
        Van Pelt, Miles, \emph{English Grammar to Ace Biblical Hebrew}
        (Grand Rapids: Zondervan, 2010). Call no.:
        \href{http://cat.tyndale.ca/vwebv/holdingsInfo?bibId=146389}{PE 1130 .H5 V35 2010}
      \item
        Scott, W. R., and H. P. Rüger, \emph{A Simplified Guide to BHS:
        Critical Apparatus, Masora, Accents, Unusual Letters \& Other
        Markings} (3rd ed.; N. Richland Hills, TX: BIBAL, 1995). Call
        no. (1987 ed.):
        \href{http://cat.tyndale.ca/vwebv/holdingsInfo?bibId=73217}{Ref BS 715 1984}
    \end{itemize}

  \item Grammars

    \begin{itemize}
      \item
        Pratico, Gary and Miles Van Pelt, \emph{Basics of Biblical Hebrew}
        (Grand Rapids: Zondervan, 2001). Call no.:
        \href{http://cat.tyndale.ca/vwebv/holdingsInfo?bibId=58735}{PJ 4567 .3 .P73 2001}
      \item
        Seow, C. L., \emph{A Grammar for Biblical Hebrew} (Nashville   :
        Abingdon, 1995). Call no.                                      :
        \href{http://cat.tyndale.ca/vwebv/holdingsInfo?bibId=23111}{PJ 4567 .S424 1995}
      \item
        Weingreen, J., \emph{A Practical Grammar for Classical Hebrew}
        (Oxford: Clarendon, 1959). Call no.:
        \href{http://cat.tyndale.ca/vwebv/holdingsInfo?bibId=13817}{PJ 4567 .W4 1939}
      \item
        Martin, J. D., \emph{Davidson’s Introductory Hebrew Grammar}
        (27th edition; Edinburgh: T\&T Clark, 1993). This is the grammar
        I was assigned in St Andrews, Scotland. Our library has copies
        of some older editions of Davidson, including the 26th. Call no.:
        \href{http://cat.tyndale.ca/vwebv/holdingsInfo?bibId=13804}{PJ 4567 .D3 1966}
      \item
        Gesenius, Wilhelm, E. Kautsch and A. E. Cowley, \emph{Hebrew
        Grammar} (Oxford: Clarendon, 1910). \textbf{GKC} remains the
        standard Hebrew reference grammars in English, even though
        Cowley's translation -- of the 28th german edition -- is now
        over 100 years old. Call no.:
        \href{http://cat.tyndale.ca/vwebv/holdingsInfo?bibId=72811}{Ref PJ 4567 .G46 1910}
    \end{itemize}

  \item Lexicons

    \begin{itemize}
      \item
        Brown, Francis, S.\,R. Driver and Charles A. Briggs. \emph{The
        Brown-Driver-Briggs Hebrew and English Lexicon}. Peabody, Mass:
        Hendrickson, 2004. The \textbf{BDB} was originally published in 1906
        (note the reliance on Gesenius: \href{https://archive.org/details/hebrewenglishlex00geseuoft}{archive.org}).
      \item
        Köhler, Ludwig, and Walter Baumgartner, \emph{The Hebrew
        and Aramaic Lexicon of the Old Testament} (Leiden: Brill,
        1994--2000). Call no.:
        \href{http://cat.tyndale.ca/vwebv/holdingsInfo?bibId=73713}{Ref PJ 4833 .K61813}
      \item
        Clines, David J. A., ed., \emph{The Dictionary of Classical
        Hebrew} (Sheffield: Sheffield Academic Press, 1993--2011). Call no.:
        \href{http://cat.tyndale.ca/vwebv/holdingsInfo?bibId=72831}{Ref PJ 4833 .D53}
    \end{itemize}

\end{itemize}

\section{Course Outline}
\label{outline}

We will adhere to the schedule as closely as possible, though I reserve
the right to adjust it to suit the needs of the class.

\setcolumncount{3}
\begin{table}[phtb]
  \centering\addfontfeature{ItalicFont=SBLBibLit}
  \begin{tabular}{@{}r<{.}@{ }lr}
    \toprule
    \bfseries\S & \textbf{Grammar Lesson}                                         & \textbf{Date} \\
    \midrule
    1   & \texthebrew{שׁלום}, The Consonants                               & 10 Sept. \\
    2   & The Vowels                                                      & 14 Sept. \\
    3   & \texthebrew{שׁוא} (\emph{Shəva})                                 & 17 Sept. \\
    4   & \texthebrew{דגשׁ} (\emph{Dagesh})                                &          \\
    5   & Subject Pronouns: Singular                                      & 21 Sept. \\
    7   & Copular Clauses                                                 & 24 Sept. \\
    6   & Nouns: Singular                                                 &          \\
    8   & The Article \texthebrew{ה} and the Interrogative \texthebrew{ה} & 28 Sept. \\
    9   & \texthebrew{ל} of Possession: Singular                          & 1 Oct.   \\
    r-1 & \texthebrew{מקרא א} (Reading 1)                                & 5 Oct.   \\
    10  & Nouns: Plural and Dual                                          & 8 Oct.   \\
    11  & Subject Pronouns: Plural                                        &          \\
    \noclass{Thanksgiving}                                                & 12 Oct.  \\
    12  & \texthebrew{ישׁ} and \texthebrew{אין}                            & 15 Oct.   \\
    13  & Conjunction \texthebrew{ו} and Prepositions \texthebrew{בּ},
         \texthebrew{כּ}, \texthebrew{ל}, \texthebrew{מן}                  & 19 Oct.  \\
    14  & \texthebrew{שׁאלוח} (Questions)                                  &          \\
    \noclass{Reading Day}                                                 & 22 Oct.  \\
    \sessionskip{\rarr} & \textbf{Midterm Exam}                           & 26 Oct.  \\
    r-2 & \texthebrew{מקרא ב} (Genesis 3\texthebrew{א})                   & 29 Oct.  \\
    15  & Verbs: A Preview                                                & 2 Nov.  \\
    16  & \texthebrew{קל} Perfect Conjugation: Singular                   &          \\
    17  & \texthebrew{ל} of Possession: Plural                            & 5 Nov.   \\
    18  & Word Order                                                      &          \\
    r-3 & \texthebrew{מקרא ג} (Genesis 22\texthebrew{א})                  & 9 Nov.   \\
    19  & \texthebrew{קל} Perfect Conjugation: Plural                     & 12 Nov.  \\
    20  & \texthebrew{סמיכות} (Bound Nouns)                               &          \\
    21  & The Irreal Use of the Perfect Conjugation                       & 16 Nov.  \\
    22  & Attached Pronouns: Singular                                     & 19 Nov.  \\
    23  & \texthebrew{קל} Imperfect Conjugation: Singular                 &          \\
    r-4 & \texthebrew{מקרא ד} (Genesis 37\texthebrew{א})                  & 23 Nov.  \\
    24  & The Infinitive                                                  & 26 Nov.  \\
    25  & The Adverbial Infinitive                                        &          \\
    26  & Objects                                                         & 30 Nov.  \\
    r-5 & \texthebrew{מקרא ד} (Genesis 3\texthebrew{ב})                   & 3 Dec.   \\
    \sessionskip{\rarr} & Review for the \textbf{Final Exam}              & 7 Dec.   \\
    \bottomrule
  \end{tabular}
  \caption{Schedule of Readings}
  \label{schedule}
\end{table}

See the Registrar's website for a list of other
\href{http://www.tyndale.ca/registrar/important-dates}{important dates}.
The last day to add a class, or to drop one without penalty, is
ordinarily the end of the term's second week.

\section{Evaluation}
\label{evaluation}

\subsection{Grade Structure for \ccode}
\label{structure}

\begin{enumerate}
 \item
    Students are expected to complete all exercises for the assigned
    lessons and readings in \cite{bbh}. Workbooks may be spot-checked
    for completeness at any time. Failure to complete the work may
    result in a 5\% deduction from the total grade.
%  \item
%    Tutorials are offered every Wednesday of the semester, from
%    5:20--6:20 p.m. Attendance is not required, but it is strongly
%    encouraged. Those who attend 10 sessions over the semester will
%    receive a 5\% bonus on their total grade; 8 or 9 get 3\%.
  \item
    Up to once a week, usually on Thursdays, I will distributed short
    quizzes in class. These will often come directly from \cite{bbh}.
 \item
   A midterm exam will be given in class as scheduled in the course
   outline (Section~\ref{outline}).
 \item
   A comprehensive final exam will be held during the exam period as
   schedule by the Registrar (see Section~\ref{exams}).
\end{enumerate}

The breakdown for the semester's total work is as follows:

\begin{table}[htbp]
  \centering
  {\lining
  \begin{tabular}{lr}
    \toprule
    Quizzes      & 30\% \\
    Midterm Exam & 30\% \\
    Final Exam   & 40\% \\
    \bottomrule
  \end{tabular}}
  \caption{Distribution of Grades}
  \label{distribution}
\end{table}

\input{\policy/grades}

\section{Policy on Assignments \& Exams}
\label{policy}

\input{\policy/academic_calendar}
\input{\policy/assignments}
\input{\policy/exams}

\section{Student Expectations \& Guidelines}
\label{expectations}

\input{\policy/academic_integrity}
\input{\policy/attendance}
\input{\policy/technology-hebrew}

\input{\policy/support}

\section{Course Bibliography}
\label{bibliography}

For resources in addition to those flagged in Section~\ref{supplementary},
browse PJ 4564--PJ4567 in the Tyndale library. For an audio version of the
Hebrew Bible, go to <\href{http://aoal.org/hebrew_audiobible.html}{aoal.org/hebrew\_audiobible.html}>.

\end{document}
