% -*- program: xelatex -*-
% -*- pdf: HEBR_3013_Driver_F14 -*-

\documentclass[titlepage]{article}
% clone the necessary input files: git@github.com:danieldriver/syllabus.git
\newcommand\policy{../policy}
\newcommand\incl{../includes}
\input{\incl/variables}

\coursecode[3.0]{HEBR 3013}
\coursetitle{Readings in Biblical Hebrew I}

\professor{Daniel R. Driver}
\phone{416-226-6620 ext. 2201}
\email{ddriver@tyndale.ca}
\officehours{Mon. \& Thur., 1:30--3:30 \PM}

\semester{Fall 2014}
\meets{Mondays \& Wednesdays} % \meets{on}{at}{in}
      {8:15--9:35 \AM}
      {Ballyconnor 2083}
\website{classes.tyndale.ca}
\cdescription{% copy from tyndale.ca/registrar/calendar
  Provides the student with a broad exposure to an extensive amount of
  biblical Hebrew prose, facilitating an environment where the student's
  reading ability is enhanced. In addition to providing a platform of
  advanced morphology and syntax, also provides a preliminary
  introduction to matters of textual criticism and exposure to the
  Septuagint and Qumran materials. Prerequisites: \textsc{hebr} 201,
  202; \textsc{bsth} 101, 102, 201. Exclusion: \textsc{hebr} 401.
}

\input{\incl/preamble}

\begin{document}
\input{\incl/title}

\section{Learning Outcomes}
\label{outcomes}

The basic goal of this course is to become proficient in reading
biblical Hebrew. We will build on what students have done in previous
study, aiming to bridge whatever gaps remain between rudimentary Hebrew
and intermediate to advanced reading competence. Students will progress
toward the mature, independent use of Hebrew language skills, though of
course the need for memorization does not disappear: the steady
acquisition of vocabulary will continue, as will the memorization of
select passages of scripture.

By the end of the course students should be able to:
  recite and write out Psalm 1 in Hebrew;
  classify different types of classical Hebrew literature;
  read and translate representative Hebrew texts from historical, legal, prophetic and poetic material;
  comfortably read aloud any unfamiliar pointed texts (without necessarily translating them on the spot);
  use standard grammars and lexicons to study and translate unfamiliar texts independently.

\section{Required Texts \& Materials}
\label{texts}

All required texts are available in the Tyndale Bookstore.

\begingroup
\renewcommand{\section}[2]{}% temporarily remove the section heading
\begin{thebibliography}{Ben Zvi}% use the longest item in the bibliography
  \bibitem[BHS]{bhs}
    Karl Elliger and Willhelm Rudolph, eds. \emph{Biblia Hebraica
    Stuttgartensia}. Stutt\-gart: Deut\-sche Bi\-bel\-ge\-sell\-schaft,
    1997. Repr. in paperback, Peabody, Mass.: Hendrickson, 2006. The
    \href{http://www.academic-bible.com/en/home/current-projects/biblia-hebraica-quinta-bhq/}%
    {Biblia Hebraica Quinta} (BHQ), a fifth edition of the Biblia
    Hebraica, is currently in preparation and will eventually supplant
    the BHS. To date six fascicles are in print:
        Deuteronomy (2007),
        Judges (2011),
        the Twelve Prophets (2010),
        Proverbs (2008),
        the Five Megilloth (2004),
        Ezra and Nehemiah (2006).
  \bibitem[BDB]{bdb}
    Francis Brown, S.\,R. Driver and Charles A. Briggs. \emph{The
    Brown-Driver-Briggs Hebrew and English Lexicon: With an Appendix
    Containing the Biblical Aramaic}. Peabody, Mass: Hendrickson, 2004.
    Originally published as \emph{A Hebrew and English Lexicon of the
    Old Testament} (Boston: Houghton, Mifflin and Co., 1906), which was
    in turn ``based on the lexicon of William Gesenius, as translated by
    Edward Robinson, and edited with constant reference to the thesaurus
    of Gesenius as completed by E. Rödiger, and with authorized use of
    the latest German editions of Gesenius's \emph{Handwörterbuch über
    das Alte Testament}." Browse the
    \href{https://archive.org/details/hebrewenglishlex00geseuoft}{original BDB online}.
  \bibitem[Ben Zvi]{bz}
    Ehud Ben Zvi, Maxine Hancock and Richard Beinert. \emph{Readings in
    Biblical Hebrew: An Intermediate Textbook}. Yale Language Series.
    New Haven: Yale University Press, 1993. The publisher offers a
    \href{http://yalepress.yale.edu/yupbooks/languages/pdf/Zvi_excerpt.pdf}%
    {free PDF of the first reading}.
\end{thebibliography}
\endgroup

\section{Supplementary Texts}
\label{supplementary}

In addition to \cite{bz} refer to these \textbf{grammars}:

\begin{enumerate}
\item
  GKC = E. Kautsch, translated from the 28th German edition and revised
  by A. E. Crowley. \emph{Gesenius' Hebrew Grammar}. Oxford: Clarendon,
  1910. Despite its age this is still a standard reference grammar. I
  hear that it is being revised again.
  [\href{http://tyndale.worldcat.org/oclc/748712337}{PJ 4567.G46 1910} and \href{http://tyndale.worldcat.org/oclc/575651}{online}]
\item
  JM = Paul Joüon, translated from the French and extensively revised by
  Takamitsu Muraoka. \emph{A Grammar of Biblical Hebrew}. 2nd ed. Rome:
  Pontificio Instituto Biblico, 2006. Revision of 2 vol. edition
  (Subsidia Biblica 14/1, 14/2), 1991.
  [\href{http://tyndale.worldcat.org/oclc/76949728}{PJ 4567.J7613 2006}]
\item
  KHW = Bonnie P. Kittel, Vicki Hoffer and Rebecca A. Wright.
  \emph{Biblical Hebrew: A Text and Workbook}. New Haven: Yale
  University Press, 1989. I have used the 2nd edition in class before,
  and in many ways it is a natural companion to \cite{bz}.
  [\href{http://tyndale.worldcat.org/oclc/18557541}{PJ 4567.3.K5 1989}]
\item
  Martin, J. D. \emph{Davidson's Introductory Hebrew Grammar}. 27th ed.
  Edinburgh: T\&T Clark, 1993. This is the grammar I was assigned in St
  Andrews, Scotland. Our library has copies of some older editions,
  including the 26th:
  [\href{http://tyndale.worldcat.org/oclc/456246}{PJ 4567.D3 1966}]
\item
  Seow, C. L. \emph{A Grammar for Biblical Hebrew}. Nashville: Abingdon,
  1995.
  [\href{http://tyndale.worldcat.org/oclc/32854250}{PJ 4567.S424 1995}]
\item
  Weingreen, J. \emph{A Practical Grammar for Classical Hebrew}. 2nd ed.
  Oxford: Clarendon, 1959. Robert Holmstedt told me in 2013 that he
  still prefers this as a basic grammar. Two older copies are in the
  library.
  [\href{http://tyndale.worldcat.org/oclc/926806}{PJ 4567.W4 1939}]
\item
  Williams, Ronald J. \emph{Williams' Hebrew Syntax}. 3rd ed. Revised
  and expanded by John C. Beckman. Toronto: University of Toronto Press,
  2007.
  [\href{http://tyndale.worldcat.org/oclc/84989344}{PJ 4701.W5 2007} and \href{http://ezproxy.mytyndale.ca:2048/login?url=http://search.ebscohost.com/login.aspx?direct=true&db=e093mww&AN=682592&site=ehost-live&scope=site}{online}]
\item
  WO'C = Bruce K. Waltke and Michael O'Connor. \emph{Biblical Hebrew
  Syntax}. Winona Lake, Ind.: Eisenbrauns, 1990.
  [\href{http://tyndale.worldcat.org/oclc/20088442}{PJ 4707.W35 1990}]
\end{enumerate}


In addition to the \cite{bdb} refer to these \textbf{lexicons}:

\begin{enumerate}\setcounter{enumi}{8}
\item
  Clines, David J. A. \emph{The Dictionary of Classical Hebrew}.
  Sheffield: Sheffield Academic Press, 1993--2011.
  [\href{http://tyndale.worldcat.org/oclc/29742583}{Ref PJ 4833.D53}]
\item
  HALOT or KB = Köhler, Ludwig, and Walter Baumgartner. \emph{The Hebrew
  and Aramaic Lexicon of the Old Testament}. 1st English ed. Leiden:
  Brill, 1994--2000.
  [\href{http://tyndale.worldcat.org/oclc/30905049}{Ref PJ 4833.K61813}]
\end{enumerate}

Refer also to the following \textbf{aids and general guidance}:

\begin{enumerate}\setcounter{enumi}{10}
\item
  Einspahr, Bruce. \emph{Index to Brown, Driver \& Briggs Hebrew
  Lexicon}. Chicago: Moody, 1976.
  [\href{http://tyndale.worldcat.org/oclc/3741038}{Ref PJ 4833.B6 E35 1976}]
\item
  Guide = Scott, W.R. and H.P. Scanlin. \emph{A Simplified Guide to BHS:
  Critical Apparatus, Masora, Accents, Unusual Letters \& Other
  Markings}. Richland Hills: BIBAL, 2007.
  [\href{http://tyndale.worldcat.org/oclc/17336542}{Ref BS 715 1984}]
\item
  Landes, George M. \emph{Building Your Biblical Hebrew Vocabulary:
  Learning Words by Frequency and Cognate}. Resources for Biblical Study
  41. Atlanta: Society of Biblical Literature, 2001.
  [\href{http://tyndale.worldcat.org/oclc/45230417}{PJ 4845.L25 2001}]
\item
  Masorah = Page H. Kelley, Daniel S. Mynatt and Timothy G. Crawford.
  \emph{The Masorah of Biblia Hebraica Stuttgartensia: Introduction and
  Annotated Glossary}. Grand Rapids: Eerdmans, 1998.
  [\href{http://tyndale.worldcat.org/oclc/38168226}{Ref BS 718.K38 1998}]
\item
  Sáenz-Badillos, Angel. \emph{A History of the Hebrew Language}.
  Cambridge: Cambridge University Press, 1996.
\item
  Tov, Emanuel. \emph{Textual Criticism of the Hebrew Bible}.
  3\textsuperscript{rd} edition, revised and expanded. Minneapolis:
  Fortress, 2012.
  [\href{http://tyndale.worldcat.org/oclc/26129277}{BS 1136.T6813 1992}]
\end{enumerate}

\section{Evaluation}
\label{evaluation}

\subsection{Grade Structure for \ccode}
\label{structure}

\begin{enumerate}

 \item The backbone of the course is reading and \textbf{translation}.
 Biblical texts are set for each week. Students are to provide their own
 translations for class, which are then to be collected, refined and
 typed for submission at the end of each unit.

 \item Weekly quizzes make sure that students have acquired a
 rudimentary \textbf{vocabulary} (500 friends) by the end of the fall
 semester.

 \item By the end of the 10th week students need to schedule office
 hours with the professor to \textbf{recite Psalm 1} in Hebrew. We will
 study and practice reciting the psalm in class, but each student is
 responsible to memorize it individually.

 \item A comprehensive \textbf{final exam} will be held during the exam
 period as schedule by the Registrar (see Section~\ref{exams}). It is
 designed to assess learning outcomes---how well you have obtained the
 objectives outlined in Section~\ref{outcomes}. Test your readiness for
 the final by asking yourself how well you can perform the tasks
 outlined in those paragraphs.

\end{enumerate}

The breakdown for the semester's total work is as follows:

\begin{table}[htbp]
  \centering
  {\lining
  \begin{tabular}{lr}
    \toprule
    Translation Sets (4) & 40\% \\
    Vocabulary Quizzes   & 25\% \\
    Recitation of Ps 1  & 10\% \\
    Final Examination    & 25\% \\
    \bottomrule
  \end{tabular}}
  \caption{Distribution of Grades}
  \label{distribution}
\end{table}

\input{\policy/grades}

\section{Policy on Assignments \& Exams}
\label{policy}

\input{\policy/academic_calendar}
\input{\policy/assignments}
\input{\policy/exams}

\section{Student Expectations \& Guidelines}
\label{expectations}

\input{\policy/academic_integrity}
\input{\policy/attendance}
\input{\policy/technology}

\input{\policy/support}

\section{Course Outline}
\label{outline}

Readings should be completed before the start of the class for which they are
assigned. We will adhere to the schedule as closely as possible, though I
reserve the right to adjust it to suit the needs of the class.

\setcolumncount{4} % set up \sessioncount, \unit{} and \noclass{} macros
\begin{table}[htb]% add p to put the schedule on its own page
  \centering
  \begin{tabular}{>{\sessioncount.}r@{ }llr}
    \toprule
    \sessionskip{\textbf{\S}.}&\textbf{BHS Reading}&\textbf{Ben Zvi}&\textbf{Date}\\
    \midrule
          & Psalm 1                           & pp. 207--216  &  8 Sep.   \\
    \unit{Readings in the Historical Books} \\
          & 1 Samuel 1:1--3                   & pp. 3--7      & 10 Sep.   \\ [1ex]
          
          & 1 Samuel 1:4--11                  & pp. 7--20     & 15 Sep.   \\
          & 1 Samuel 1:12--18                 & pp. 21--28    & 17 Sep.   \\ [1ex]
          
          & 1 Samuel 1:19--28                 & pp. 28--40    & 22 Sep.   \\
          & 2 Kings 14:23--29                 & pp. 41--51    & 24 Sep.   \\ [1ex]
          
    \unit{Readings in Legal Literature} \\
          & Exodus 21:28--32                  & pp. 55--63    & 29 Sep.   \\
          & Exodus 21:33--36                  & pp. 63--68    &  1 Oct.   \\ [1ex]
          
          & Leviticus 5:20--26                & pp. 69--82    &  6 Oct.   \\
          & Deuteronomy 24:14--18             & pp. 83--90    &  8 Oct.   \\ [1ex]
          
    \noclass{Thanksgiving}                                    & 13 Oct.   \\
          & Deuteronomy 24:18--22             & pp. 90--96    & 15 Oct.   \\ [1ex]
          
    \unit{Readings in Prophetic Literature} \\
          & Jeremiah 22:1--5                  & pp. 99--111   & 20 Oct.   \\
          & Ezekiel 37:1--5                   & pp. 112--122  & 22 Oct.   \\ [1ex]
%   \noclass{Reading Days}                                    & 23--24 Oc \\
    
          & Ezekiel 37:6--10                  & pp. 122--130  & 27 Oct.   \\
          & Ezekiel 37:11--14                 & pp. 130--138  & 29 Oct.   \\ [1ex]
          
          & Isaiah 49:1--3                    & pp. 139--147  &  3 Nov.   \\
          & Isaiah 49:4--6                    & pp. 147--157  &  5 Nov.   \\ [1ex]
          
    \unit{Readings in Wisdom Literature} \\
          & Proverbs 3:13--20                 & pp. 161--170  & 10 Nov.   \\
          & Proverbs 3:21--26, 10:1, 16:8     & pp. 170--182  & 12 Nov.   \\ [1ex]
          
          & Proverbs 22:22--23, 24:29, 25:28  & pp. 182--189  & 17 Nov.   \\
          & Qohelet 1:1--5                    & pp. 190--197  & 19 Nov.   \\ [1ex]
          
          & Qohelet 1:6--11                   & pp. 197--204  & 24 Nov.   \\
    \unit{Readings in the Psalms} \\
          & Psalm 15                          & pp. 217--229  & 26 Nov.   \\ [1ex]

          & Psalm 150                         & pp. 230--235  & 1 Dec.    \\
    \noclass{Reading Days}                                    & 2--3 Dec. \\
    \bottomrule
  \end{tabular}
  \caption{Schedule of Readings}
  \label{schedule}
\end{table}

See the \href{http://www.tyndale.ca/registrar/important-dates}{Registrar's
website} for a list of other important dates. The last day to add a class, or
to drop one without penalty, is ordinarily the end of the term's second week.

\section{Course Bibliography}
\label{bibliography}

Refer to the bibliographies that \cite{bz} provides for the
selection of texts we study.

\end{document}
