% Copyright (c) 2015 by Daniel R. Driver.
% !TEX encoding = UTF-8 Unicode
% !TEX TS-program = XeLaTeX

\documentclass[titlepage]{article}

% This document presumes a file structure and set of inputs that are
% available at: git@github.com:danieldriver/syllabi.git

\newcommand\policy{../policy}
\newcommand\incl{../includes}
\input{\incl/variables}

\coursecode[3.0]{HEBR 3013}
\coursetitle{Readings in Biblical Hebrew II}

\professor{Daniel R. Driver}
\phone{416.226.6620 x2201}
\email{ddriver@tyndale.ca}
\officehours{Mon. \& Wed., 1:30--3:30 \PM}

\semester{Winter 2015}
\meets{Mondays \& Wednesdays}% \meets{on}{at}{in}
      {8:15--9:35 \AM}
      {Ballyconnor 2081}
\website{classes.tyndale.ca}
\cdescription{% copy from tyndale.ca/registrar/calendar

	As a continuation of Readings in Biblical Hebrew I, provides
	students with an opportunity to advance their skills in reading
	considerable portions of biblical Hebrew prose. In addition to
	further studies in advanced grammar, syntax and text criticism,
	features an introduction to biblical Hebrew poetry in the classical
	writing Prophets. Prerequisite: \textsc{hebr} 301. Exclusion:
	\textsc{hebr} 402.

}% end of course description

\input{\incl/preamble}

\begin{document}
\input{\incl/title}

\section{Learning Outcomes}
\label{outcomes}

The basic goal of this course is to become more proficient in reading
biblical Hebrew. We will build on what students have done in previous
study, aiming to bridge whatever gaps remain between rudimentary Hebrew
and intermediate to advanced reading competence. Students will progress
toward the mature, independent use of Hebrew language skills, though of
course the need for memorization does not disappear: the steady
acquisition of vocabulary will continue, as will the memorization of
Hebrew psalms.

By the end of the course students should be able to:
	recite and write out Psalm 15 in Hebrew;
	classify different types of classical Hebrew literature;
	read and translate short biblical books in their entirety;
	comfortably read aloud any unfamiliar pointed texts;
	use standard grammars and lexicons to study and translate unfamiliar texts independently.

\section{Required Texts \& Materials}
\label{texts}

All required textbooks are available in the Tyndale Bookstore.

\begingroup
\renewcommand{\section}[2]{}% temporarily remove the section heading
\begin{thebibliography}{Holm}% use the longest item in the bibliography

	\bibitem[BHS]{bhs}
	Karl Elliger and Willhelm Rudolph, eds. \emph{Biblia Hebraica
	Stuttgartensia}. Stutt\-gart: Deut\-sche Bi\-bel\-ge\-sell\-schaft,
	1997. Repr. in paperback, Peabody, Mass.: Hendrickson, 2006. The
	\href{http://www.academic-bible.com/en/home/current-projects/biblia-hebraica-quinta-bhq/}%
	{Biblia Hebraica Quinta} (BHQ), a fifth edition of the Biblia
	Hebraica, is currently in preparation and will eventually supplant
	the BHS. To date six fascicles are in print:
		Deuteronomy (2007),
		Judges (2011),
		the Twelve Prophets (2010),
		Proverbs (2008),
		the Five Megilloth (2004),
		Ezra and Nehemiah (2006).
		Genesis is scheduled to arrive later in 2015.

	\bibitem[BDB]{bdb}
	Francis Brown, S.\,R. Driver and Charles A. Briggs. \emph{The
	Brown-Driver-Briggs Hebrew and English Lexicon: With an Appendix
	Containing the Biblical Aramaic}. Peabody, Mass: Hendrickson, 2004.
	Originally published as \emph{A Hebrew and English Lexicon of the
	Old Testament} (Boston: Houghton, Mifflin and Co., 1906), which was
	in turn ``based on the lexicon of William Gesenius, as translated by
	Edward Robinson, and edited with constant reference to the thesaurus
	of Gesenius as completed by E. Rödiger, and with authorized use of
	the latest German editions of Gesenius's \emph{Handwörterbuch über
	das Alte Testament}'' (\href{https://archive.org/details/hebrewenglishlex00geseuoft}{archive.org}).

	\bibitem[Holm]{holm}
	Robert D. Holmstedt. \emph{Ruth: A Handbook on the Hebrew Text}.
	Baylor Handbook on the Hebrew Bible. Waco: Baylor University Press,
	2010. The publisher offers a 25\% discount code to students who
	order directly with them (see me).

	\bibitem[Wms]{wms}
	Ronald J. Williams. \emph{Williams' Hebrew Syntax}. 3rd ed. Revised
	and expanded by John C. Beckman. Toronto: University of Toronto
	Press, 2007. You must have your own hard copy as we will work
	through the book together in class.

\end{thebibliography}
\endgroup

\section{Supplementary Texts}
\label{supplementary}

Refer to these \textbf{reference grammars} and \textbf{introductory texts}:

\begin{enumerate}

	\item GKC = E. Kautsch, translated from the 28th German edition and
	revised by A. E. Crowley. \emph{Gesenius' Hebrew Grammar}. Oxford:
	Clarendon, 1910. Despite its age this is still a standard reference
	grammar. I hear that it is being revised again.
	[\href{http://tyndale.worldcat.org/oclc/748712337}{PJ 4567.G46 1910} and \href{http://tyndale.worldcat.org/oclc/575651}{online}]

	\item JM = Paul Joüon, translated from the French and extensively
	revised by Takamitsu Muraoka. \emph{A Grammar of Biblical Hebrew}.
	2nd ed. Rome: Pontificio Instituto Biblico, 2006. Revision of 2 vol.
	edition (Subsidia Biblica 14/1, 14/2), 1991.
	[\href{http://tyndale.worldcat.org/oclc/76949728}{PJ 4567.J7613 2006}]

	\item BBH = John A. Cook and Robert D. Holmstedt. \emph{Beginning
	Biblical Hebrew: A Grammar and Illustrated Reader}. Grand Rapids:
	Baker Academic, 2013.
	[\href{http://bakeracademic.com/beginningbiblicalhebrew}{study aids}]

	\item Ben Zvi = Ehud Ben Zvi, Maxine Hancock and Richard Beinert.
	\emph{Readings in Biblical Hebrew: An Intermediate Textbook}. Yale
	Language Series. New Haven: Yale University Press, 1993.
	[\href{http://yalepress.yale.edu/yupbooks/languages/pdf/Zvi_excerpt.pdf}{excerpt}]

	\item KHW = Bonnie P. Kittel, Vicki Hoffer and Rebecca A. Wright.
	\emph{Biblical Hebrew: A Text and Workbook}. New Haven: Yale
	University Press, 1989. I have used the 2nd edition in class before,
	and in many ways it is a natural companion to Ben Zvi.
	[\href{http://tyndale.worldcat.org/oclc/18557541}{PJ 4567.3.K5 1989}]

	\item Martin, J. D. \emph{Davidson's Introductory Hebrew Grammar}.
	27th ed. Edinburgh: T\&T Clark, 1993. This is the grammar I was
	assigned in St Andrews, Scotland. Our library has copies of some
	older editions, including the 26th:
	[\href{http://tyndale.worldcat.org/oclc/456246}{PJ 4567.D3 1966}]

	\item Seow, C. L. \emph{A Grammar for Biblical Hebrew}. Nashville:
	Abingdon, 1995.
	[\href{http://tyndale.worldcat.org/oclc/32854250}{PJ 4567.S424 1995}]

	\item Weingreen, J. \emph{A Practical Grammar for Classical Hebrew}.
	2nd ed. Oxford: Clarendon, 1959. Robert Holmstedt told me in 2013
	that he still prefers this as a basic grammar. Two older copies are
	in the library.
	[\href{http://tyndale.worldcat.org/oclc/926806}{PJ 4567.W4 1939}]

	\item Williams, Ronald J. \emph{Williams' Hebrew Syntax}. 3rd ed.
	Revised and expanded by John C. Beckman. Toronto: University of
	Toronto Press, 2007.
	[\href{http://tyndale.worldcat.org/oclc/84989344}{PJ 4701.W5 2007} and \href{http://ezproxy.mytyndale.ca:2048/login?url=http://search.ebscohost.com/login.aspx?direct=true&db=e093mww&AN=682592&site=ehost-live&scope=site}{online}]

	\item WO'C = Bruce K. Waltke and Michael O'Connor. \emph{Biblical
	Hebrew Syntax}. Winona Lake, Ind.: Eisenbrauns, 1990.
	[\href{http://tyndale.worldcat.org/oclc/20088442}{PJ 4707.W35 1990}]

\end{enumerate}

In addition to \cite{bdb} refer to these \textbf{lexicons}:

\begin{enumerate}\setcounter{enumi}{10}

	\item Clines, David J. A. \emph{The Dictionary of Classical Hebrew}.
	Sheffield: Sheffield Academic Press, 1993--2011.
	[\href{http://tyndale.worldcat.org/oclc/29742583}{Ref PJ 4833.D53}]

	\item HALOT or KB = Köhler, Ludwig, and Walter Baumgartner.
	\emph{The Hebrew and Aramaic Lexicon of the Old Testament}. 1st
	English ed. Leiden: Brill, 1994--2000.
	[\href{http://tyndale.worldcat.org/oclc/30905049}{Ref PJ 4833.K61813}]

\end{enumerate}

Refer also to the following general \textbf{aids and guides}:

\begin{enumerate}\setcounter{enumi}{12}

	\item Einspahr, Bruce. \emph{Index to Brown, Driver \& Briggs Hebrew
	Lexicon}. Chicago: Moody, 1976.
	[\href{http://tyndale.worldcat.org/oclc/3741038}{Ref PJ 4833.B6 E35 1976}]

	\item Guide = Scott, W.R. and H.P. Scanlin. \emph{A Simplified Guide
	to BHS: Critical Apparatus, Masora, Accents, Unusual Letters \&
	Other Markings}. Richland Hills: BIBAL, 2007.
	[\href{http://tyndale.worldcat.org/oclc/17336542}{Ref BS 715 1984}]

	\item Landes, George M. \emph{Building Your Biblical Hebrew
	Vocabulary: Learning Words by Frequency and Cognate}. Resources for
	Biblical Study 41. Atlanta: Society of Biblical Literature, 2001.
	[\href{http://tyndale.worldcat.org/oclc/45230417}{PJ 4845.L25 2001}]

	\item Masorah = Page H. Kelley, Daniel S. Mynatt and Timothy G.
	Crawford. \emph{The Masorah of Biblia Hebraica Stuttgartensia:
	Introduction and Annotated Glossary}. Grand Rapids: Eerdmans, 1998.
	[\href{http://tyndale.worldcat.org/oclc/38168226}{Ref BS 718.K38 1998}]

\end{enumerate}

\section{Evaluation}
\label{evaluation}

\subsection{Grade Structure for \ccode}
\label{structure}

% Please consider the following structure in your course. Evaluation
% should be clearly linked to Learning Outcomes.
%   - Some form of meaningful evaluation should occur during the first 4
%     weeks of the course; **all students should (and first-year
%     students must) receive an indication of their performance in the
%     first half of the course.**
%   - **Plan your assignments so that each can be returned to students
%     before the next is due.**
%   - Most courses should have a rigorous final exam of 2--3 hours
%     duration. Some upper-year courses may not require a final,
%     depending on pedagogical design and assessment strategy. **Final
%     exams should be appropriately demanding in both breadth and depth
%     to assess accurately the achievement of learning outcomes.**
%   - **No assignments should be due in the last week of classes; final
%     examinations will be scheduled only by the Registrar’s Office.**

\begin{enumerate}

	\item The backbone of the course is \textbf{reading and
	translation}. Chapters of biblical Hebrew are set for each week.
	Students are to provide their own translations for class, which are
	then to be collected, refined, and typed up for submission in weeks
	6 and 12.

	\item A \textbf{midterm exam} will be given in class as scheduled in
	the course outline (Section~\ref{outline}). It will stress the
	secondary reading for weeks 1 to 6 \cite{holm} as well as the text
	and translation of Qohelet 1 and Ruth 1--4.

	\item In weeks 7 to 10 each student is to \textbf{teach one of the
	four main topics} in \cite{wms}: nominals, verbs, particles, and
	clauses. The third unit, on particles, is longer than the others, so
	two students will share the task of teaching in week 9. Each
	presentation should last 45 minutes, and must include a
	\textbf{handout} summary of the topic (one page front and back) and
	selection of \textbf{key examples} from Williams to work through
	with the rest of the class.

	\item In the 12th week students need to \textbf{recite Psalm 15} in
	Hebrew. We will study and practice reciting the psalm in class, but
	each student is responsible to memorize it individually.

	\item A comprehensive \textbf{final exam} will be held during the
	exam period as schedule by the Registrar (see Section~\ref{exams}).
	It is designed to assess learning outcomes, i.e., your attainment of
	the objectives in Section~\ref{outcomes}. Test your readiness for
	the final by asking yourself how well you can perform the tasks
	outlined in those paragraphs.

\end{enumerate}

The breakdown for the semester's total work is as follows:

\begin{table}[htbp]
  \centering
  {\lining
  \begin{tabular}{lr}
    \toprule
    Two Translation Sets & 30\% \\
    Midterm Exam         & 25\% \\
    Teaching Unit        & 10\% \\
    Psalm Memorization   & 10\% \\
    Final Exam           & 25\% \\
    \bottomrule
  \end{tabular}}
  \caption{Distribution of Grades}
  \label{distribution}
\end{table}

\input{\policy/grades}

\section{Policy on Assignments \& Exams}
\label{policy}

\input{\policy/academic_calendar}
\input{\policy/assignments}
\input{\policy/exams}

\section{Student Expectations \& Guidelines}
\label{expectations}

\input{\policy/academic_integrity}
\input{\policy/attendance}
\input{\policy/technology-hebrew}

\input{\policy/support}

\section{Course Outline}
\label{outline}

Readings should be completed before the start of the class for which they are
assigned. We will adhere to the schedule as closely as possible, though I
reserve the right to adjust it to suit the needs of the class.

\setcolumncount{4}% set up \sessioncount, \unit{}, \noclass{}, and \reminder{memo}{date} macros
\begin{table}[htb]% add p to put the schedule on its own page
  \centering
  \begin{tabular}{>{\sessioncount.}r@{ }llr}% make sure the column config agrees with \setcolumncount
	\toprule
	\sessionskip{\textbf{Wk}.}&\textbf{Primary Reading}&\textbf{Secondary Reading}&\textbf{Date}\\
	\midrule
	& Qohelet 1           & Holmstedt 1--49           &  5, 7 Jan.      \\
	& Ruth 1              & Holmstedt 51--101         & 12, 14 Jan.     \\
	& Ruth 2              & Holmstedt 103--146        & 19, 21 Jan.     \\
	& Ruth 3              & Holmstedt 147--178        & 26, 28 Jan.     \\
	& Ruth 4              & Holmstedt 179--214        &   2, 4 Feb.     \\
	& Revise translations & Review                    &      9 Feb.     \\
	\reminder{\textbf{Midterm Exam} (given in class)}{11 Feb.}          \\ [1ex]

	\noclass{Reading Week}                            & 16--20 Feb.     \\ [1ex]

	& Jonah 1             & Williams 1--55            & 23, 25 Feb.     \\
	& Jonah 2             & Williams 56--95           &   2, 4 Mar.     \\
	& Jonah 3             & Williams 96--171 (!)      &  9, 11 Mar.     \\
	& Jonah 4             & Williams 172--211         & 16, 18 Mar.     \\
	& Psalms 1, 15, 150   & Ben Zvi (\textsc{hebr} 301) & 23, 25 Mar.   \\
	& Revise translations & Review                    &      30 Mar.    \\
	\reminder{\textbf{Psalm Recitation} (in the last class)}{1 Apr.}    \\ [1ex]
	\noclass{Reading Days}                            & 6--7 Apr.       \\
	\reminder{\textbf{Final Exam} (as schedule by the Registrar)}{8--15 Apr.} \\
	\bottomrule
  \end{tabular}
  \caption{Schedule of Readings}
  \label{schedule}
\end{table}

See the Registrar's website for a list of other
\href{http://www.tyndale.ca/registrar/important-dates}{important dates}.
The last day to add a class, or to drop one without penalty, is
ordinarily the end of the term's second week.

\section{Course Bibliography}
\label{bibliography}

In addition to the many tools listed in Section~\ref{supplementary}, the
following books are without parallel. Serious students will want to own
and study them.

\begin{enumerate}

	\item Sáenz-Badillos, Angel. \emph{A History of the Hebrew
	Language}. Cambridge: Cambridge University Press, 1996.

	\item Tov, Emanuel. \emph{Textual Criticism of the Hebrew Bible}.
	3\textsuperscript{rd} edition, revised and expanded. Minneapolis:
	Fortress, 2012.
	[\href{http://tyndale.worldcat.org/oclc/26129277}{BS 1136.T6813 1992}]

\end{enumerate}

Refer to the bibliographies that \cite{holm} provides for Ruth. I can
provide bibliographies for other particular readings upon request.

\end{document}
